### 2015-09-16 inst/manuscript/manuscript.rmd
Prettify the title;

---
title: "`flippant` -- An `R` package for the automated  analysis of dithionite 
  scramblase assays"
author: "Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
  Mike A. Goren ^‡^ and Anant K. Menon ^‡^"
date: "September 16, 2015"
output: 
#  word_document
  pdf_document:
    toc: false
    toc_depth: 2
    fig_caption: yes
#bibliography: flippant.bib
#csl: cell.csl
---

†

:    \
    Weill Cornell Medical College in Qatar, P.O.Box 24144, Doha, State of Qatar

‡

:   Department of Biochemistry, Weill Cornell Medical College, New York, NY 
    10065, USA

\*

:   To whom correspondence should be addresse: jog2030@qatar-med.cornell.edu

#Abstract

# Introduction
Scramblases are proteins mediating the mass-action driven equilibration of 
lipids between the sheets of lipid bilayers representing biological membranes
<CITE SOME REVIEW>. Indipendent of ATP or other energy equivalents they 
facilitate this ``flipping'' by providing a mechanism of transition through the 
hydrophobic environment of membranes to polar lipid head groups, thus 
reducing the massive energetic cost that process would carry otherwise <CITE 
ANANT HALF TIME>. While the underlying molecular mechanisms remain enigmatic 
<CITE SOMETHING>, and molecules supporting flipping processes as central as the 
equilibration of the ubiquitous phosphoglycerolipids across the membrane of the 
endoplasmic reticulum, where they are synthesized in the cytoplasmicfrom sheet, 
have yet to be identified <CITE SOMETHING>, there has been much recent progress 
in scramblase identification and characterization. Molecules shown to have 
scramblase activity include opsin/rhodopsin <CITE INDU, MIKE, BIRGIT>, X <CITE> 
and Y <CITE>.

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2015-09-16 inst/manuscript/manuscript.rmd
Do not use a TOC;

@@
   pdf_document:
-    toc: false
-    toc_depth: 2
     fig_caption: yes

### 2015-09-16 inst/manuscript/manuscript.rmd
Get the "Bioninformatics" citation style definition form the zotero repository and initiate its usage;
Reformat author associations etc.;

@@
 #bibliography: flippant.bib
-#csl: cell.csl
+#csl: bioinformatics.csl
 ---
@@
 †
-
 :    \
@@
 ‡
-
 :   Department of Biochemistry, Weill Cornell Medical College, New York, NY 
@@
 \*
-
-:   To whom correspondence should be addresse: jog2030@qatar-med.cornell.edu
+:   To whom correspondence should be addressed: jog2030@qatar-med.cornell.edu
 

### 2015-09-16 inst/manuscript/manuscript.rmd
Implement a structure compatible with "Bioinformatics";
Paraphrasing in first intro paragraph;

@@
 
+##Summary
+
+##Availability and Implementation
+
+##Contact
+jog2030@qatar-med.cornell.edu
+
+##Supplementary Information
+
 # Introduction
@@
 lipids between the sheets of lipid bilayers representing biological membranes
-<CITE SOME REVIEW>. Indipendent of ATP or other energy equivalents they 
+<CITE SOME REVIEW>. Indipendent of energy equivalents such as ATP they 
 facilitate this ``flipping'' by providing a mechanism of transition through the 
@@
 equilibration of the ubiquitous phosphoglycerolipids across the membrane of the 
-endoplasmic reticulum, where they are synthesized in the cytoplasmicfrom sheet, 
+endoplasmic reticulum, where they are synthesized in the cytoplasmic sheet, 
 have yet to be identified <CITE SOMETHING>, there has been much recent progress 
@@
 and Y <CITE>.
+
+#Main Features
+
+#Case Study
+
+#Conclusion
+
+#Funding
+J.G., R.J.C. and the Proteomics Core at WCMC-Q were supported by ``Biomedical 
+#Acknowledgements
 

### 2015-09-16 inst/manuscript/manuscript.rmd
Finalize a first intro draft (missing citations);

@@
 
+Following work by X <CITE>, Y<CITE> and Z<CITE>, we have develloped an assay 
+suited to characterize scramblase activity in purified proteins and protein 
+extracts <CITE OPSIN PAPER, MIKE, BIRGIT>, based on the reconstitution of 
+scramblases or candidate proteins into large synthetic vesicles with a lipid
+composition that includes the fluorescent lipid XYC. Upon exposure of these 
+vesicles to membrane-impermeable reducing agents such as dithionite, 
+fluorophores in the external sheet of the vesicles are quenched and fluorescence
+in scramblase-free vesicles accordingly quickly drops to approximately 50% of 
+the initial value. However, for vesicles reconstituted with proteins conferring 
+a scramblase activity, fluorescence dissapears entirely, as fast 
+scramblase-mediated equilibration between outer (exposed) and inner (protected)
+sheet of the vesicle membrane renders all fluorescent lipids accessible to 
+reduction. By titration of the protein amount reconstituted into the vesicle 
+membranes it is thus possible to characterize scramblases and probe their 
+activity. Beyond functional validation of candidate scramblases 
+<CITE OPSIN, Birgit>, the assay has for example also been used to characterize 
+the stoichiometry of scramblase homo-multimers reconstituting into the vesicles
+<CITE BIRGIT>.
+
+From the identification of baseline and post-reduction fluorescense from 
+fluorometer-generated spectra, via the calculation of the underlying statistics
+and through publication-grade representation of the results, data analysis in 
+the context of this assay has until now involved an extensive series of manual 
+steps, at most supported by spread sheet calculation facilities. Based on the
+`R` free software environment for statistical computing and graphics <CITE CORE>
+and prominently drawing on the power and elegance of the `ggplot2` plotting 
+system <CITE the book>, we here provide `flippant` a comprehensive package
+covering fast, reproducible data analysis and graphing for scramblase assays 
+from raw fluorescense spectra with a simple parametrizing spreadsheet as the
+sole required input.
+
 #Main Features

### 2015-09-16 inst/manuscript/manuscript.rmd
Provide funding info (Anant will have to check);

@@
 J.G., R.J.C. and the Proteomics Core at WCMC-Q were supported by ``Biomedical 
+Research Program'' funds at Weill Cornell Medical College in Qatar, a program 
+funded by Qatar Foundation. B.P. was supported by a grant from Qatar National 
+Research Fund’s National Priority Research Program (5-669-1-112) to J.G. and
+A.K.M.
+
 #Acknowledgements

### 2015-09-16 inst/manuscript/manuscript.rmd
Fix sheet/leaflet terminaology error;

@@
 Scramblases are proteins mediating the mass-action driven equilibration of 
-lipids between the sheets of lipid bilayers representing biological membranes
 <CITE SOME REVIEW>. Indipendent of energy equivalents such as ATP they 
+lipids between the leaflets of lipid bilayers representing biological membranes
 facilitate this ``flipping'' by providing a mechanism of transition through the 
@@
 equilibration of the ubiquitous phosphoglycerolipids across the membrane of the 
-endoplasmic reticulum, where they are synthesized in the cytoplasmic sheet, 
+endoplasmic reticulum, where they are synthesized in the cytoplasmic leaflet, 
 have yet to be identified <CITE SOMETHING>, there has been much recent progress 

### 2015-09-16 inst/manuscript/manuscript.rmd
Provide proper citing facilities and start to fill in the citations; also add some clarification comments to ask Birgit;

@@
     fig_caption: yes
-#bibliography: flippant.bib
-#csl: bioinformatics.csl
+bibliography: flippant.bib
+csl: bioinformatics.csl
 ---
@@
 Scramblases are proteins mediating the mass-action driven equilibration of 
-<CITE SOME REVIEW>. Indipendent of energy equivalents such as ATP they 
 lipids between the leaflets of lipid bilayers representing biological membranes
+[@waechter_flippases_2013]. Indipendent of energy equivalents such as ATP they 
 facilitate this ``flipping'' by providing a mechanism of transition through the 
@@
 in scramblase identification and characterization. Molecules shown to have 
-scramblase activity include opsin/rhodopsin <CITE INDU, MIKE, BIRGIT>, X <CITE> 
-and Y <CITE>.
+scramblase activity include opsin/rhodopsin 
+[@menon_opsin_2011;@goren_constitutive_2014], TMEM16 
+[@malvezzi_ca2-dependent_2013], $\beta$ 2-adrenergic and adenosine A2A 
+receptors [both @goren_constitutive_2014]. **Would be good to include/replace some 
+with non-in-house identifications/characterizations. What else is out there?**
 
-Following work by X <CITE>, Y<CITE> and Z<CITE>, we have develloped an assay 
-suited to characterize scramblase activity in purified proteins and protein 
-extracts <CITE OPSIN PAPER, MIKE, BIRGIT>, based on the reconstitution of 
-scramblases or candidate proteins into large synthetic vesicles with a lipid
-composition that includes the fluorescent lipid XYC. Upon exposure of these 
-vesicles to membrane-impermeable reducing agents such as dithionite, 
-fluorophores in the external sheet of the vesicles are quenched and fluorescence
-in scramblase-free vesicles accordingly quickly drops to approximately 50% of 
-the initial value. However, for vesicles reconstituted with proteins conferring 
-a scramblase activity, fluorescence dissapears entirely, as fast 
-scramblase-mediated equilibration between outer (exposed) and inner (protected)
-sheet of the vesicle membrane renders all fluorescent lipids accessible to 
-reduction. By titration of the protein amount reconstituted into the vesicle 
-membranes it is thus possible to characterize scramblases and probe their 
-activity. Beyond functional validation of candidate scramblases 
-<CITE OPSIN, Birgit>, the assay has for example also been used to characterize 
-the stoichiometry of scramblase homo-multimers reconstituting into the vesicles
-<CITE BIRGIT>.
+To interrogate factors of this functional class, we have developed a biochemical 
+assay suited to characterize scramblase activity in purified proteins and protein 
+extracts [@chang_chemical_2004], based on the reconstitution of scramblases or 
+candidate proteins into large synthetic vesicles with a lipid
+composition that includes nitrobenzoxadiazole (NBD) labeled fluorescent lipids.
+Upon exposure of these vesicles to membrane-impermeable reducing agents such as 
+dithionite, fluorophores in the external leaflet of the vesicles are quenched and 
+fluorescence in scramblase-free vesicles accordingly quickly drops to 
+approximately 50% of the initial value. However, for vesicles reconstituted with
+proteins conferring a scramblase activity, fluorescence dissapears entirely, as
+fast scramblase-mediated equilibration between outer (exposed) and inner
+(protected) leaflet of the vesicle membrane renders all fluorescent lipids
+accessible to reduction. By titration of the protein amount reconstituted into
+the vesicle membranes it is thus possible to characterize scramblases and probe
+their activity. Beyond the identification of scramblase activities in crude 
+membrane preparations [@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
+functional validation of candidate scramblases [@menon_opsin_2011;@goren_constitutive_2014;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014],
+the assay has for example 
+also been used to characterize the stoichiometry of scramblase homo-multimers 
+reconstituting into the vesicles [@ploier_perturbed_submitted] and probe the 
+ATP-dependence of flippases, molecules that under energy-consumption flip lipids
+against a concentration gradient between bilayer leaflets [@soupene_atp8a1_2008].
+**Are you aware of further use? More adoption would fortify the need for the package ...**
 
@@
 the context of this assay has until now involved an extensive series of manual 
-steps, at most supported by spread sheet calculation facilities. Based on the
-`R` free software environment for statistical computing and graphics <CITE CORE>
+steps, at most supported by spreadsheet calculation facilities [see the 
+supplementary material of @menon_opsin_2011 for extensive stepwise discussion]. Based on the
+`R` free software environment for statistical computing and graphics [@r_core_team_r:_2015]
 and prominently drawing on the power and elegance of the `ggplot2` plotting 
-system <CITE the book>, we here provide `flippant` a comprehensive package
+system [@wickham_ggplot2_2009], we here provide `flippant`, a comprehensive package
 covering fast, reproducible data analysis and graphing for scramblase assays 
@@
 Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+#References

### 2015-09-16 inst/manuscript/manuscript.rmd
Paraphrasing to avoid doublication ("from") and clarifiy ("user" input);

@@
 
-From the identification of baseline and post-reduction fluorescense from 
+Starting with the identification of baseline and post-reduction fluorescense from 
 fluorometer-generated spectra, via the calculation of the underlying statistics
@@
 from raw fluorescense spectra with a simple parametrizing spreadsheet as the
-sole required input.
+sole required user input.
 

### 2015-09-16 inst/manuscript/manuscript.rmd
Purge template remnants put originally in place by RStudio;

@@
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r}
-summary(cars)
-```
-
-You can also embed plots, for example:
-
-```{r, echo=FALSE}
-plot(cars)
-```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
 #References

### 2015-09-16 inst/manuscript/manuscript.rmd
Finalize reference addition to first intro draft and keep paraphrasing editing; This is the first version sent to Birgit for feedback;

@@
 Scramblases are proteins mediating the mass-action driven equilibration of 
-lipids between the leaflets of lipid bilayers representing biological membranes
+lipids between the leaflets of lipid bilayers that constitute biological membranes
 [@waechter_flippases_2013]. Indipendent of energy equivalents such as ATP they 
-facilitate this ``flipping'' by providing a mechanism of transition through the 
-hydrophobic environment of membranes to polar lipid head groups, thus 
-reducing the massive energetic cost that process would carry otherwise <CITE 
-ANANT HALF TIME>. While the underlying molecular mechanisms remain enigmatic 
-<CITE SOMETHING>, and molecules supporting flipping processes as central as the 
-equilibration of the ubiquitous phosphoglycerolipids across the membrane of the 
-endoplasmic reticulum, where they are synthesized in the cytoplasmic leaflet, 
-have yet to be identified <CITE SOMETHING>, there has been much recent progress 
-in scramblase identification and characterization. Molecules shown to have 
-scramblase activity include opsin/rhodopsin 
-[@menon_opsin_2011;@goren_constitutive_2014], TMEM16 
+facilitate this ``flipping'' by providing to polar lipid head groups a mechanism
+of transition through the hydrophobic environment of membranes, thus reducing 
+the massive energetic cost that process would carry otherwise 
+[@kornberg_inside-outside_1971]. While the underlying molecular mechanisms in 
+many cases remain enigmatic [for a discussion including exceptions see @ernst_phospholipid_2015], and molecules supporting flipping processes as 
+central as the equilibration of the ubiquitous phosphoglycerolipids across the 
+membrane of the endoplasmic reticulum, where they are synthesized in the 
+cytoplasmic monolayer, have yet to be identified **(I was looking for a recent 
+citation that clearly spelled that out - in vain. Do you have a proposal?)**, 
+there has been much recent progress in scramblase identification and 
+characterization. Molecules shown to have scramblase activity include 
+opsin/rhodopsin [@menon_opsin_2011;@goren_constitutive_2014], TMEM16 
 [@malvezzi_ca2-dependent_2013], $\beta$ 2-adrenergic and adenosine A2A 
@@
 assay suited to characterize scramblase activity in purified proteins and protein 
-extracts [@chang_chemical_2004], based on the reconstitution of scramblases or 
-candidate proteins into large synthetic vesicles with a lipid
+extracts [@chang_chemical_2004] based on the reconstitution of scramblases or 
+candidate proteins into synthetic liposomes with a lipid
 composition that includes nitrobenzoxadiazole (NBD) labeled fluorescent lipids.
-Upon exposure of these vesicles to membrane-impermeable reducing agents such as 
-dithionite, fluorophores in the external leaflet of the vesicles are quenched and 
-fluorescence in scramblase-free vesicles accordingly quickly drops to 
-approximately 50% of the initial value. However, for vesicles reconstituted with
-proteins conferring a scramblase activity, fluorescence dissapears entirely, as
+Upon exposure of these liposomes to membrane-impermeable reducing agents such as 
+dithionite, fluorophores in the external leaflet are quenched and fluorescence in scramblase-free liposomes accordingly quickly drops to approximately 50% of the 
+initial value. However, for proteoliposomes reconstituted with proteins 
+conferring a scramblase activity, fluorescence dissapears entirely, as
 fast scramblase-mediated equilibration between outer (exposed) and inner
-(protected) leaflet of the vesicle membrane renders all fluorescent lipids
+(protected) leaflet of the bilayer renders all fluorescent lipids
 accessible to reduction. By titration of the protein amount reconstituted into
-the vesicle membranes it is thus possible to characterize scramblases and probe
+the liposome membranes it is thus possible to characterize scramblases and probe
 their activity. Beyond the identification of scramblase activities in crude 
 membrane preparations [@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
-functional validation of candidate scramblases [@menon_opsin_2011;@goren_constitutive_2014;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014],
-the assay has for example 
-also been used to characterize the stoichiometry of scramblase homo-multimers 
-reconstituting into the vesicles [@ploier_perturbed_submitted] and probe the 
-ATP-dependence of flippases, molecules that under energy-consumption flip lipids
-against a concentration gradient between bilayer leaflets [@soupene_atp8a1_2008].
-**Are you aware of further use? More adoption would fortify the need for the package ...**
+functional validation of candidate scramblases [@menon_opsin_2011;@goren_constitutive_2014;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014], the assay has also been used to characterize the stoichiometry of scramblase homo-multimers reconstituting into the proteoliposomes
+[@ploier_perturbed_submitted] and probe the ATP-dependence of flippases, 
+molecules that under energy-consumption flip lipids against a concentration 
+gradient between bilayer leaflets [@soupene_atp8a1_2008].
+**Are you aware of further use? More adoption would fortify the need for the 
+package ...**
 
-Starting with the identification of baseline and post-reduction fluorescense from 
-fluorometer-generated spectra, via the calculation of the underlying statistics
-and through publication-grade representation of the results, data analysis in 
-the context of this assay has until now involved an extensive series of manual 
-steps, at most supported by spreadsheet calculation facilities [see the 
-supplementary material of @menon_opsin_2011 for extensive stepwise discussion]. Based on the
-`R` free software environment for statistical computing and graphics [@r_core_team_r:_2015]
-and prominently drawing on the power and elegance of the `ggplot2` plotting 
-system [@wickham_ggplot2_2009], we here provide `flippant`, a comprehensive package
-covering fast, reproducible data analysis and graphing for scramblase assays 
-from raw fluorescense spectra with a simple parametrizing spreadsheet as the
-sole required user input.
+Starting with the identification of baseline and post-reduction fluorescense 
+from fluorometer-generated spectra, via the calculation of the underlying 
+statistics and through publication-grade representation of the results, data 
+analysis in the context of this assay has until now involved an extensive series
+of manual steps, at most supported by spreadsheet calculation facilities
+[see the supplementary material of @menon_opsin_2011 for extensive stepwise discussion].
+Based on the `R` free software environment for statistical computing and 
+graphics [@r_core_team_r:_2015] and prominently drawing on the power and 
+elegance of the `ggplot2` plotting system [@wickham_ggplot2_2009], we here 
+provide `flippant`, a package that comprehensively, fast and reproducibly covers
+all data analysis and graphing needs from raw fluorescense spectra produced by 
+scramblase assays. A simple parametrizing spreadsheet is the sole required user 
+input.
 

### 2015-09-16 inst/manuscript/manuscript.rmd
Typo fixing;

@@
 lipids between the leaflets of lipid bilayers that constitute biological membranes
-[@waechter_flippases_2013]. Indipendent of energy equivalents such as ATP they 
+[@waechter_flippases_2013]. Independent of energy equivalents such as ATP they 
 facilitate this ``flipping'' by providing to polar lipid head groups a mechanism
@@
 initial value. However, for proteoliposomes reconstituted with proteins 
-conferring a scramblase activity, fluorescence dissapears entirely, as
+conferring a scramblase activity, fluorescence disappears entirely, as
 fast scramblase-mediated equilibration between outer (exposed) and inner
@@
 
-Starting with the identification of baseline and post-reduction fluorescense 
+Starting with the identification of baseline and post-reduction fluorescence 
 from fluorometer-generated spectra, via the calculation of the underlying 
@@
 of manual steps, at most supported by spreadsheet calculation facilities
-[see the supplementary material of @menon_opsin_2011 for extensive stepwise discussion].
+[see the supplementary material of @menon_opsin_2011 for extensive step-wise discussion].
 Based on the `R` free software environment for statistical computing and 
@@
 provide `flippant`, a package that comprehensively, fast and reproducibly covers
-all data analysis and graphing needs from raw fluorescense spectra produced by 
+all data analysis and graphing needs from raw fluorescence spectra produced by 
 scramblase assays. A simple parametrizing spreadsheet is the sole required user 

### 2015-09-16 inst/manuscript/manuscript.rmd
Add a document-leading R section for loading of packages, variable precalculations etc.; Currently package dependencies of flippant are retreived and formated on the fly, as well as 'mvbutils' loaded;

@@
 :   To whom correspondence should be addressed: jog2030@qatar-med.cornell.edu
+
+```{r, echo = FALSE}
+library(magrittr)
+library(stringi)
+flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
+  unlist(use.names = FALSE) %>%
+  stri_split(regex = ",", omit_empty = TRUE) %>%
+  unlist(use.names = FALSE) %>%
+  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
+  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
+  tail(n=length(.) - 1) %>%
+  sort() %>%
+  ( function(x){
+    paste0(
+      c(
+        "`",
+        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
+        "` and `",
+        tail(x, n = 1),
+        "`"),
+      collapse = "")} )
+
+library(mvbutils)
+```
 

### 2015-09-16 inst/manuscript/manuscript.rmd
Settle on title and structure of 'Installation, Input Requirements and Main Features' section; First drafts of "Installation" and "Input Data" subsections;

@@
 
-#Main Features
+#Installation, Input Requirements and Main Features
+##Installation
+`flippant` has been integrated into the `bioconductor` collection of tools for 
+biomedical data analysis [@huber_orchestrating_2015] and is thus installable and
+loadable as follows from within a functioning `R` environment:
+```{r eval = FALSE}
+source("http://bioconductor.org/biocLite.R")
+biocLite(pkgs = "flippant")
+library(flippant)
+```
+The package depends on the following, automatically satisfied extensions to `R`
+base functionality: `r flippant_dependencies`
+
+##Input Data
+To analyse raw data stemming from dithionite scramblase assays, `flippant` 
+requires for each data point information as the path to the 
+fluorometer-generated spectrum, the amount of protein used to reconstitute 
+proteoliposomes, the volume used in the assay before and after addition of 
+dithionite (to calculate a volume correction factor), the amount of lips 
+present (to calculate a proteine to phospholipid ratio or PPR) etc. The 
+following function generates a spreadsheet program-compatible tab-delimited 
+`ASCII` template including column names, commentary, expected data type and the 
+default used when ommited, supporting the user in providing the data needed in 
+one table row per data point.
+```{r echo = FALSE, comment = ""}
+make.usage.section("scramblaseAssayInputTemplate", env = asNamespace("flippant"))
+```
+The application agnostic tab-delimited format must be maintained for the 
+completed table, which is subjected to extensive input checks when read by 
+`flippant`.
+
+Spectral input data is read by `flippant` using the information provided in the
+input template raw spectra produced by QuantaMaster fluorometer instruments 
+(Photon Technology International,Inc., Edison, New Jersey) running software 
+versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as simple generic
+tab-delimited spectrum representing file format with time (s) and fluorescence 
+intensity containing columns are currently supported. File type determination is
+handled algorythmically.
+
+##Graphic Representation of Spectral Traces
+```{r echo = FALSE, comment = ""}
+make.usage.section("scramblaseAssayTraces", env = asNamespace("flippant"))
+```
+
+##Producing Protein To Phospholipid (PPR) Plots
+```{r echo = FALSE, comment = ""}
+make.usage.section("scramblaseAssayPlot", env = asNamespace("flippant"))
+```
+
+##Non-graphical Output of Analysis Results
+```{r echo = FALSE, comment = ""}
+make.usage.section("scramblaseAssayStats", env = asNamespace("flippant"))
+```
 

### 2015-09-16 R/onAttach.R
Eliminate dependency on internal "pdapbase" package;

@@ -1,17 +1,0 @@
-#' @importFrom pdapbase checkVersion
-.onAttach <- function(...){
-  vC <- checkVersion(
-    expectedR = package_version("3.2.2"),
-    expectedPackages = list(
-      assertive = package_version("0.3-0"),
-      ggplot2 = package_version("1.0.1"),
-      nlmrt = package_version("2013-9.25"),
-      pdapbase = package_version("0.5.2"),
-      plyr = package_version("1.8.3"),
-      RcppRoll = package_version("0.2.2"),
-      splus2R = package_version("1.2-0"),
-      wmtsa = package_version("2.0-0")))
-  if(!is.null(vC)){
-    packageStartupMessage(vC)
-  }
-}

### 2015-09-16 R/parseManualOutput.R
Fix incorrect column name listing;

@@ -3,7 +3,7 @@
 #' format.
 #' @details A helper function to \code{\link{parseFluorimeterOutput}}.
 #' The file in question is supposed to contain a tab-delimited table
-#' with the columns \code{Time (sec)} and \code{Blank}.
+#' with the columns \code{Time (sec)} and \code{Fluorescense Intensity}.
 #' @param x \code{\link{character}} vector resulting from 
 #' \code{\link{readLines}} of the corresponding data file.
 #' @return See \code{\link{parseFluorimeterOutput}}.

### 2015-09-17 inst/manuscript/manuscript.rmd
Suppress package startup messages in R preamble;

@@
 ```{r, echo = FALSE}
-library(magrittr)
-library(stringi)
+suppressMessages(
+  library(magrittr))
+suppressMessages(
+  library(stringi))
 flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%

### 2015-09-17 inst/manuscript/manuscript.rmd
Fix erroneous citation doublication;

@@
 membrane preparations [@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
-functional validation of candidate scramblases [@menon_opsin_2011;@goren_constitutive_2014;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014], the assay has also been used to characterize the stoichiometry of scramblase homo-multimers reconstituting into the proteoliposomes
+functional validation of candidate scramblases [@menon_opsin_2011;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014], the 
+assay has also been used to characterize the stoichiometry of scramblase 
+homo-multimers reconstituting into the proteoliposomes 
 [@ploier_perturbed_submitted] and probe the ATP-dependence of flippases, 

### 2015-09-17 inst/manuscript/manuscript.rmd
Roearganize structure, including a data processing section;

@@
 
-#Installation, Input Requirements and Main Features
-##Installation
+#Installation
 `flippant` has been integrated into the `bioconductor` collection of tools for 
@@
 
-##Input Data
+#Input Data and Data Processing
 To analyse raw data stemming from dithionite scramblase assays, `flippant` 
@@
 following function generates a spreadsheet program-compatible tab-delimited 
+#Main Features
+##Template Generation for Data Input
+The following function generates a spreadsheet program-compatible tab-delimited 
 `ASCII` template including column names, commentary, expected data type and the 

### 2015-09-17 inst/manuscript/manuscript.rmd
Ensure code highlighting of function calls (knitr author);

@@
 
-library(mvbutils)
 ```
@@
 `ASCII` template including column names, commentary, expected data type and the 
-default used when ommited, supporting the user in providing the data needed in 
-one table row per data point.
-```{r echo = FALSE, comment = ""}
-make.usage.section("scramblaseAssayInputTemplate", env = asNamespace("flippant"))
+default used when ommited, supporting the user in providing the data needed.
+```{r, code=formatR::usage('scramblaseAssayInputTemplate'), eval=FALSE}
 ```
@@
 ##Graphic Representation of Spectral Traces
-```{r echo = FALSE, comment = ""}
-make.usage.section("scramblaseAssayTraces", env = asNamespace("flippant"))
+```{r, code = formatR::usage('scramblaseAssayTraces'), eval = FALSE}
 ```
@@
 ##Producing Protein To Phospholipid (PPR) Plots
-```{r echo = FALSE, comment = ""}
-make.usage.section("scramblaseAssayPlot", env = asNamespace("flippant"))
+```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
 ```
@@
 ##Non-graphical Output of Analysis Results
-```{r echo = FALSE, comment = ""}
-make.usage.section("scramblaseAssayStats", env = asNamespace("flippant"))
+```{r, code = formatR::usage('scramblaseAssayStats'), eval = FALSE}
 ```

### 2015-09-17 inst/manuscript/manuscript.rmd
Continuous editing ...;

@@
 `flippant` has been integrated into the `bioconductor` collection of tools for 
-biomedical data analysis [@huber_orchestrating_2015] and is thus installable and
-loadable as follows from within a functioning `R` environment:
-```{r eval = FALSE}
+biomedical data analysis [@huber_orchestrating_2015] and is thus install- and
+loadable as follows from within a functional `R` environment:
+```{r, eval = FALSE}
 source("http://bioconductor.org/biocLite.R")
@@
 ```
-The package depends on the following, automatically satisfied extensions to `R`
-base functionality: `r flippant_dependencies`
+The package depends on the following packaged extensions to `R` base 
+functionality, which are automatically satisfied on installation: 
+`r flippant_dependencies`.
 

### 2015-09-17 inst/manuscript/manuscript.rmd
Major progress on data flow section (from package documentation);

@@
 proteoliposomes, the volume used in the assay before and after addition of 
-dithionite (to calculate a volume correction factor), the amount of lips 
-present (to calculate a proteine to phospholipid ratio or PPR) etc. The 
-following function generates a spreadsheet program-compatible tab-delimited 
+dithionite (to calculate a volume correction factor), the amount of lipids 
+present (to calculate a protein to phospholipid ratio or PPR) etc. The user 
+supplies this information in one row of a spreadsheet (see below for supporting functionality).
+
+Spectral input data is read by `flippant` using the information provided in the
+input template. Raw spectra produced by QuantaMaster fluorometer instruments 
+(Photon Technology International, Inc., Edison, New Jersey) running software 
+versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as a simple 
+generic tab-delimited spectrum representing file format with time (s) and 
+fluorescence intensity representing columns are currently supported. 
+File type determination is handled algorythmically.
+
+Based on @menon_opsin_2011 and @goren_constitutive_2014, <CHECK THAT THERE'S INFO IN THE LATTER> data is processed as 
+follows. Input is format checked and defaults are injected for facultative 
+parameters/columns as appropriate. Fluorescence spectra are parsed, including 
+determination of when dithionite was added to the sample using `wmtsa`-supplied
+methodology <CITE AND MORE DETAIL> and resetting the acquisition time 
+accordingly. The zero time point henceforth corresponds to the time of addition. 
+Pre-dithionite-addition baseline fluorescence $F_{\text{baseline}}$ is 
+determined for each spectrum by averaging (median) over the ten values preceding
+dithionite addition. Post-dithinonite-addition minimum fluorescence 
+$F_{\text{min}}$ is analogously calculated from the last ten datapoints after 
+the default 400 s or the timepoint of measurement supplied by the user in the 
+parameter file. $F_{\text{min}}$ is volume-corrected based on supplied reaction 
+volumes
+with and without dithionite and for each spectrum/datapoint a fluorescence 
+reduction is calculated as follows:
+$$
+y_{\text{raw}} = 1 - \frac{F_{\text{min}}}{F_{\text{baseline}}}
+$$
+<!--
+Data are split for parallel treatment using a combined Experimental Series/Experiment identifier (see above).
+
+A Relative Fluorescence Reduction is calculated in comparison to the liposomes-only/no-protein control).
+
+A Protein per Phospholipid (mg/mmol) ratio (PPR) is calculated.
+
+A probability for a liposome holding ≤ 1 scramblase molecules is calculated using
+
+(y - y0)/(ymax - y0)
+
+where y is the Relative Fluorescence Reduction and y0 is the Relative Fluorescence Reduction in an experiment without addition of protein extract.
+Depending on the scaleTo parameter, ymax is either the maximal Relative Fluorescence Reduction in the series (scaleTo = "data") or derived from a mono-exponential fit to the data (scaleTo = "model").
+The latter (default) is a precaution for the case where the protein/phospholipid titration did not reach the plateau of the saturation curve.
+
+A monoexponential curve is fitted unsig nlxb to either
+
+p(≤ 1) = b - c*exp(-PPR/a)
+
+(if forceThroughOrigin = FALSE) or
+
+p(≤ 1) = b * (1 - exp(-PPR/a))
+
+(if forceThroughOrigin = TRUE).
+
+Data split apart above are recombined and a ggplot object is assembled with the following layers:
+
+Lines (geom_line) representing the monoexponential fit(s). color is used to differentiate Experimental Series.
+
+Segments (geom_segment) representing the PPR at which the fit constant a is equal to PPR.
+This tau value has the implication that at this PPR all vesicles on average have one scramblase and 63% have one or more (i.e.
+are active).
+color is used to differentiate Experimental Series.
+
+Points (geom_point) representing the corresponding datapoints. color is used to differentiate Experimental Series.
+
+Plots are finally facet_wraped by Experiment and labels adjusted cosmetically.-->
+
 #Main Features
@@
 `flippant`.
-
-Spectral input data is read by `flippant` using the information provided in the
-input template raw spectra produced by QuantaMaster fluorometer instruments 
-(Photon Technology International,Inc., Edison, New Jersey) running software 
-versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as simple generic
-tab-delimited spectrum representing file format with time (s) and fluorescence 
-intensity containing columns are currently supported. File type determination is
-handled algorythmically.
 

### 2015-09-17 inst/manuscript/manuscript.rmd
Finish a first draft of the Data Analysis flow;

@@
 
-Based on @menon_opsin_2011 and @goren_constitutive_2014, <CHECK THAT THERE'S INFO IN THE LATTER> data is processed as 
+Based on @menon_opsin_2011 and @goren_constitutive_2014, data is processed as 
 follows. Input is format checked and defaults are injected for facultative 
 parameters/columns as appropriate. Fluorescence spectra are parsed, including 
-determination of when dithionite was added to the sample using `wmtsa`-supplied
-methodology <CITE AND MORE DETAIL> and resetting the acquisition time 
-accordingly. The zero time point henceforth corresponds to the time of addition. 
+determination of when dithionite was added to the sample using peak detection by
+continuous wavelet transformation as implemented by the `wmtsa` `R` package 
+[@percival_wavelet_2000;@constantine_wmtsa:_2013] and resetting the acquisition 
+time accordingly. The zero time point henceforth corresponds to the time of 
+addition. 
 Pre-dithionite-addition baseline fluorescence $F_{\text{baseline}}$ is 
@@
 <!--
-Data are split for parallel treatment using a combined Experimental Series/Experiment identifier (see above).
-
-A Relative Fluorescence Reduction is calculated in comparison to the liposomes-only/no-protein control).
-
-A Protein per Phospholipid (mg/mmol) ratio (PPR) is calculated.
-
-A probability for a liposome holding ≤ 1 scramblase molecules is calculated using
-
-(y - y0)/(ymax - y0)
-
-where y is the Relative Fluorescence Reduction and y0 is the Relative Fluorescence Reduction in an experiment without addition of protein extract.
-Depending on the scaleTo parameter, ymax is either the maximal Relative Fluorescence Reduction in the series (scaleTo = "data") or derived from a mono-exponential fit to the data (scaleTo = "model").
-The latter (default) is a precaution for the case where the protein/phospholipid titration did not reach the plateau of the saturation curve.
-
-A monoexponential curve is fitted unsig nlxb to either
-
-p(≤ 1) = b - c*exp(-PPR/a)
-
-(if forceThroughOrigin = FALSE) or
-
-p(≤ 1) = b * (1 - exp(-PPR/a))
-
-(if forceThroughOrigin = TRUE).
-
-Data split apart above are recombined and a ggplot object is assembled with the following layers:
-
-Lines (geom_line) representing the monoexponential fit(s). color is used to differentiate Experimental Series.
-
-Segments (geom_segment) representing the PPR at which the fit constant a is equal to PPR.
-This tau value has the implication that at this PPR all vesicles on average have one scramblase and 63% have one or more (i.e.
-are active).
-color is used to differentiate Experimental Series.
-
-Points (geom_point) representing the corresponding datapoints. color is used to differentiate Experimental Series.
-
-Plots are finally facet_wraped by Experiment and labels adjusted cosmetically.-->
+Data are split for parallel treatment using a combined Experimental Series/Experiment identifier (see above).-->
+A relative fluorescence reduction $y$ is calculated scaled to a (required) liposomes-only/no-protein control and the probability $P_{\geq 1}$ for a 
+liposome to contain at least one scramblase molecules is calculated using
+$$
+P_{\geq 1} = \frac{(y - y_0)}{(y_{\text{max}} - y_0)}
+$$
+where $y$ is the relative fluorescence reduction for the proteoliposome 
+measurement and $y_0$ for a measurement of protein-free liposomes. 
+$y_{\text{max}}$ refers to either the maximal $y$ in the experiment or is 
+derived from a monoexponential fit to the data (default) as a precaution for the 
+case where the protein/phospholipid titration did not reach the plateau of the 
+saturation curve. The behavior is adjustable using the `scaleTo` parameter of 
+the corresponding functions (see below). Next a monoexponential curve is fitted
+to the realtionship of $P_{\geq 1}$ to the protein to phospholipid ratio (PPR; 
+(mg/mmol)), providing the scramblase-characterizing fit factor $\alpha$.
 

### 2015-09-18 inst/manuscript/manuscript.rmd
Integrate changes by Birgit;

@@
 the massive energetic cost that process would carry otherwise 
-[@kornberg_inside-outside_1971]. While the underlying molecular mechanisms in 
-many cases remain enigmatic [for a discussion including exceptions see @ernst_phospholipid_2015], and molecules supporting flipping processes as 
-central as the equilibration of the ubiquitous phosphoglycerolipids across the 
-membrane of the endoplasmic reticulum, where they are synthesized in the 
-cytoplasmic monolayer, have yet to be identified **(I was looking for a recent 
-citation that clearly spelled that out - in vain. Do you have a proposal?)**, 
-there has been much recent progress in scramblase identification and 
-characterization. Molecules shown to have scramblase activity include 
-opsin/rhodopsin [@menon_opsin_2011;@goren_constitutive_2014], TMEM16 
+[@kornberg_inside-outside_1971]. The underlying molecular mechanisms remain 
+largely enigmatic [for a discussion including exceptions see @ernst_phospholipid_2015].
+Proteins supporting flipping processes as central as the equilibration of the 
+ubiquitous phosphoglycerolipids across the membrane of the endoplasmic 
+reticulum, where they are synthesized in the cytoplasmic monolayer, have yet to 
+be identified **(I was looking for a recent 
+citation that clearly spelled that out - in vain. Do you have a proposal?)**. 
+None the less, there has been much recent progress in scramblase identification 
+and characterization. Proteins shown to have scramblase activity include 
+FtsW [@mohammadi_identification_2011], opsin/rhodopsin
+[@menon_opsin_2011;@goren_constitutive_2014], TMEM16 
 [@malvezzi_ca2-dependent_2013], $\beta$ 2-adrenergic and adenosine A2A 
-receptors [both @goren_constitutive_2014]. **Would be good to include/replace some 
-with non-in-house identifications/characterizations. What else is out there?**
+receptors [both @goren_constitutive_2014]. Extrapolating from the latter findings 
+and the opsin/rhodopsin case, we speculate that lipid scrambling may, in fact, 
+be an intrinsic property of G-protein coupled receptors in general 
+[@goren_constitutive_2014].
 
 To interrogate factors of this functional class, we have developed a biochemical 
-assay suited to characterize scramblase activity in purified proteins and protein 
+assay suited to characterize scramblase activity of purified proteins and protein 
 extracts [@chang_chemical_2004] based on the reconstitution of scramblases or 
-candidate proteins into synthetic liposomes with a lipid
-composition that includes nitrobenzoxadiazole (NBD) labeled fluorescent lipids.
-Upon exposure of these liposomes to membrane-impermeable reducing agents such as 
-dithionite, fluorophores in the external leaflet are quenched and fluorescence in scramblase-free liposomes accordingly quickly drops to approximately 50% of the 
+candidate proteins into preformed synthetic liposomes that contain trace amounts
+of nitrobenzoxadiazole (NBD) labeled fluorescent lipids.
+Upon addition of membrane-impermeable reducing agents such as dithionite to 
+these liposomes, fluorophores in the external leaflet are quenched and fluorescence in scramblase-free liposomes accordingly quickly drops to approximately 50% of the 
 initial value. However, for proteoliposomes reconstituted with proteins 

### 2015-09-18 inst/manuscript/manuscript.rmd
Keep working on the data analysis flow section;

@@
 To analyse raw data stemming from dithionite scramblase assays, `flippant` 
-requires for each data point information as the path to the 
+requires for each data point information on the path to the 
 fluorometer-generated spectrum, the amount of protein used to reconstitute 
-proteoliposomes, the volume used in the assay before and after addition of 
+proteoliposomes, the assay volume before and after addition of 
 dithionite (to calculate a volume correction factor), the amount of lipids 
 present (to calculate a protein to phospholipid ratio or PPR) etc. The user 
-supplies this information in one row of a spreadsheet (see below for supporting functionality).
+supplies this information in a spreadsheet (see below for supporting 
+functionality).
 
-Spectral input data is read by `flippant` using the information provided in the
-input template. Raw spectra produced by QuantaMaster fluorometer instruments 
+Spectral input data is read by `flippant` using the file paths provided in the
+spreadsheet. Raw spectra produced by QuantaMaster fluorometer instruments 
 (Photon Technology International, Inc., Edison, New Jersey) running software 
 versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as a simple 
-generic tab-delimited spectrum representing file format with time (s) and 
-fluorescence intensity representing columns are currently supported. 
+generic tab-delimited spectrum representing file format with time (in seconds) 
+and fluorescence intensity representing columns are currently supported. 
 File type determination is handled algorythmically.
@@
 follows. Input is format checked and defaults are injected for facultative 
-parameters/columns as appropriate. Fluorescence spectra are parsed, including 
-determination of when dithionite was added to the sample using peak detection by
-continuous wavelet transformation as implemented by the `wmtsa` `R` package 
-[@percival_wavelet_2000;@constantine_wmtsa:_2013] and resetting the acquisition 
-time accordingly. The zero time point henceforth corresponds to the time of 
-addition. 
+parameters/columns as appropriate. Fluorescence spectra are parsed. This includes 
+algorithmic determination of when dithionite was added to the sample using peak
+detection by continuous wavelet transformation as implemented in the 
+`wmtsa` `R` package [@percival_wavelet_2000;@constantine_wmtsa:_2013]. The 
+acquisition time is reset such that the zero time point henceforth corresponds 
+to the time of addition. 
 Pre-dithionite-addition baseline fluorescence $F_{\text{baseline}}$ is 
@@
 the default 400 s or the timepoint of measurement supplied by the user in the 
-parameter file. $F_{\text{min}}$ is volume-corrected based on supplied reaction 
-volumes
-with and without dithionite and for each spectrum/datapoint a fluorescence 
-reduction is calculated as follows:
+parameter spreadsheet. $F_{\text{min}}$ is volume-corrected based on supplied 
+reaction volumes with and without dithionite and for each spectrum/datapoint a 
+fluorescence reduction is calculated as follows:
 $$
@@
 $$
-<!--
-Data are split for parallel treatment using a combined Experimental Series/Experiment identifier (see above).-->
 A relative fluorescence reduction $y$ is calculated scaled to a (required) liposomes-only/no-protein control and the probability $P_{\geq 1}$ for a 

### 2015-09-18 inst/manuscript/manuscript.rmd
Load "flippant" explicitly to make code presentation work;

@@
       collapse = "")} )
-
+suppressMessages(
+  library(flippant))
 ```

### 2015-09-18 inst/manuscript/manuscript.rmd
Switch to usage of "quietly" statement in package loading;

--- 2015-09-18 inst/manuscript/manuscript.rmd
@@
 ```{r, echo = FALSE}
-suppressMessages(
-  library(magrittr))
-suppressMessages(
-  library(stringi))
+library(magrittr, quietly = TRUE)
+library(stringi, quietly = TRUE)
 flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
@@
       collapse = "")} )
-
+library(flippant, quietly = TRUE)
 ```

### 2015-09-19 inst/manuscript/manuscript.rmd
Keep on refining;

@@
 [@waechter_flippases_2013]. Independent of energy equivalents such as ATP they 
-facilitate this ``flipping'' by providing to polar lipid head groups a mechanism
-of transition through the hydrophobic environment of membranes, thus reducing 
+facilitate this ``flipping'' by providing a mechanism of transition through the 
+hydrophobic environment of membranes to polar lipid head groups, thus reducing 
 the massive energetic cost that process would carry otherwise 
@@
 
-To interrogate factors of this functional class, we have developed a biochemical 
+To interrogate this functional class of proteins, we have developed a biochemical 
 assay suited to characterize scramblase activity of purified proteins and protein 
-extracts [@chang_chemical_2004] based on the reconstitution of scramblases or 
-candidate proteins into preformed synthetic liposomes that contain trace amounts
-of nitrobenzoxadiazole (NBD) labeled fluorescent lipids.
+extracts based on the reconstitution of scramblases or candidate proteins into 
+preformed synthetic liposomes that contain trace amounts of nitrobenzoxadiazole 
+(NBD) labeled fluorescent lipids [@chang_chemical_2004].
 Upon addition of membrane-impermeable reducing agents such as dithionite to 
@@
 of manual steps, at most supported by spreadsheet calculation facilities
-[see the supplementary material of @menon_opsin_2011 for extensive step-wise discussion].
+[see @menon_opsin_2011;@goren_constitutive_2014 for extensive step-wise discussion].
 Based on the `R` free software environment for statistical computing and 
@@
 detection by continuous wavelet transformation as implemented in the 
-`wmtsa` `R` package [@percival_wavelet_2000;@constantine_wmtsa:_2013]. The 
-acquisition time is reset such that the zero time point henceforth corresponds 
-to the time of addition. 
+`wmtsa` `R` package [@percival_wavelet_2000;@constantine_wmtsa:_2013]. 
+Acquisition time is aligned for all spectra in the data set such that the zero 
+time point henceforth corresponds to the time of addition. 
 Pre-dithionite-addition baseline fluorescence $F_{\text{baseline}}$ is 
@@
 $F_{\text{min}}$ is analogously calculated from the last ten datapoints after 
-the default 400 s or the timepoint of measurement supplied by the user in the 
+a default 400 s or the timepoint of measurement supplied by the user in the 
 parameter spreadsheet. $F_{\text{min}}$ is volume-corrected based on supplied 
@@
 ##Template Generation for Data Input
-The following function generates a spreadsheet program-compatible tab-delimited 
-`ASCII` template including column names, commentary, expected data type and the 
-default used when ommited, supporting the user in providing the data needed.
+Supporting the user in providing the input data needed, the following function 
+generates a spreadsheet program-compatible tab-delimited `ASCII` template, 
+including column names, commentary, expected data type and the default used when
+ommited.
 ```{r, code=formatR::usage('scramblaseAssayInputTemplate'), eval=FALSE}

### 2015-09-19 inst/manuscript/manuscript.rmd
Add a first draft on the traces plotting function;

@@
 ##Graphic Representation of Spectral Traces
+In a first, graphical data analytics step of a scramblase assay-derived data 
+set, fluorescent spectra or traces may be plotted in publication-appropriate
+quality with acquisition time in the x- and fluorescense intensity on the y-axis
+using
 ```{r, code = formatR::usage('scramblaseAssayTraces'), eval = FALSE}
 ```
+and handing the function the path to the user assembled spreadsheet of input 
+data (`x`). The `adjust` argument to the function call serves to selectively 
+inactivate `wmtsa`-provided (see above) alignment of multiple spectra to the 
+time of dithionite addition. Acquisition time coverage of the plot may be tuned 
+by user-provided minimal (`timeMin` ) and maximal (`timeMax`) time points to be
+included.
 

### 2015-09-19 inst/manuscript/manuscript.rmd
Header reformating;

@@
 ---
-title: "`flippant` -- An `R` package for the automated  analysis of dithionite 
-  scramblase assays"
-author: "Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
-  Mike A. Goren ^‡^ and Anant K. Menon ^‡^"
-date: "September 16, 2015"
+title: '`flippant` -- An `R` package for the automated  analysis of dithionite scramblase
+  assays'
+author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^, Mike A.
+  Goren ^‡^ and Anant K. Menon ^‡^
+date: "September 19, 2015"
 output:
@@
     fig_caption: yes
+csl: bioinformatics.csl
 bibliography: flippant.bib
-csl: bioinformatics.csl
 ---

### 2015-09-19 inst/manuscript/manuscript.rmd
Finishing a first draft of the "Main Features" section;

@@
 
-##Producing Protein To Phospholipid (PPR) Plots
+##Scramblase Assay Analysis
+Plotting protein to phospholipid ratio (PPR) against the likelyhood for a given
+proteoliposome to contain one or more scramblases, the PPR plot is at the heart 
+of the analysis of dithionite scramblase assays, allowing for the visual 
+comparison of specific scramblase activity between interrogated experimental 
+series, which may e.g. be representative of protein preparations including 
+mutant protein forms or crude extracts with or without depletion of a candidate
+scramblase. 
 ```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
 ```
+allows for the complete generation of the PPR plot in publication quality from 
+the user assembled spreadsheet of input data (`x`), including automatically 
+added graphical representations of $\tau$, the PPR value equal to the fit 
+constant $\alpha$, which implies all liposomes on average carrying one 
+scramblase and 63% have one or more (i.e. are active). The behavior of the 
+function may be adjusted to use scramblase-mediated fluorescense reduction 
+normalized to either the maximum measurement in the series (`scaleTo = "data"`)
+or the plateau of an exponential fit to it (`scaleTo = "model"`; for reasoning
+see above) and whether or not to require the exponential curve fitted to the 
+data to go through the origin.
 
-##Non-graphical Output of Analysis Results
+Numeric scramblase assay results such as $\tau$ may be generated in tabular form
+using
 ```{r, code = formatR::usage('scramblaseAssayStats'), eval = FALSE}
 ```
+with the same modifying arguments to the function as for `scramblaseAssayPlot`.
 

### 2015-09-19 R/scramblaseAssayPlot.R
Document recently added parameter governing alignment at dithionite addition;

@@ -115,6 +115,9 @@
 #' @param timeMax A single \code{\link{numeric}}. If given, 
 #' \code{\link{scramblaseAssayTraces}} produces a time/x axis trimmed to
 #' this value.
+#' @param adjust A single \code{\link{logical}}, indicating of whether (default) or 
+#' not spectral traces to be plotted are algorithmically aligned at the time
+#' point of dithionite addition.
 #' @return \code{scrambalseAssayTraces} and \code{scramblaseAssayPlot} return 
 #' \code{\link{ggplot}} objects representing the raw fluorescence traces and a
 #' complete PPR plot, respectively. \code{scrambalseAssayInputTamplate} 

### 2015-09-19 inst/manuscript/manuscript.rmd
Draft intro to "Case Study" section;

@@
 #Case Study
+*Retinitis pigmentosa* is a degenerative disease of the retina, of which the 
+majority of cases is linked to mutant forms of the G-protein coupled receptor 
+rhodopsin [@mendes_mechanisms_2005]. Motivated by our recent discovery that 
+opsin/rhodopsin has scramblase activity [@menon_opsin_2011;@goren_constitutive_2014],
+we hypothesized that a class of enigmatic rhodopsin mutations, which are known
+to cause *retinitis pigmentosa* yet do not display the commonly associated 
+molecular phenotypes of impaired binding of retinal, folding and/or trafficking or 
+transducin activation, may in fact be impacted in their scramblase activity.
+This hypothesis was disproved when tested using the dithionite scramblase assay
+among other techniques. However, the same set of experiments pointed at a defect 
+in rhodopsin dimerization prior to insertion into liposomes, generating the new 
+hypothesis that the mutations may cause disease by interfering with the highly 
+ordered quarternary structure of the molecule in the retina 
+[@ploier_perturbed_submitted].
+
+`flippant`s capabilities are demonstrated here by reanalyzing the data underlying 
+Figure 5b in @ploier_perturbed_submitted.
 

### 2015-09-19 inst/manuscript/manuscript.rmd
Various typo fixes;

@@
 determined for each spectrum by averaging (median) over the ten values preceding
-dithionite addition. Post-dithinonite-addition minimum fluorescence 
-$F_{\text{min}}$ is analogously calculated from the last ten datapoints after 
-a default 400 s or the timepoint of measurement supplied by the user in the 
+dithionite addition. Post-dithionite-addition minimum fluorescence 
+$F_{\text{min}}$ is analogously calculated from the last ten data points after 
+a default 400 s or the time point of measurement supplied by the user in the 
 parameter spreadsheet. $F_{\text{min}}$ is volume-corrected based on supplied 
-reaction volumes with and without dithionite and for each spectrum/datapoint a 
+reaction volumes with and without dithionite and for each spectrum/data point a 
 fluorescence reduction is calculated as follows:
@@
 the corresponding functions (see below). Next a monoexponential curve is fitted
-to the realtionship of $P_{\geq 1}$ to the protein to phospholipid ratio (PPR; 
+to the relationship of $P_{\geq 1}$ to the protein to phospholipid ratio (PPR; 
 (mg/mmol)), providing the scramblase-characterizing fit factor $\alpha$.
@@
 including column names, commentary, expected data type and the default used when
-ommited.
+omitted.
 ```{r, code=formatR::usage('scramblaseAssayInputTemplate'), eval=FALSE}
@@
 ##Graphic Representation of Spectral Traces
-In a first, graphical data analytics step of a scramblase assay-derived data 
+In a first, graphical data analytic step of a scramblase assay-derived data 
 set, fluorescent spectra or traces may be plotted in publication-appropriate
-quality with acquisition time in the x- and fluorescense intensity on the y-axis
+quality with acquisition time in the x- and fluorescence intensity on the y-axis
 using
@@
 ##Scramblase Assay Analysis
-Plotting protein to phospholipid ratio (PPR) against the likelyhood for a given
+Plotting protein to phospholipid ratio (PPR) against the likelihood for a given
 proteoliposome to contain one or more scramblases, the PPR plot is at the heart 
@@
 scramblase and 63% have one or more (i.e. are active). The behavior of the 
-function may be adjusted to use scramblase-mediated fluorescense reduction 
+function may be adjusted to use scramblase-mediated fluorescence reduction 
 normalized to either the maximum measurement in the series (`scaleTo = "data"`)
@@
 #Funding
-J.G., R.J.C. and the Proteomics Core at WCMC-Q were supported by ``Biomedical 
+J.G., R.J.C. and the Proteomics Core at WCMC-Q are supported by ``Biomedical 
 Research Program'' funds at Weill Cornell Medical College in Qatar, a program 

### 2015-09-19 R/scramblaseAssayCalculations.R
Begin purging requirement for consistency of measurement time;

@@ -18,6 +18,7 @@ scramblaseAssayCalculations <- function(x,scaleTo,forceThroughOrigin=TRUE){
     stop("'Timepoint of Measurement (s)' is larger than the shortest spectrum 
          acquisition. Aborting.")
   } else {
+    stop("Implement individual timepoints of measurement!")
     maxAcquisitionTime <- unique(x$"Timepoint of Measurement (s)")
   }
   # Average over 10 values before dithionite addition for activity baseline

### 2015-09-19 R/scramblaseAssayInputValidation.R

@@ -111,11 +111,7 @@ scramblaseAssayInputValidation <- function(
       paste(facultativeColumnsInX$Class,collapse="', '"),
       "'.")
   }
-  ## Check "Timepoint of Measurement (s)" consistency
-  if(length(unique(x$"Timepoint of Measurement (s)")) != 1){
-    stop("Column 'Timepoint of Measurement (s)' contains multiple values. Exiting.")
-  }
-  
+
   # Check scaleTo
   scaleTo <- match.arg(
     arg=scaleTo,

### 2015-09-19 inst/manuscript/manuscript.rmd
Put in first analysis step;

@@
 ```{r, echo = FALSE}
+library(flippant, quietly = TRUE)
+library(grid, quietly = TRUE)
 library(magrittr, quietly = TRUE)
+library(multipanelfigure, quietly = TRUE)
 library(stringi, quietly = TRUE)
@@
       collapse = "")} )
-library(flippant, quietly = TRUE)
+
+tmpDir <- tempdir()
+file.path("extdata", "PloierEtAl_Data.zip") %>%
+  system.file(
+    package = "flippant",
+    mustWork = TRUE) %>%
+  unzip(
+    overwrite = TRUE,
+    exdir = tmpDir)
+
+figure1 <- multipanelfigure(
+  width = 17.22, 
+  height = 18, 
+  units = "cm", 
+  columns = 2, 
+  rows = 2)
+
+knitr::opts_chunk$set(fig.width=6.78, fig.height=6.78, warning=FALSE, message=FALSE)
 ```
@@
 `flippant`s capabilities are demonstrated here by reanalyzing the data underlying 
-Figure 5b in @ploier_perturbed_submitted.
+Figure 5b in @ploier_perturbed_submitted. The following work flow in a first 
+step plots spectral traces for all points of the data set (Figure 1A). Note that
+alorithmic alignment to the time of dithionite addition is employed (default) as
+well as custom trimming of the time axis to account for divergent acquisition 
+times between experiments.
+<!-- Fix F220CEx1_E.txt to F220CEx1_D.txt -->
+```{r, eval = FALSE}
+# Plot spectral traces (Figure 1A)
+scramblaseAssayTraces("inputTable.txt", timeMax = 350)
+```
+```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "**`flippant`-based reanalysis of data in Figure 5b from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`."}
+setwd(tmpDir)
+figure1 <- addpanel(
+  figure = figure1,
+  topPanel = 1, 
+  leftPanel = 1, 
+  rightPanel = 2, 
+  panel = scramblaseAssayTraces("inputTable.txt", timeMax = 350)
+)
+grid.draw(figure1)
+```
 

### 2015-09-19 R/scramblaseAssayCalculations.R
Implement usage of individual timepoints of measurement;

@@ -18,8 +18,7 @@ scramblaseAssayCalculations <- function(x,scaleTo,forceThroughOrigin=TRUE){
     stop("'Timepoint of Measurement (s)' is larger than the shortest spectrum 
          acquisition. Aborting.")
   } else {
-    stop("Implement individual timepoints of measurement!")
-    maxAcquisitionTime <- unique(x$"Timepoint of Measurement (s)")
+    maxAcquisitionTime <- max(x$"Timepoint of Measurement (s)")
   }
   # Average over 10 values before dithionite addition for activity baseline
   x$"Baseline Fluorescence" <- vapply(
@@ -31,13 +30,15 @@ scramblaseAssayCalculations <- function(x,scaleTo,forceThroughOrigin=TRUE){
     1)
   # Average over last 10 values (in common time range) for activity
   x$"Minimum Fluorescence" <- vapply(
-    spectralData,
+    seq_along(spectralData),
     function(z){
-      stopIndexForAveraging <- max(which(z$Data$Time.in.sec <= maxAcquisitionTime))
+      stopIndexForAveraging <- max(
+        which(
+          spectralData[[z]]$Data$Time.in.sec <= x[z,"Timepoint of Measurement (s)"]))
       indexesForAveraging <- seq(
         from=stopIndexForAveraging-9,
         to=stopIndexForAveraging)
-      return(median(z$Data$Fluorescence.Intensity[indexesForAveraging],na.rm=TRUE))
+      return(median(spectralData[[z]]$Data$Fluorescence.Intensity[indexesForAveraging],na.rm=TRUE))
     },
     1)
   # Apply volume correction factors as needed

### 2015-09-21 R/scramblaseAssayCalculations.R
Adapt error message to new (individual) implementation;

@@ -15,8 +15,8 @@ scramblaseAssayCalculations <- function(x,scaleTo,forceThroughOrigin=TRUE){
   }
   maxAcquisitionTime <- vapply(spectralData,function(y){y$Max.Acquisition.Time.in.sec},1)
   if(any(maxAcquisitionTime < x$"Timepoint of Measurement (s)")){
-    stop("'Timepoint of Measurement (s)' is larger than the shortest spectrum 
-         acquisition. Aborting.")
+    stop("At least one 'Timepoint of Measurement' is larger than the 
+      corresponding spectrum acquisition. Aborting.")
   } else {
     maxAcquisitionTime <- max(x$"Timepoint of Measurement (s)")
   }

### 2015-09-21 R/scramblaseAssayPlot.R
Fix a missing "setwd" in the example section;

@@ -147,9 +147,10 @@
 #'     mustWork = TRUE),
 #'   overwrite = TRUE,
 #'   exdir = tmpDir)
+#' setwd(tmpDir)
 #' # Plot the spectal traces
 #' scramblaseAssayTraces(
-#'   file.path(tmpDir, "inputTable.txt"),
+#'   "inputTable.txt",
 #'   timeMax = 350)
 #' stop("Add example using actually published data.")
 scramblaseAssayPlot <- function(x, scaleTo=c("model","data"),forceThroughOrigin=TRUE){

### 2015-09-21 R/scramblaseAssayTraces.R
Clearer axis labeling;

@@ -86,7 +86,7 @@ baseFunctionScramblaseAssayTraces <- function(
   # Prettify
   plotOutput <- plotOutput +
     labs(
-      x="Time (s)",
+      x="Acquisition Time (s)",
       y="Relative Fluorescence Intensity",
       colour=expression("PPR "*bgroup("(",frac("mg","mmol"),")")))
   # Facetting

### 2015-09-21 inst/manuscript/manuscript.rmd
clarify knitr options;
More edits/typo fixing;

@@
 
-knitr::opts_chunk$set(fig.width=6.78, fig.height=6.78, warning=FALSE, message=FALSE)
+knitr::opts_chunk$set(
+  fig.width=6.78, 
+  fig.height=6.78, 
+  warning=FALSE, 
+  message=FALSE,
+  dev = 'pdf')
 ```
@@
 
-To interrogate this functional class of proteins, we have developed a biochemical 
-assay suited to characterize scramblase activity of purified proteins and protein 
-extracts based on the reconstitution of scramblases or candidate proteins into 
-preformed synthetic liposomes that contain trace amounts of nitrobenzoxadiazole 
-(NBD) labeled fluorescent lipids [@chang_chemical_2004].
+To interrogate scramblases as a functional class of proteins, we have developed 
+a biochemical assay suited to characterize scramblase activity of purified 
+proteins and protein extracts based on the reconstitution of scramblases or 
+candidate proteins into preformed synthetic liposomes that contain trace amounts
+of nitrobenzoxadiazole (NBD) labeled fluorescent lipids [@chang_chemical_2004].
 Upon addition of membrane-impermeable reducing agents such as dithionite to 
@@
 dithionite addition. Post-dithionite-addition minimum fluorescence 
-$F_{\text{min}}$ is analogously calculated from the last ten data points after 
-a default 400 s or the time point of measurement supplied by the user in the 
-parameter spreadsheet. $F_{\text{min}}$ is volume-corrected based on supplied 
-reaction volumes with and without dithionite and for each spectrum/data point a 
-fluorescence reduction is calculated as follows:
+$F_{\text{min}}$ is analogously calculated from the last ten data points before 
+(and including) a default 400 s or the time point of measurement supplied by the
+user in the parameter spreadsheet. $F_{\text{min}}$ is volume-corrected based on
+supplied reaction volumes with and without dithionite and for each spectrum/data
+point a fluorescence reduction is calculated as follows:
 $$
@@
 #Case Study
-*Retinitis pigmentosa* is a degenerative disease of the retina, of which the 
-majority of cases is linked to mutant forms of the G-protein coupled receptor 
+*Retinitis pigmentosa* is a degenerative disease of the retina, the majority of 
+cases of which is linked to mutant forms of the G-protein coupled receptor 
 rhodopsin [@mendes_mechanisms_2005]. Motivated by our recent discovery that 

### 2015-09-21 inst/manuscript/manuscript.rmd
Fix citing details as provided by Birgit Ploier;
Clean up knittr options;
More careful multipanel figure formatting;

@@
   columns = 2, 
-  rows = 2)
+  rows = 2,
+  interPanelSpacing = 0.25)
 
 knitr::opts_chunk$set(
-  fig.width=6.78, 
-  fig.height=6.78, 
-  warning=FALSE, 
-  message=FALSE,
-  dev = 'pdf')
+  fig.width = 6.78, 
+  fig.height = 7.09, 
+  warning = FALSE, 
+  message = FALSE)
 ```
@@
 Research Fund’s National Priority Research Program (5-669-1-112) to J.G. and
-A.K.M.
+A.K.M., as well as by the Austrian Science Fund (FWF), project J3686-B21.
 

### 2015-09-21 inst/manuscript/manuscript.rmd
Start work on summary;

@@
 library(magrittr, quietly = TRUE)
+library(microbenchmark, quietly = TRUE)
 library(multipanelfigure, quietly = TRUE)
@@
 #Conclusion
+```{r, echo = FALSE}
+setwd(tmpDir)
+analysis_timing_n <- 100
+analysis_timing_function <- function(){
+
+  scramblaseAssayTraces("inputTable.txt", timeMax = 350)
+}
+analysis_timing <- microbenchmark(
+  analysis_timing_function(),
+  times = analysis_timing_n)
+
+analysis_timing_median <- round(
+  summary(
+    analysis_timing)$median,
+  2)
+
+analysis_timing_iqr <- round(
+  diff(
+    unlist(
+      summary(analysis_timing)[c("lq", "uq")],
+      use.names = FALSE)),
+  2)
+```
+With `flippant` we present an integrated solution for data analysis in the 
+context of dithionite scramblase assays. Requiring only basic familiarity with 
+`R` [@r_core_team_r:_2015] as an environment for statistical computing and
+graphics, scientists can quickly analyse such data and arrive at 
+publication-grade graphics that offer extensive facilities for individual 
+optimization and adaptation [@wickham_ggplot2_2009]. On a system running `Linux`
+and `R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
+statements generating equivalents to the plots and calculations presented here
+take a mere `r analysis_timing_median` seconds (IQR: `r analysis_timing__iqr` s;
+$n==`r analysis_timing_n`$).
 

### 2015-09-21 inst/manuscript/manuscript.rmd
Fix a typo;

@@
 statements generating equivalents to the plots and calculations presented here
-take a mere `r analysis_timing_median` seconds (IQR: `r analysis_timing__iqr` s;
+take a mere `r analysis_timing_median` seconds (IQR: `r analysis_timing_iqr` s;
 $n==`r analysis_timing_n`$).

### 2015-09-21 inst/manuscript/manuscript.rmd
Force LONG timing evaluation to be cached;
Keep refining the conclusions ...;

@@
 #Conclusion
-```{r, echo = FALSE}
+```{r, echo = FALSE, cache = TRUE}
 setwd(tmpDir)
@@
 statements generating equivalents to the plots and calculations presented here
-take a mere `r analysis_timing_median` seconds (IQR: `r analysis_timing_iqr` s;
-$n==`r analysis_timing_n`$).
+take a mere `r analysis_timing_median` seconds (median; IQR: 
+`r analysis_timing_iqr` s; $n==`r analysis_timing_n`$).
 

### 2015-09-21 inst/manuscript/manuscript.rmd
Fix figure numbering to what's currently in the Ploier et al. Manuscript;

@@
 `flippant`s capabilities are demonstrated here by reanalyzing the data underlying 
-Figure 5b in @ploier_perturbed_submitted. The following work flow in a first 
+Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
 step plots spectral traces for all points of the data set (Figure 1A). Note that
@@
 ```
-```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "**`flippant`-based reanalysis of data in Figure 5b from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`."}
+```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "**`flippant`-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`."}
 setwd(tmpDir)

### 2015-09-21 inst/manuscript/manuscript.rmd
Birgit Ploier approved the renaming of the file ...;

@@
 times between experiments.
-<!-- Fix F220CEx1_E.txt to F220CEx1_D.txt -->
 ```{r, eval = FALSE}

### 2015-09-21 inst/manuscript/manuscript.rmd
Fix math mode type "==";

@@
 take a mere `r analysis_timing_median` seconds (median; IQR: 
-`r analysis_timing_iqr` s; $n==`r analysis_timing_n`$).
+`r analysis_timing_iqr` s; $n=`r analysis_timing_n`$).
 

### 2015-09-21 inst/manuscript/manuscript.rmd
Nicer math writing;

@@
 statements generating equivalents to the plots and calculations presented here
-take a mere `r analysis_timing_median` seconds (median; IQR: 
-`r analysis_timing_iqr` s; $n=`r analysis_timing_n`$).
+take a mere `r analysis_timing_median` seconds (median; 
+$\text{IQR}=`r analysis_timing_iqr` \text{s}$; $n=`r analysis_timing_n`$).
 

### 2015-09-23 inst/manuscript/manuscript.rmd
Continued refinement;

@@
 
-`flippant`s capabilities are demonstrated here by reanalyzing the data underlying 
+`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
 Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
-step plots spectral traces for all points of the data set (Figure 1A). Note that
-alorithmic alignment to the time of dithionite addition is employed (default) as
-well as custom trimming of the time axis to account for divergent acquisition 
+step plots the corresponding spectral traces (Figure 1A). Note that alorithmic
+alignment to the time of dithionite addition is employed (default) as well as 
+custom trimming of the time axis to account for divergent acquisition 
 times between experiments.

### 2015-09-23 R/scramblaseAssayCalculations.R
Make "forceThroughOrigin = FALSE" the default, as it has delivered better results in 2 datasets now;

@@ -1,5 +1,5 @@
 #' @importFrom nlmrt nlxb
-scramblaseAssayCalculations <- function(x,scaleTo,forceThroughOrigin=TRUE){
+scramblaseAssayCalculations <- function(x,scaleTo,forceThroughOrigin=FALSE){
 # Set parameters ----------------------------------------------------------
   nlsControl <- list(minFactor=1/20480,maxit=100)
 # Parsing spectra ---------------------------------------------------------

### 2015-09-23 R/scramblaseAssayTraces.R

@@ -30,7 +30,7 @@ baseFunctionScramblaseAssayTraces <- function(
   validatedParams <- scramblaseAssayInputValidation(
     x = x,
     scaleTo = "data",
-    forceThroughOrigin = TRUE,
+    forceThroughOrigin = FALSE,
     verbose = FALSE)
   x <- validatedParams[["x"]]
   assert_is_a_number(timeMin)

### 2015-09-23 R/scramblaseAssayCalculations.R
Explicitly trigger garbage collection following "wmtsa" functionality use - otherwise recalls will start tripping over unallocated memory;

@@ -170,6 +170,7 @@ scramblaseAssayCalculations <- function(x,scaleTo,forceThroughOrigin=FALSE){
           start = list(a=estimatedA,b=1,c=1)
         },
         control = nlsControl)
+      gc()
       z$"Fit Constant (a)" <- coef(rMod)[["a"]]
       z$"PPR at P = 0.5" <- if(forceThroughOrigin){
         -coef(rMod)[["a"]] * log(1 - 0.5/coef(rMod)[["b"]])

### 2015-09-23 R/scramblaseAssayStats.R
Small output reformatting;

@@ -35,7 +35,7 @@ baseFunctionScramblaseAssayStats <- function(x,scaleTo=c("model","data"),forceTh
   output <- output[!duplicated(output$CombinedId),]
   output <- output[which(names(output) %in% c("Fit Constant (a)","PPR at P = 0.5","Experimental Series","Experiment"))]
   output[c("Fit Constant (a)","PPR at P = 0.5")] <- round(output[c("Fit Constant (a)","PPR at P = 0.5")],digits=2)
-
+  names(output)[which(names(output) == "Fit Constant (a)")] <- "Fit Constant"
 # Return ------------------------------------------------------------------
   return(output)
 }

### 2015-09-23 inst/manuscript/manuscript.rmd
Figure reformatting to a 3/5-2/5 split;
Further editing;

@@
 figure1 <- multipanelfigure(
-  width = 17.22, 
-  height = 18, 
+  widths = rep(17.22/3-2*0.25, 3), 
+  heights = rep(18/5-4*0.25, 5), 
   units = "cm",
-  columns = 2, 
-  rows = 2,
   interPanelSpacing = 0.25)
@@
 
-Numeric scramblase assay results such as $\tau$ may be generated in tabular form
-using
+Numeric scramblase assay results such as $\tau$/$\alpha$ may be generated in 
+tabular form using
 ```{r, code = formatR::usage('scramblaseAssayStats'), eval = FALSE}
@@
 ```
-```{r, echo = FALSE, warning=FALSE, message=FALSE, fig.cap = "**`flippant`-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`."}
+```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`, while (B) shows protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details)."}
 setwd(tmpDir)
@@
   topPanel = 1,
+  bottomPanel = 3,
   leftPanel = 1, 
-  rightPanel = 2, 
-  panel = scramblaseAssayTraces("inputTable.txt", timeMax = 350)
-)
+  rightPanel = 3, 
+  panel = scramblaseAssayTraces("inputTable.txt", timeMax = 350) + theme_bw())
+figure1 <- addpanel(
+  figure = figure1,
+  topPanel = 4,
+  bottomPanel = 5,
+  leftPanel = 1, 
+  rightPanel = 3, 
+  panel = scramblaseAssayPlot("inputTable.txt") + 
+    theme_bw() + 
+    xlim(0, 2) + 
+    xlab(expression("PPR"~~("mg"/"mmol"))) +
+    ylab(expression(P[{phantom()>=1}])))
 grid.draw(figure1)
 ```
+
+Scramblase activity analysis as described above is performed on the data set with
+the following calls.
+```{r, eval = FALSE}
+# Plot PPR plot (Figure 1B)
+scramblaseAssayPlot("inputTable.txt") + xlim(0, 2)
+# Write out results in tabular manner
+scramblaseAssayStats("inputTable.txt")
+```
+```{r, echo = FALSE}
+setwd(tmpDir)
+max_PPR <- read.delim(
+    "inputTable.txt",
+    check.names = FALSE) %>%
+  flippant:::calculatePpr() %>%
+  max(
+    na.rm = TRUE) %>%
+  round(
+    digits = 2
+  )
+```
+The first call results in the protein to phospholipid ratio (PPR) plot shown in
+Figure 1B. Using the customization facilities provided by `ggplot2` 
+[@wickham_ggplot2_2009] as a plotting system the plot's x-axis is trimmed to
+avoid visual compression of all data by a single data point from the wild type 
+rhodopsin series in experiment 1, where $\text{PPR}=`r max_PPR`$. Dashed lines
+are added automatically as graphical representations of the fit constant 
+$\alpha$ or $\tau$, but are difficult to evaluate visually.
+
+Recapitulation of the calculations underlying PPR plot generation by 
+`scramblaseAssayPlot` in a call to `scramblaseAssayStats` produces tabular 
+output represented in Table 1, which includes series-specific fit constants 
+$\alpha$ in numeric and easily accessible form.
+```{r, echo = FALSE}
+setwd(tmpDir)
+ppr_results <- scramblaseAssayStats("inputTable.txt")
+ppr_results_tau_average <- ppr_results %>%
+  split(ppr_results$`Experimental Series`) %>% 
+  sapply(function(y){mean(y$`Fit Constant`, na.rm = TRUE)}) %>%
+  round(2)
+ppr_results_tau_average_names <- names(ppr_results_tau_average) %>%
+  head(n = length(ppr_results_tau_average) - 1) %>%
+  paste(collapse = ", ") %>%
+  paste("and") %>%
+  paste(tail(names(ppr_results_tau_average), n = 1))
+ppr_results_tau_average_print <- ppr_results_tau_average %>%
+  unname() %>%
+  head(n = length(ppr_results_tau_average) - 1) %>%
+  paste(collapse = ", ") %>%
+  paste("and") %>%
+  paste(tail(ppr_results_tau_average, n = 1))
+knitr::kable(
+  ppr_results,
+  row.names = FALSE,
+  caption = "**Tabular output of `flippant`-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An `ASCII`-version of this output is produced by calling `scramblaseAssayStats`.")
+```
+
+Mean $\tau$ values (or fit constants $\alpha$) correspond with `r ppr_results_tau_average_print` for `r ppr_results_tau_average_names`, 
+respectively, very well to the prior manual analyis by 
+@ploier_perturbed_submitted, where $\tau \approx 0.12$ was reported for mustant 
+and $\tau \approx 0.26$ for wild type rhodopsin. Based on the manual analysis of
+the data we conclude in @ploier_perturbed_submitted that the mutant rhodopsins
+investigated are reconsituted into proteoliposomes in monomeric form, contrary 
+to the wild type, which is reconstituting as a homodimer. `flippant` analysis of
+the data, shows identical trends and close matches of the results, supporting 
+identical conclusions.
 
@@
 analysis_timing_function <- function(){
-
-  scramblaseAssayTraces("inputTable.txt", timeMax = 350)
+  scramblaseAssayTraces(
+    "inputTable.txt",
+    timeMax = 350)
+  scramblaseAssayPlot("inputTable.txt")
+  scramblaseAssayStats("inputTable.txt")
 }
@@
 publication-grade graphics that offer extensive facilities for individual 
-optimization and adaptation [@wickham_ggplot2_2009]. On a system running `Linux`
-and `R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
+optimization and adaptation [@wickham_ggplot2_2009]. On a laptop system with 
+`r parallel::detectCores()` cores and 8 GB RAM (no SSD), running `Linux` and 
+`R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
 statements generating equivalents to the plots and calculations presented here
 take a mere `r analysis_timing_median` seconds (median; 
-$\text{IQR}=`r analysis_timing_iqr` \text{s}$; $n=`r analysis_timing_n`$).
+$\text{IQR}=`r analysis_timing_iqr`~\text{s}$; $n=`r analysis_timing_n`$).
 

### 2015-09-24 inst/manuscript/manuscript.rmd
Add another conclusion paragraph;

@@
 
+Results from `flippant`-driven analysis track well prior manual analysis. 
+Deviations observed may stem from algorithmic differences such as the fitting 
+routine used (`flippant` uses the Nash variant of the Marquardt 
+nonlinear least squares algorithm as implemented by @nash_nlmrt:_2014) and 
+general handling of significant digits and rounding.
+
 #Funding

### 2015-09-24 inst/manuscript/manuscript.rmd
Try to robustify nlmrt-calls further by additional garbage collection;

@@
   scramblaseAssayStats("inputTable.txt")
+  gc()
 }

### 2015-09-24 inst/manuscript/manuscript.rmd
A spell checking pass;

@@
 and fluorescence intensity representing columns are currently supported. 
-File type determination is handled algorythmically.
+File type determination is handled algorithmically.
 
@@
 Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
-step plots the corresponding spectral traces (Figure 1A). Note that alorithmic
+step plots the corresponding spectral traces (Figure 1A). Note that algorithmic
 alignment to the time of dithionite addition is employed (default) as well as 
@@
 Mean $\tau$ values (or fit constants $\alpha$) correspond with `r ppr_results_tau_average_print` for `r ppr_results_tau_average_names`, 
-respectively, very well to the prior manual analyis by 
-@ploier_perturbed_submitted, where $\tau \approx 0.12$ was reported for mustant 
+respectively, very well to the prior manual analysis by 
+@ploier_perturbed_submitted, where $\tau \approx 0.12$ was reported for mutant 
 and $\tau \approx 0.26$ for wild type rhodopsin. Based on the manual analysis of
 the data we conclude in @ploier_perturbed_submitted that the mutant rhodopsins
-investigated are reconsituted into proteoliposomes in monomeric form, contrary 
+investigated are reconstituted into proteoliposomes in monomeric form, contrary 
 to the wild type, which is reconstituting as a homodimer. `flippant` analysis of
@@
 context of dithionite scramblase assays. Requiring only basic familiarity with 
-`R` [@r_core_team_r:_2015] as an environment for statistical computing and
-graphics, scientists can quickly analyse such data and arrive at 
+`R` as an environment for statistical computing and graphics 
+[@r_core_team_r:_2015], scientists can quickly analyse such data and arrive at 
 publication-grade graphics that offer extensive facilities for individual 
@@
 
-Results from `flippant`-driven analysis track well prior manual analysis. 
+Results from `flippant`-driven analysis track prior manual analysis well. 
 Deviations observed may stem from algorithmic differences such as the fitting 

### 2015-09-24 inst/manuscript/manuscript.rmd
Two terminal paragraphs of a first complete draft;

@@
 
+The choice of `R` for the implementation is not only motivated by the extensive
+tool kit for statistic methodology and exquisite plotting environment it 
+provides, but also by the fact that it is a scripting language, rendering the
+implementation unequivocally open to scrutiny and adaptation or extension by 
+users.
+
+`flippant`, in conclusion, provides means for quick, reproducible data analysis
+in the context of dithionite scramblase analysis and a platform for review, 
+dissemination and extension of the strategies it employs.
+
 #Funding

### 2015-09-24 inst/manuscript/manuscript.rmd
Integrate edits by Birgit Ploier;

@@
 # Introduction
-Scramblases are proteins mediating the mass-action driven equilibration of 
-lipids between the leaflets of lipid bilayers that constitute biological membranes
-[@waechter_flippases_2013]. Independent of energy equivalents such as ATP they 
-facilitate this ``flipping'' by providing a mechanism of transition through the 
-hydrophobic environment of membranes to polar lipid head groups, thus reducing 
-the massive energetic cost that process would carry otherwise 
-[@kornberg_inside-outside_1971]. The underlying molecular mechanisms remain 
-largely enigmatic [for a discussion including exceptions see @ernst_phospholipid_2015].
+Scramblases are proteins mediating the bidirectional, mass-action driven 
+equilibration of lipids between the leaflets of lipid bilayers that constitute 
+biological membranes [@waechter_flippases_2013]. Independent of energy 
+equivalents such as ATP they facilitate this ``flipping'' by providing a 
+mechanism of transition through the hydrophobic environment of membranes to 
+polar lipid head groups, thus reducing the massive energetic cost that process 
+would carry otherwise [@kornberg_inside-outside_1971]. The underlying molecular 
+mechanisms remain largely enigmatic [for a discussion including exceptions see @ernst_phospholipid_2015].
 Proteins supporting flipping processes as central as the equilibration of the 
@@
 the user assembled spreadsheet of input data (`x`), including automatically 
-added graphical representations of $\tau$, the PPR value equal to the fit 
+added graphical representations the PPR value equal to the fit 
 constant $\alpha$, which implies all liposomes on average carrying one 
@@
 
-Numeric scramblase assay results such as $\tau$/$\alpha$ may be generated in 
+Numeric scramblase assay results such as $\alpha$ may be generated in 
 tabular form using
@@
 are added automatically as graphical representations of the fit constant 
-$\alpha$ or $\tau$, but are difficult to evaluate visually.
+$\alpha$, but are difficult to evaluate visually.
 
@@
 ppr_results <- scramblaseAssayStats("inputTable.txt")
-ppr_results_tau_average <- ppr_results %>%
+ppr_results_alpha_average <- ppr_results %>%
   split(ppr_results$`Experimental Series`) %>% 
@@
   round(2)
-ppr_results_tau_average_names <- names(ppr_results_tau_average) %>%
-  head(n = length(ppr_results_tau_average) - 1) %>%
+ppr_results_alpha_average_names <- names(ppr_results_alpha_average) %>%
+  head(n = length(ppr_results_alpha_average) - 1) %>%
   paste(collapse = ", ") %>%
   paste("and") %>%
-  paste(tail(names(ppr_results_tau_average), n = 1))
-ppr_results_tau_average_print <- ppr_results_tau_average %>%
+  paste(tail(names(ppr_results_alpha_average), n = 1))
+ppr_results_alpha_average_print <- ppr_results_alpha_average %>%
   unname() %>%
-  head(n = length(ppr_results_tau_average) - 1) %>%
+  head(n = length(ppr_results_alpha_average) - 1) %>%
   paste(collapse = ", ") %>%
   paste("and") %>%
-  paste(tail(ppr_results_tau_average, n = 1))
+  paste(tail(ppr_results_alpha_average, n = 1))
 knitr::kable(
@@
 
-Mean $\tau$ values (or fit constants $\alpha$) correspond with `r ppr_results_tau_average_print` for `r ppr_results_tau_average_names`, 
+Mean values of fit constant $\alpha$) correspond with 
+`r ppr_results_alpha_average_print` for `r ppr_results_alpha_average_names`, 
 respectively, very well to the prior manual analysis by 
-@ploier_perturbed_submitted, where $\tau \approx 0.12$ was reported for mutant 
-and $\tau \approx 0.26$ for wild type rhodopsin. Based on the manual analysis of
-the data we conclude in @ploier_perturbed_submitted that the mutant rhodopsins
-investigated are reconstituted into proteoliposomes in monomeric form, contrary 
-to the wild type, which is reconstituting as a homodimer. `flippant` analysis of
-the data, shows identical trends and close matches of the results, supporting 
-identical conclusions.
+@ploier_perturbed_submitted, where $\alpha \approx 0.13$ was reported for mutant 
+and $\alpha \approx 0.26$ for wild type rhodopsin. Based on the manual analysis 
+of the data we conclude in @ploier_perturbed_submitted that the mutant 
+rhodopsins investigated are reconstituted into proteoliposomes in monomeric 
+form, contrary to the wild type, which is reconstituting as a homodimer. 
+`flippant` analysis of the data, shows identical trends and close matches of the
+results, supporting identical conclusions.
 

### 2015-09-24 inst/manuscript/manuscript.rmd
Keep on editing;

@@
 
-##Summary
-
-##Availability and Implementation
-
 ##Contact
 jog2030@qatar-med.cornell.edu
-
-##Supplementary Information
 
@@
 
-#Installation
-`flippant` has been integrated into the `bioconductor` collection of tools for 
-biomedical data analysis [@huber_orchestrating_2015] and is thus install- and
-loadable as follows from within a functional `R` environment:
+#Availablility and Implementation
+`flippant` has been implemented in `R` [@r_core_team_r:_2015] and integrated 
+into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install- and loadable as follows from 
+within a functional `R` environment:
 ```{r, eval = FALSE}

### 2015-09-24 inst/manuscript/manuscript.rmd
Add an draft abstract;

@@
 #Abstract
-
-##Contact
-jog2030@qatar-med.cornell.edu
+Dithionite scramblase assays are an established means of probing the lipid 
+scrambling activity of protein extracts and purified proteins. While the assay
+has yielded insight into the scramblase activity in crude membrane preparations,
+functional validation of candidate scramblases, stoichiometry of scramblase 
+complexes and probe ATP-dependence of flippases, data analysis in its context 
+has remained a task involving many manual steps. With the extension package 
+`flippant` to `R`, a free software environment for statistical computing and 
+graphics, we introduce an integrated solution for the analysis and 
+publication-grade graphical presentation of dithionite scramblase assays and 
+demonstrate its utility in a reanalysis of manual analysis from the publication
+record, closely reproducing the reported results.
 

### 2015-09-25 inst/manuscript/manuscript.rmd
Add an draft abstract;
Fix "Mike" to "Michael", as advised by Birgit Ploier;
Typo;

@@
   assays'
-author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^, Mike A.
-  Goren ^‡^ and Anant K. Menon ^‡^
-date: "September 19, 2015"
+author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
+  Michael A. Goren ^‡^ and Anant K. Menon ^‡^
+date: "September 24, 2015"
 output:
@@
 
-Mean values of fit constant $\alpha$) correspond with 
+Mean values of fit constant $\alpha$ correspond with 
 `r ppr_results_alpha_average_print` for `r ppr_results_alpha_average_names`, 

### 2015-09-25 inst/manuscript/manuscript.rmd
Paraphrasing;

@@
 publication-grade graphical presentation of dithionite scramblase assays and 
-demonstrate its utility in a reanalysis of manual analysis from the publication
-record, closely reproducing the reported results.
+demonstrate its utility in revisiting an originally manual analysis from the 
+publication record, closely reproducing the reported results.
 

### 2015-10-01 R/scramblaseAssayPlot.R
Fix a typo;

@@ -120,7 +120,7 @@
 #' point of dithionite addition.
 #' @return \code{scrambalseAssayTraces} and \code{scramblaseAssayPlot} return 
 #' \code{\link{ggplot}} objects representing the raw fluorescence traces and a
-#' complete PPR plot, respectively. \code{scrambalseAssayInputTamplate} 
+#' complete PPR plot, respectively. \code{scrambalseAssayInputTemplate} 
 #' generates a tab-delimited \code{ASCII} file in the file system and does not
 #' provide further output. \code{scrambalseAssayStats} prints assay statistics.
 #' @author Johannes Graumann

### 2015-10-01 R/scramblaseAssayPlot.R
Clarification;

@@ -122,7 +122,8 @@
 #' \code{\link{ggplot}} objects representing the raw fluorescence traces and a
 #' complete PPR plot, respectively. \code{scrambalseAssayInputTemplate} 
 #' generates a tab-delimited \code{ASCII} file in the file system and does not
-#' provide further output. \code{scrambalseAssayStats} prints assay statistics.
+#' provide further output. \code{scrambalseAssayStats} assembles (and prints) 
+#' assay statistics as a \code{\link{data.frame}}.
 #' @author Johannes Graumann
 #' @references Menon, I., Huber, T., Sanyal, S., Banerjee, S., Barre, P., Canis, 
 #' S., Warren, J.D., Hwa, J., Sakmar, T.P., and Menon, A.K. (2011). Opsin Is a 

### 2015-10-01 R/scramblaseAssayStats.R
Remove default printing of P(0.5) - request by Mike Goren;

@@ -33,8 +33,8 @@ baseFunctionScramblaseAssayStats <- function(x,scaleTo=c("model","data"),forceTh
 # Assemble the output -----------------------------------------
   output <- plyr::rbind.fill(processedListFromX)
   output <- output[!duplicated(output$CombinedId),]
-  output <- output[which(names(output) %in% c("Fit Constant (a)","PPR at P = 0.5","Experimental Series","Experiment"))]
-  output[c("Fit Constant (a)","PPR at P = 0.5")] <- round(output[c("Fit Constant (a)","PPR at P = 0.5")],digits=2)
+  output <- output[which(names(output) %in% c("Fit Constant (a)","Experimental Series","Experiment"))]
+  output["Fit Constant (a)"] <- round(output["Fit Constant (a)"],digits=2)
   names(output)[which(names(output) == "Fit Constant (a)")] <- "Fit Constant"
 # Return ------------------------------------------------------------------
   return(output)

### 2015-10-01 inst/manuscript/manuscript.rmd
As given by Mike Goren: add a citation for the ER phosphoglycerolipid flippase;

@@
 reticulum, where they are synthesized in the cytoplasmic monolayer, have yet to 
-be identified **(I was looking for a recent 
-citation that clearly spelled that out - in vain. Do you have a proposal?)**. 
+be identified [@menon_specific_2000]. 
 None the less, there has been much recent progress in scramblase identification 

### 2015-10-01 inst/manuscript/manuscript.rmd
Broaden application scope by reference to BSA back-extraction assay (proposal by mike);

@@
 gradient between bilayer leaflets [@soupene_atp8a1_2008].
-**Are you aware of further use? More adoption would fortify the need for the 
-package ...**
 
@@
 in the context of dithionite scramblase analysis and a platform for review, 
-dissemination and extension of the strategies it employs.
+dissemination and extension of the strategies it employs. As BSA-back 
+extraction, a different assay for lipid translocation across liposome bilayers
+[@kubelt_transbilayer_2002;@vehring_flip-flop_2007], can utilize an essentially 
+identical data analysis workflow, `flippant` is expected to facilitate analysis
+of such experiments as well.
 

### 2015-10-01 inst/manuscript/manuscript.rmd
Clarify intended usage for the generic data format (in response to remark by Mike Goren);
Fix a superfluous comma;

@@
 generic tab-delimited spectrum representing file format with time (in seconds) 
-and fluorescence intensity representing columns are currently supported. 
-File type determination is handled algorithmically.
+and fluorescence intensity representing columns are currently supported. The 
+latter is trivially assembled from any fluorescence data using a spreadsheet 
+program. File type determination is handled algorithmically.
 
@@
 form, contrary to the wild type, which is reconstituting as a homodimer. 
-`flippant` analysis of the data, shows identical trends and close matches of the
+`flippant` analysis of the data shows identical trends and close matches of the
 results, supporting identical conclusions.

### 2015-10-04 inst/manuscript/manuscript.rmd
Add a "Research Division" to the institutional association;
typo fixes

@@
 :    \
-    Weill Cornell Medical College in Qatar, P.O.Box 24144, Doha, State of Qatar
+    Research Division, Weill Cornell Medical College in Qatar, P.O.Box 24144, Doha, State of Qatar
 
@@
 `flippant` has been implemented in `R` [@r_core_team_r:_2015] and integrated 
-into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install- and loadable as follows from 
+into the `Bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install- and loadable as follows from 
 within a functional `R` environment:
@@
 time of dithionite addition. Acquisition time coverage of the plot may be tuned 
-by user-provided minimal (`timeMin` ) and maximal (`timeMax`) time points to be
+by user-provided minimal (`timeMin`) and maximal (`timeMax`) time points to be
 included.
@@
 
-`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
+`flippant`'s capabilities are demonstrated here by reanalyzing data underlying 
 Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 

### 2015-10-05 inst/manuscript/manuscript.rmd
Clarify units of the timeMin/Max parameters by switching to timeMinSec/timeMaxSec;

--- 2015-10-01 inst/manuscript/manuscript.rmd
@@
 time of dithionite addition. Acquisition time coverage of the plot may be tuned 
-by user-provided minimal (`timeMin` ) and maximal (`timeMax`) time points to be
-included.
+by user-provided minimal (`timeMinSec` ) and maximal (`timeMaxSec`) time points
+to be (in seconds) included.
 
@@
   rightPanel = 3, 
-  panel = scramblaseAssayTraces("inputTable.txt", timeMax = 350) + theme_bw())
+  panel = scramblaseAssayTraces("inputTable.txt", timeMaxSec = 350) + theme_bw())
 figure1 <- addpanel(
@@
     "inputTable.txt",
-    timeMax = 350)
+    timeMaxSec = 350)
   scramblaseAssayPlot("inputTable.txt")

### 2015-10-05 R/scramblaseAssayPlot.R

@@ -109,12 +109,12 @@
 #' \code{model}. See "Details".
 #' @param forceThroughOrigin \code{\link{logical}} indicating whether to force 
 #' the fitted curve(s) to penetrate the origin (defaulting to \code{FALSE}).
-#' @param timeMin A single \code{\link{numeric}}. If given, 
+#' @param timeMinSec A single \code{\link{numeric}}. If given, 
 #' \code{\link{scramblaseAssayTraces}} produces a time/x axis trimmed to
-#' this value.
-#' @param timeMax A single \code{\link{numeric}}. If given, 
+#' this value (in seconds).
+#' @param timeMaxSec A single \code{\link{numeric}}. If given, 
 #' \code{\link{scramblaseAssayTraces}} produces a time/x axis trimmed to
-#' this value.
+#' this value (in seconds).
 #' @param adjust A single \code{\link{logical}}, indicating of whether (default) or 
 #' not spectral traces to be plotted are algorithmically aligned at the time
 #' point of dithionite addition.
@@ -153,7 +153,7 @@
 #' # Plot the spectal traces
 #' scramblaseAssayTraces(
 #'   "inputTable.txt",
-#'   timeMax = 350)
+#'   timeMaxSec = 350)
 #' stop("Add example using actually published data.")
 #' # Plot the PPR plot(s)
 #' scramblaseAssayPlot("inputTable.txt")

### 2015-10-05 R/scramblaseAssayTraces.R

@@ -5,8 +5,8 @@
 #' @export
 scramblaseAssayTraces <- function(
   x,
-  timeMin=NA_real_,
-  timeMax=NA_real_,
+  timeMinSec=NA_real_,
+  timeMaxSec=NA_real_,
   adjust = TRUE){
   UseMethod("scramblaseAssayTraces", x)
 }
@@ -23,8 +23,8 @@ scramblaseAssayTraces.character <- function(x, ...){
 }
 baseFunctionScramblaseAssayTraces <- function(
   x,
-  timeMin=NA_real_,
-  timeMax=NA_real_,
+  timeMinSec=NA_real_,
+  timeMaxSec=NA_real_,
   adjust = TRUE){
 # Check Prerequisites -----------------------------------------------------
   validatedParams <- scramblaseAssayInputValidation(
@@ -33,8 +33,8 @@ baseFunctionScramblaseAssayTraces <- function(
     forceThroughOrigin = FALSE,
     verbose = FALSE)
   x <- validatedParams[["x"]]
-  assert_is_a_number(timeMin)
-  assert_is_a_number(timeMax)
+  assert_is_a_number(timeMinSec)
+  assert_is_a_number(timeMaxSec)
 
 # Processing --------------------------------------------------------------
   # Perform assay calculations to retrive PPR
@@ -74,10 +74,10 @@ baseFunctionScramblaseAssayTraces <- function(
   # Plot traces with lines
   plotOutput <- plotOutput + geom_line()
   # Restrict x axis as requested
-  if(any(!is.na(c(timeMin,timeMax)))){
+  if(any(!is.na(c(timeMinSec,timeMaxSec)))){
     xRange <- range(mergedData$Time.in.sec, na.rm=TRUE)
-    if(!is.na(timeMin)){xRange[1] <- timeMin}
-    if(!is.na(timeMax)){xRange[2] <- timeMax}
+    if(!is.na(timeMinSec)){xRange[1] <- timeMinSec}
+    if(!is.na(timeMaxSec)){xRange[2] <- timeMaxSec}
     plotOutput <- plotOutput + xlim(xRange)
   }
   # Render color scale friendly to the color blind

### 2015-10-05 inst/manuscript/manuscript.rmd
Include RJC's comments (edited);

@@
 ---
-title: '`flippant` -- An `R` package for the automated analysis of dithionite scramblase
+title: '*flippant* -- An R package for the automated analysis of dithionite scramblase
   assays'
@@
       c(
-        "`",
-        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
-        "` and `",
+        "*",
+        paste0(head(x, n = length(x) - 1), collapse = "*, *"),
+        "* and *",
         tail(x, n = 1),
-        "`"),
+        "*"),
       collapse = "")} )
@@
 has remained a task involving many manual steps. With the extension package 
-`flippant` to `R`, a free software environment for statistical computing and 
+*flippant* to R, a free software environment for statistical computing and 
 graphics, we introduce an integrated solution for the analysis and 
@@
 [see @menon_opsin_2011;@goren_constitutive_2014 for extensive step-wise discussion].
-Based on the `R` free software environment for statistical computing and 
+Based on the R free software environment for statistical computing and 
 graphics [@r_core_team_r:_2015] and prominently drawing on the power and 
 elegance of the `ggplot2` plotting system [@wickham_ggplot2_2009], we here 
-provide `flippant`, a package that comprehensively, fast and reproducibly covers
+provide *flippant*, a package that comprehensively, fast and reproducibly covers
 all data analysis and graphing needs from raw fluorescence spectra produced by 
@@
 #Availablility and Implementation
-`flippant` has been implemented in `R` [@r_core_team_r:_2015] and integrated 
+*flippant* has been implemented in R [@r_core_team_r:_2015] and integrated 
 into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install- and loadable as follows from 
-within a functional `R` environment:
+within a functional R environment:
 ```{r, eval = FALSE}
@@
 ```
-The package depends on the following packaged extensions to `R` base 
+The package depends on the following packaged extensions to R base 
 functionality, which are automatically satisfied on installation: 
@@
 #Input Data and Data Processing
-To analyse raw data stemming from dithionite scramblase assays, `flippant` 
+To analyse raw data stemming from dithionite scramblase assays, *flippant* 
 requires for each data point information on the path to the 
@@
 
-Spectral input data is read by `flippant` using the file paths provided in the
+Spectral input data is read by *flippant* using the file paths provided in the
 spreadsheet. Raw spectra produced by QuantaMaster fluorometer instruments 
@@
 
-Based on @menon_opsin_2011 and @goren_constitutive_2014, data is processed as 
-follows. Input is format checked and defaults are injected for facultative 
-parameters/columns as appropriate. Fluorescence spectra are parsed. This includes 
-algorithmic determination of when dithionite was added to the sample using peak
-detection by continuous wavelet transformation as implemented in the 
-`wmtsa` `R` package [@percival_wavelet_2000;@constantine_wmtsa:_2013]. 
+Based on @menon_opsin_2011 and @goren_constitutive_2014 and largly keeping with
+nomenclature used therein, data is processed as follows. Input is format checked
+and defaults are injected for facultative parameters/columns as appropriate. 
+Fluorescence spectra are parsed. This includes algorithmic determination of when 
+dithionite was added to the sample using peak detection by continuous wavelet
+transformation as implemented in the *wmtsa* R package [@percival_wavelet_2000;@constantine_wmtsa:_2013]. 
 Acquisition time is aligned for all spectra in the data set such that the zero 
@@
 Supporting the user in providing the input data needed, the following function 
-generates a spreadsheet program-compatible tab-delimited `ASCII` template, 
+generates a spreadsheet program-compatible tab-delimited plain text template, 
 including column names, commentary, expected data type and the default used when
@@
 completed table, which is subjected to extensive input checks when read by 
-`flippant`.
+*flippant*.
 
@@
 data (`x`). The `adjust` argument to the function call serves to selectively 
-inactivate `wmtsa`-provided (see above) alignment of multiple spectra to the 
+inactivate *wmtsa*-provided (see above) alignment of multiple spectra to the 
 time of dithionite addition. Acquisition time coverage of the plot may be tuned 
@@
 comparison of specific scramblase activity between interrogated experimental 
-series, which may e.g. be representative of protein preparations including 
+series, which may, for example, be representative of protein preparations including 
 mutant protein forms or crude extracts with or without depletion of a candidate
@@
 the user assembled spreadsheet of input data (`x`), including automatically 
-added graphical representations the PPR value equal to the fit 
-constant $\alpha$, which implies all liposomes on average carrying one 
-scramblase and 63% have one or more (i.e. are active). The behavior of the 
+added graphical representations the PPR value equal to the fit constant 
+$\alpha$, which implies all liposomes on average carrying one scramblase and 63%
+have one or more [i.e. are active; @goren_constitutive_2014]. The behavior of the 
 function may be adjusted to use scramblase-mediated fluorescence reduction 
@@
 
-`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
+*flippant*s capabilities are demonstrated here by reanalyzing data underlying 
 Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
@@
 # Plot spectral traces (Figure 1A)
-scramblaseAssayTraces("inputTable.txt", timeMax = 350)
+scramblaseAssayTraces("inputTable.txt", timeMaxSec = 350)
 ```
-```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`, while (B) shows protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details)."}
+```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`, while (B) shows protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details)."}
 setwd(tmpDir)
@@
   row.names = FALSE,
-  caption = "**Tabular output of `flippant`-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An `ASCII`-version of this output is produced by calling `scramblaseAssayStats`.")
+  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblaseAssayStats`.")
 ```
@@
 form, contrary to the wild type, which is reconstituting as a homodimer. 
-`flippant` analysis of the data shows identical trends and close matches of the
+*flippant* analysis of the data shows identical trends and close matches of the
 results, supporting identical conclusions.
@@
 ```
-With `flippant` we present an integrated solution for data analysis in the 
+With *flippant* we present an integrated solution for data analysis in the 
 context of dithionite scramblase assays. Requiring only basic familiarity with 
-`R` as an environment for statistical computing and graphics 
+R as an environment for statistical computing and graphics 
 [@r_core_team_r:_2015], scientists can quickly analyse such data and arrive at 
@@
 `r parallel::detectCores()` cores and 8 GB RAM (no SSD), running `Linux` and 
-`R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
+R version `r paste(R.version[c("major","minor")], collapse = ".")`, the
 statements generating equivalents to the plots and calculations presented here
@@
 
-Results from `flippant`-driven analysis track prior manual analysis well. 
+Results from *flippant*-driven analysis track prior manual analysis well. 
 Deviations observed may stem from algorithmic differences such as the fitting 
-routine used (`flippant` uses the Nash variant of the Marquardt 
+routine used (*flippant* uses the Nash variant of the Marquardt 
 nonlinear least squares algorithm as implemented by @nash_nlmrt:_2014) and 
@@
 
-The choice of `R` for the implementation is not only motivated by the extensive
+The choice of R for the implementation is not only motivated by the extensive
 tool kit for statistic methodology and exquisite plotting environment it 
@@
 
-`flippant`, in conclusion, provides means for quick, reproducible data analysis
+*flippant*, in conclusion, provides means for quick, reproducible data analysis
 in the context of dithionite scramblase analysis and a platform for review, 
@@
 [@kubelt_transbilayer_2002;@vehring_flip-flop_2007], can utilize an essentially 
-identical data analysis workflow, `flippant` is expected to facilitate analysis
+identical data analysis workflow, *flippant* is expected to facilitate analysis
 of such experiments as well.

### 2015-10-05 inst/manuscript/manuscript.rmd
One more edit-request by RJC;

@@
 added graphical representations the PPR value equal to the fit constant 
-$\alpha$, which implies all liposomes on average carrying one scramblase and 63%
-have one or more [i.e. are active; @goren_constitutive_2014]. The behavior of the 
-function may be adjusted to use scramblase-mediated fluorescence reduction 
-normalized to either the maximum measurement in the series (`scaleTo = "data"`)
-or the plateau of an exponential fit to it (`scaleTo = "model"`; for reasoning
-see above) and whether or not to require the exponential curve fitted to the 
-data to go through the origin.
+$\alpha$ ($P_{\geq 1} = 1 - e^{-1}$), which implies all liposomes on average 
+carrying one scramblase and 63% have one or more 
+[i.e. are active; @goren_constitutive_2014]. The behavior of the function may be
+adjusted to use scramblase-mediated fluorescence reduction normalized to either
+the maximum measurement in the series (`scaleTo = "data"`) or the plateau of an
+exponential fit to it (`scaleTo = "model"`; for reasoning see above) and whether
+or not to require the exponential curve fitted to the data to go through the
+origin.
 

### 2015-10-05 inst/manuscript/manuscript.rmd
Make execution(more?) reliable by introducing empyt lines;

--- 2015-10-05 inst/manuscript/manuscript.rmd
@@
 within a functional R environment:
+
 ```{r, eval = FALSE}
@@
 ```
+
 The package depends on the following packaged extensions to R base 
@@
 omitted.
+
 ```{r, code=formatR::usage('scramblaseAssayInputTemplate'), eval=FALSE}
 ```
+
 The application agnostic tab-delimited format must be maintained for the 
@@
 using
+
 ```{r, code = formatR::usage('scramblaseAssayTraces'), eval = FALSE}
 ```
+
 and handing the function the path to the user assembled spreadsheet of input 
@@
 scramblase.
+
 ```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
 ```
+
 allows for the complete generation of the PPR plot in publication quality from 
@@
 tabular form using
+
 ```{r, code = formatR::usage('scramblaseAssayStats'), eval = FALSE}
 ```
+
 with the same modifying arguments to the function as for `scramblaseAssayPlot`.
@@
 times between experiments.
+
 ```{r, eval = FALSE}
@@
 ```
+
 ```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`, while (B) shows protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details)."}
@@
 the following calls.
+
 ```{r, eval = FALSE}
@@
 ```
+
 ```{r, echo = FALSE}
@@
 ```
+
 The first call results in the protein to phospholipid ratio (PPR) plot shown in
@@
 $\alpha$ in numeric and easily accessible form.
+
 ```{r, echo = FALSE}
@@
 #Conclusion
+
 ```{r, echo = FALSE, cache = TRUE}
@@
 ```
+
 With *flippant* we present an integrated solution for data analysis in the 

### 2015-10-16 inst/manuscript/manuscript.rmd
Automate dating of manuscript compilation;

@@
   Michael A. Goren ^‡^ and Anant K. Menon ^‡^
-date: "September 24, 2015"
+date: '`r format(Sys.Date(), "%B %d,%Y")`'
 output:

### 2015-10-16 inst/manuscript/manuscript.rmd
More carefully omit taking ownership where it is Menn-lab only;

@@
 receptors [both @goren_constitutive_2014]. Extrapolating from the latter findings 
-and the opsin/rhodopsin case, we speculate that lipid scrambling may, in fact, 
-be an intrinsic property of G-protein coupled receptors in general 
+and the opsin/rhodopsin case, one may speculate that lipid scrambling may, in
+fact, be an intrinsic property of G-protein coupled receptors in general 
 [@goren_constitutive_2014].
 
-To interrogate scramblases as a functional class of proteins, we have developed 
-a biochemical assay suited to characterize scramblase activity of purified 
+To interrogate scramblases as a functional class of proteins, a biochemical
+assay was developed suited to characterize scramblase activity of purified 
 proteins and protein extracts based on the reconstitution of scramblases or 
@@
 cases of which is linked to mutant forms of the G-protein coupled receptor 
-rhodopsin [@mendes_mechanisms_2005]. Motivated by our recent discovery that 
+rhodopsin [@mendes_mechanisms_2005]. Motivated by the recent discovery that 
 opsin/rhodopsin has scramblase activity [@menon_opsin_2011;@goren_constitutive_2014],

### 2015-10-16 inst/manuscript/manuscript.rmd
Integrate usage of "splitByExperiment" functonality;

@@
   widths = rep(17.22/3-2*0.25, 3), 
-  heights = rep(18/5-4*0.25, 5), 
+  heights = rep(27/7-5*0.25, 7), 
   units = "cm",
@@
   fig.width = 6.78, 
-  fig.height = 7.09, 
+  fig.height = 10.63, 
   warning = FALSE, 
@@
 or not to require the exponential curve fitted to the data to go through the
-origin.
+origin. The `splitByExperiment` argument is used to indicate whether independent
+experiments are integrated into a single analysis (`splitByExperiment = FALSE`)
+or treated separately (`splitByExperiment = TRUE`; see below for example usage).
 
@@
 
-```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`, while (B) shows protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details)."}
+```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details).
+In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
 setwd(tmpDir)
@@
     ylab(expression(P[{phantom()>=1}])))
+figure1 <- addpanel(
+  figure = figure1,
+  topPanel = 6,
+  bottomPanel = 7,
+  leftPanel = 1,
+  rightPanel = 2,
+  panel = scramblaseAssayPlot("inputTable.txt", splitByExperiment = FALSE) + 
+    theme_bw() + 
+    xlim(0, 2) + 
+    xlab(expression("PPR"~~("mg"/"mmol"))) +
+    ylab(expression(P[{phantom()>=1}])))
 grid.draw(figure1)
@@
 scramblaseAssayPlot("inputTable.txt") + xlim(0, 2)
-# Write out results in tabular manner
-scramblaseAssayStats("inputTable.txt")
 ```
@@
 
-The first call results in the protein to phospholipid ratio (PPR) plot shown in
+The call results in the protein to phospholipid ratio (PPR) plot shown in
 Figure 1B. Using the customization facilities provided by `ggplot2` 
@@
 are added automatically as graphical representations of the fit constant 
-$\alpha$, but are difficult to evaluate visually.
+$\alpha$.
 
-Recapitulation of the calculations underlying PPR plot generation by 
-`scramblaseAssayPlot` in a call to `scramblaseAssayStats` produces tabular 
-output represented in Table 1, which includes series-specific fit constants 
-$\alpha$ in numeric and easily accessible form.
+Figure 1B emphasizes reproducebility between independent experiments
+("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
+reproducibility analysis in favor of a potentially more reliable result and
+following more closely the analysis in Figure 4C/D by
+@ploier_perturbed_submitted, a single fit may be performed for the combined data
+from all experiments as follows, resulting in Figure 1C:
+
+```{r, eval = FALSE}
+# Plot PPR plot (Figure 1C)
+scramblaseAssayPlot("inputTable.txt", splitByExperiment = FALSE) + xlim(0, 2)
+```
+
+The graphical representation of the fit constant $\alpha$ in the PPR plots is
+difficult to visually evaluate and easy access to the numeric values desireable.
+Recapitulation of the calculations underlying PPR plot generation for Figure 1C
+by `scramblaseAssayPlot` in a call to `scramblaseAssayStats`, this is achieved
+and produces tabular output represented in Table 1.
+
+```{r, eval = FALSE}
+# Write out results in tabular manner (Table 1)
+scramblaseAssayStats("inputTable.txt" splitByExperiment = FALSE)
+```
 
@@
 setwd(tmpDir)
-ppr_results <- scramblaseAssayStats("inputTable.txt")
-ppr_results_alpha_average <- ppr_results %>%
-  split(ppr_results$`Experimental Series`) %>% 
-  sapply(function(y){mean(y$`Fit Constant`, na.rm = TRUE)}) %>%
-  round(2)
-ppr_results_alpha_average_names <- names(ppr_results_alpha_average) %>%
-  head(n = length(ppr_results_alpha_average) - 1) %>%
+ppr_results <- scramblaseAssayStats("inputTable.txt", splitByExperiment = FALSE)
+ppr_results_names <- ppr_results$`Experimental Series` %>%
+  head(n = nrow(ppr_results) - 1) %>%
   paste(collapse = ", ") %>%
   paste("and") %>%
-  paste(tail(names(ppr_results_alpha_average), n = 1))
-ppr_results_alpha_average_print <- ppr_results_alpha_average %>%
-  unname() %>%
-  head(n = length(ppr_results_alpha_average) - 1) %>%
+  paste(tail(ppr_results$`Experimental Series`, n = 1))
+ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
+  round(2) %>%
+  head(n = nrow(ppr_results) - 1) %>%
   paste(collapse = ", ") %>%
   paste("and") %>%
-  paste(tail(ppr_results_alpha_average, n = 1))
+  paste(tail(ppr_results$`Fit Constant`, n = 1))
 knitr::kable(
@@
 
-Mean values of fit constant $\alpha$ correspond with 
-`r ppr_results_alpha_average_print` for `r ppr_results_alpha_average_names`, 
-respectively, very well to the prior manual analysis by 
-@ploier_perturbed_submitted, where $\alpha \approx 0.13$ was reported for mutant 
-and $\alpha \approx 0.26$ for wild type rhodopsin. Based on the manual analysis 
-of the data we conclude in @ploier_perturbed_submitted that the mutant 
-rhodopsins investigated are reconstituted into proteoliposomes in monomeric 
-form, contrary to the wild type, which is reconstituting as a homodimer. 
+The resulting values for the fit constant $\alpha$ correspond with
+`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, very well
+to the prior manual analysis by @ploier_perturbed_submitted, where
+$\alpha \approx 0.13$ was reported for mutant and $\alpha \approx 0.26$ for wild
+type rhodopsin. Based on the manual analysis of the data we conclude in @ploier_perturbed_submitted that the mutant rhodopsins investigated are
+reconstituted into proteoliposomes in monomeric form, contrary to the wild type,
+which is reconstituting as a homodimer. 
 *flippant* analysis of the data shows identical trends and close matches of the
@@
 setwd(tmpDir)
+
 analysis_timing_n <- 100
+
 analysis_timing_function <- function(){
@@
   scramblaseAssayPlot("inputTable.txt")
-  scramblaseAssayStats("inputTable.txt")
-  gc()
+  scramblaseAssayPlot("inputTable.txt", splitByExperiment = FALSE)
+  scramblaseAssayStats("inputTable.txt", splitByExperiment = FALSE)
 }
+
 analysis_timing <- microbenchmark(

### 2015-10-16 inst/manuscript/manuscript.rmd
Some typo corrections;

@@
 
-Based on @menon_opsin_2011 and @goren_constitutive_2014 and largly keeping with
+Based on @menon_opsin_2011 and @goren_constitutive_2014 and largely keeping with
 nomenclature used therein, data is processed as follows. Input is format checked
@@
 set, fluorescent spectra or traces may be plotted in publication-appropriate
-quality with acquisition time in the x- and fluorescence intensity on the y-axis
+quality with acquisition time on the x- and fluorescence intensity on the y-axis
 using
@@
 by user-provided minimal (`timeMinSec` ) and maximal (`timeMaxSec`) time points
-to be (in seconds) included.
+to be included (in seconds).
 
@@
 
-Figure 1B emphasizes reproducebility between independent experiments
+Figure 1B emphasizes reproducibility between independent experiments
 ("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
@@
 The graphical representation of the fit constant $\alpha$ in the PPR plots is
-difficult to visually evaluate and easy access to the numeric values desireable.
+difficult to visually evaluate and easy access to the numeric values desirable.
 Recapitulation of the calculations underlying PPR plot generation for Figure 1C

### 2015-10-18 inst/manuscript/manuscript.rmd
Add a reference to the git hash at the time of compilation;
Enable compilation to all formats;

@@
 output:
-#  word_document
   pdf_document:
+    fig_caption: yes
+  word_document:
+    fig_caption: yes
+  html_document:
     fig_caption: yes
@@
 :   To whom correspondence should be addressed: jog2030@qatar-med.cornell.edu
+
+Current Git Hash
+:   `r system("git log -1 --format='%H'", intern = TRUE)`
 

### 2016-03-20 inst/manuscript/manuscript.rmd
Implement tracking of whether git is clean or not;
Adapt to new version of MultiPanelFigure;

@@
 :   `r system("git log -1 --format='%H'", intern = TRUE)`
+
+Git Clean
+:   `r ifelse(length(system("git status -s", intern = TRUE)) == 0, "TRUE", "FALSE")`
 
@@
 
-figure1 <- multipanelfigure(
+figure1 <- MultiPanelFigure(
   widths = rep(17.22/3-2*0.25, 3), 
@@
 setwd(tmpDir)
-figure1 <- addpanel(
+figure1 <- AddPanel(
   figure = figure1,
@@
   panel = scramblaseAssayTraces("inputTable.txt", timeMaxSec = 350) + theme_bw())
-figure1 <- addpanel(
+  panel = scramblaseAssayTraces(x, timeMaxSec = 350) + theme_bw())
+figure1 <- AddPanel(
   figure = figure1,
@@
     ylab(expression(P[{phantom()>=1}])))
-figure1 <- addpanel(
+figure1 <- AddPanel(
   figure = figure1,

### 2016-03-20 inst/manuscript/manuscript.rmd
Switch from 'round' to 'signif';

@@
     na.rm = TRUE) %>%
-  round(
+  signif(
     digits = 2
@@
 ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
-  round(2) %>%
+  signif(2) %>%
   head(n = nrow(ppr_results) - 1) %>%
@@
 
-analysis_timing_median <- round(
+analysis_timing_median <- signif(
   summary(
@@
 
-analysis_timing_iqr <- round(
+analysis_timing_iqr <- signif(
   diff(

### 2016-03-20 inst/manuscript/manuscript.rmd
Switch away from any usage of "setwd";

@@
 In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
-setwd(tmpDir)
+x <- flippant:::readScramblaseInputFile(
+  file.path(tmpDir,"inputTable.txt"))
+x[["Path"]] <- file.path(tmpDir, x[["Path"]])
 figure1 <- AddPanel(
@@
   rightPanel = 3, 
-  panel = scramblaseAssayTraces("inputTable.txt", timeMaxSec = 350) + theme_bw())
   panel = scramblaseAssayTraces(x, timeMaxSec = 350) + theme_bw())
@@
   rightPanel = 3, 
-  panel = scramblaseAssayPlot("inputTable.txt") + 
+  panel = scramblaseAssayPlot(x, formulaGeneration = 1) + 
     theme_bw() + 
@@
   rightPanel = 2,
-  panel = scramblaseAssayPlot("inputTable.txt", splitByExperiment = FALSE) + 
+  panel = scramblaseAssayPlot(x, formulaGeneration = 1,  splitByExperiment = FALSE) + 
     theme_bw() + 
@@
 # Plot PPR plot (Figure 1B)
-scramblaseAssayPlot("inputTable.txt") + xlim(0, 2)
+scramblaseAssayPlot("inputTable.txt", formulaGeneration = 1) + xlim(0, 2)
 ```
@@
 ```{r, echo = FALSE}
-setwd(tmpDir)
 max_PPR <- read.delim(
-    "inputTable.txt",
+    file.path(tmpDir,"inputTable.txt"),
     check.names = FALSE) %>%
@@
 # Plot PPR plot (Figure 1C)
-scramblaseAssayPlot("inputTable.txt", splitByExperiment = FALSE) + xlim(0, 2)
+scramblaseAssayPlot("inputTable.txt",
+  formulaGeneration = 1,
+  splitByExperiment = FALSE) + 
+xlim(0, 2)
 ```
@@
 # Write out results in tabular manner (Table 1)
-scramblaseAssayStats("inputTable.txt" splitByExperiment = FALSE)
+scramblaseAssayStats("inputTable.txt", formulaGeneration = 1, splitByExperiment = FALSE)
 ```
@@
 ```{r, echo = FALSE}
-setwd(tmpDir)
-ppr_results <- scramblaseAssayStats("inputTable.txt", splitByExperiment = FALSE)
+ppr_results <- scramblaseAssayStats(x, formulaGeneration = 1, splitByExperiment = FALSE)
 ppr_results_names <- ppr_results$`Experimental Series` %>%
@@
 ```{r, echo = FALSE, cache = TRUE}
-setwd(tmpDir)
 
@@
   scramblaseAssayTraces(
-    "inputTable.txt",
+    x,
     timeMaxSec = 350)
-  scramblaseAssayPlot("inputTable.txt")
-  scramblaseAssayPlot("inputTable.txt", splitByExperiment = FALSE)
-  scramblaseAssayStats("inputTable.txt", splitByExperiment = FALSE)
+  scramblaseAssayPlot(
+    x,
+    formulaGeneration = 1)
+  scramblaseAssayPlot(
+    x,
+    formulaGeneration = 1,
+    splitByExperiment = FALSE)
+  scramblaseAssayStats(
+    x,
+    formulaGeneration = 1, 
+    splitByExperiment = FALSE)
 }

### 2016-03-20 inst/manuscript/manuscript.rmd
Adapt funding statement to QNRF-preferred wording;

@@
 Research Program'' funds at Weill Cornell Medical College in Qatar, a program 
-funded by Qatar Foundation. B.P. was supported by a grant from Qatar National 
-Research Fund’s National Priority Research Program (5-669-1-112) to J.G. and
-A.K.M., as well as by the Austrian Science Fund (FWF), project J3686-B21.
+funded by Qatar Foundation. This study was made possible by NPRP grant
+5-669-1-112 from the Qatar National Research Fund (a member of Qatar 
+Foundation).The statements made herein are solely the responsibility of the
+authors. B.P. was also supported by the Austrian Science Fund (FWF), project
+J3686-B21.
 

### 2016-03-20 inst/manuscript/manuscript.rmd
Adapt to the change of fitting routine in flippant;

@@
 Deviations observed may stem from algorithmic differences such as the fitting 
-routine used (*flippant* uses the Nash variant of the Marquardt 
-nonlinear least squares algorithm as implemented by @nash_nlmrt:_2014) and 
+routine used (*flippant* uses the the Marquardt nonlinear least squares
+algorithm as implemented by @elzhov_minpack.lm:_2015) and 
 general handling of significant digits and rounding.

### 2016-05-03 inst/manuscript/manuscript.rmd
rename "formulaGeneration" to "generation_of_algorithm";

@@
   rightPanel = 3, 
-  panel = scramblaseAssayPlot(x, formulaGeneration = 1) + 
+  panel = scramblaseAssayPlot(x, generation_of_algorithm = 1) + 
     theme_bw() + 
@@
   rightPanel = 2,
-  panel = scramblaseAssayPlot(x, formulaGeneration = 1,  splitByExperiment = FALSE) + 
+  panel = scramblaseAssayPlot(x, generation_of_algorithm = 1,  splitByExperiment = FALSE) + 
     theme_bw() + 
@@
 # Plot PPR plot (Figure 1B)
-scramblaseAssayPlot("inputTable.txt", formulaGeneration = 1) + xlim(0, 2)
+scramblaseAssayPlot("inputTable.txt", generation_of_algorithm = 1) + xlim(0, 2)
 ```
@@
 scramblaseAssayPlot("inputTable.txt",
-  formulaGeneration = 1,
+  generation_of_algorithm = 1,
   splitByExperiment = FALSE) + 
@@
 # Write out results in tabular manner (Table 1)
-scramblaseAssayStats("inputTable.txt", formulaGeneration = 1, splitByExperiment = FALSE)
+scramblaseAssayStats("inputTable.txt", generation_of_algorithm = 1, splitByExperiment = FALSE)
 ```
@@
 ```{r, echo = FALSE}
-ppr_results <- scramblaseAssayStats(x, formulaGeneration = 1, splitByExperiment = FALSE)
+ppr_results <- scramblaseAssayStats(x, generation_of_algorithm = 1, splitByExperiment = FALSE)
 ppr_results_names <- ppr_results$`Experimental Series` %>%
@@
     x,
-    formulaGeneration = 1)
+    generation_of_algorithm = 1)
   scramblaseAssayPlot(
     x,
-    formulaGeneration = 1,
+    generation_of_algorithm = 1,
     splitByExperiment = FALSE)
@@
     x,
-    formulaGeneration = 1, 
+    generation_of_algorithm = 1, 
     splitByExperiment = FALSE)

### 2016-05-03 R/scramblaseAssayCalculations.R

@@ -2,7 +2,7 @@
 scramblaseAssayCalculations <- function(
   x,
   scaleTo,
-  formulaGeneration = 2,
+  generation_of_algorithm = 2,
   forceThroughOrigin = FALSE,
   splitByExperiment = TRUE){
 # Set parameters ----------------------------------------------------------
@@ -167,7 +167,7 @@ scramblaseAssayCalculations <- function(
         subsetForFit[["y"]],
         na.rm=TRUE) * 0.6
       estimatedA <- subsetForFit[["x"]][which.min(abs(subsetForFit[["y"]] - pointSixY))]
-      if(formulaGeneration == 1){
+      if(generation_of_algorithm == 1){
         ##> The dependence of p(≥1 flippase) on PPR was analyzed as follows.
         ##> Definitions:
         ##>   f, number of flippases used for reconstitution
@@ -222,7 +222,7 @@ scramblaseAssayCalculations <- function(
           },
           control = nlsControl)
         gc()
-      } else if(formulaGeneration == 2){
+      } else if(generation_of_algorithm == 2){
         ## p(≥1) = 1-(1/sqrt(1+784*α*PPR))*exp(-3872*α*PPR/(1+784*α*PPR))
         ## p(≥1) = 1 - e-m = 1 – exp(-PPR/α)
         # ## Fit a monoexponential curve to the data

### 2016-05-03 R/scramblaseAssayInputValidation.R

@@ -4,7 +4,7 @@
 scramblaseAssayInputValidation <- function(
   x,
   scaleTo,
-  formulaGeneration,
+  generation_of_algorithm,
   forceThroughOrigin,
   splitByExperiment,
   verbose=TRUE){
@@ -122,22 +122,22 @@ scramblaseAssayInputValidation <- function(
   if(scaleTo == "model" & verbose){
     message("Data will be scaled to the plateau of its monoexponential fit.")
   }
-  # Check formulaGeneration
-  formulaGeneration <- as.character(formulaGeneration)
-  if(identical(formulaGeneration, c("2","1"))){
-    formulaGeneration <- "2"
+  # Check generation_of_algorithm
+  generation_of_algorithm <- as.character(generation_of_algorithm)
+  if(identical(generation_of_algorithm, c("2","1"))){
+    generation_of_algorithm <- "2"
   }
-  formulaGeneration <- match.arg(
-    arg = formulaGeneration,
+  generation_of_algorithm <- match.arg(
+    arg = generation_of_algorithm,
     choices = c("second","first", "2", "1"),
     several.ok = FALSE)
-  if(formulaGeneration %in% c("first","1")){
-    formulaGeneration <- 1
-  } else if(formulaGeneration %in% c("second", "2")){
-    formulaGeneration <- 2
+  if(generation_of_algorithm %in% c("first","1")){
+    generation_of_algorithm <- 1
+  } else if(generation_of_algorithm %in% c("second", "2")){
+    generation_of_algorithm <- 2
   }
   if(verbose){
-    message("Data will be fitted to formula generation ", formulaGeneration, ".")
+    message("Data will be fitted to algorithm generation ", generation_of_algorithm, ".")
   }
   # Check forceThroughOrigin
   assert_is_a_bool(forceThroughOrigin)
@@ -148,7 +148,7 @@ scramblaseAssayInputValidation <- function(
     list(
       x = x,
       scaleTo = scaleTo,
-      formulaGeneration = formulaGeneration,
+      generation_of_algorithm = generation_of_algorithm,
       forceThroughOrigin = forceThroughOrigin,
       splitByExperiment = splitByExperiment))
 }

### 2016-05-03 R/scramblaseAssayPlot.R

@@ -176,7 +176,7 @@ scramblaseAssayPlot <- function(
   x,
   scaleTo = c("model","data"),
   forceThroughOrigin = FALSE,
-  formulaGeneration = c(2, 1),
+  generation_of_algorithm = c(2, 1),
   splitByExperiment = TRUE){
   UseMethod("scramblaseAssayPlot",x)
 }
@@ -193,19 +193,19 @@ baseFunctionScramblaseAssayPlot <- function(
   x,
   scaleTo = c("model","data"),
   forceThroughOrigin = FALSE,
-  formulaGeneration = c(2, 1),
+  generation_of_algorithm = c(2, 1),
   splitByExperiment = TRUE){
 # Check Prerequisites -----------------------------------------------------
   validatedParams <- flippant:::scramblaseAssayInputValidation(
     x = x ,
     scaleTo = scaleTo,
     forceThroughOrigin = forceThroughOrigin,
-    formulaGeneration = formulaGeneration,
+    generation_of_algorithm = generation_of_algorithm,
     splitByExperiment = splitByExperiment)
   x <- validatedParams[["x"]]
   scaleTo <- validatedParams[["scaleTo"]]
   forceThroughOrigin <- validatedParams[["forceThroughOrigin"]]
-  formulaGeneration <- validatedParams[["formulaGeneration"]]
+  generation_of_algorithm <- validatedParams[["generation_of_algorithm"]]
   splitByExperiment <- validatedParams[["splitByExperiment"]]
   
 # Processing --------------------------------------------------------------
@@ -213,7 +213,7 @@ baseFunctionScramblaseAssayPlot <- function(
     x = x,
     scaleTo = scaleTo,
     forceThroughOrigin = forceThroughOrigin,
-    formulaGeneration = formulaGeneration,
+    generation_of_algorithm = generation_of_algorithm,
     splitByExperiment = splitByExperiment)
 
 # Recombine the processed data --------------------------------------------

### 2016-05-03 R/scramblaseAssayStats.R

@@ -5,7 +5,7 @@ scramblaseAssayStats <- function(
   x,
   scaleTo = c("model","data"),
   forceThroughOrigin = FALSE,
-  formulaGeneration = c(2, 1),
+  generation_of_algorithm = c(2, 1),
   splitByExperiment = TRUE){
   UseMethod("scramblaseAssayStats",x)
 }
@@ -22,19 +22,19 @@ baseFunctionScramblaseAssayStats <- function(
   x,
   scaleTo = c("model","data"),
   forceThroughOrigin = FALSE,
-  formulaGeneration = c(2, 1),
+  generation_of_algorithm = c(2, 1),
   splitByExperiment = TRUE){
 # Check Prerequisites -----------------------------------------------------
   validatedParams <- scramblaseAssayInputValidation(
     x = x,
     scaleTo = scaleTo,
     forceThroughOrigin = forceThroughOrigin,
-    formulaGeneration = formulaGeneration,
+    generation_of_algorithm = generation_of_algorithm,
     splitByExperiment = splitByExperiment)
   x <- validatedParams[["x"]]
   scaleTo <- validatedParams[["scaleTo"]]
   forceThroughOrigin <- validatedParams[["forceThroughOrigin"]]
-  formulaGeneration <- validatedParams[["formulaGeneration"]]
+  generation_of_algorithm <- validatedParams[["generation_of_algorithm"]]
   splitByExperiment <- validatedParams[["splitByExperiment"]]
 
 # Processing --------------------------------------------------------------
@@ -42,7 +42,7 @@ baseFunctionScramblaseAssayStats <- function(
     x = x,
     scaleTo = scaleTo,
     forceThroughOrigin = forceThroughOrigin,
-    formulaGeneration = formulaGeneration,
+    generation_of_algorithm = generation_of_algorithm,
     splitByExperiment = splitByExperiment)
   processedListFromX <- lapply(processedListFromX,function(y){y[["Raw"]]})
 

### 2016-05-03 R/scramblaseAssayTraces.R

@@ -31,7 +31,7 @@ baseFunctionScramblaseAssayTraces <- function(
     x = x,
     scaleTo = "data",
     forceThroughOrigin = FALSE,
-    formulaGeneration = 2,
+    generation_of_algorithm = 2,
     splitByExperiment = TRUE,
     verbose = FALSE)
   x <- validatedParams[["x"]]

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "scramblaseAssayTraces" to "scramblase_assay_traces";

@@
 
-```{r, code = formatR::usage('scramblaseAssayTraces'), eval = FALSE}
+```{r, code = formatR::usage('scramblase_assay_traces'), eval = FALSE}
 ```
@@
 # Plot spectral traces (Figure 1A)
-scramblaseAssayTraces("inputTable.txt", timeMaxSec = 350)
+scramblase_assay_traces("inputTable.txt", timeMaxSec = 350)
 ```
 
-```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblaseAssayTraces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details).
+```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details).
 In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
@@
   rightPanel = 3, 
-  panel = scramblaseAssayTraces(x, timeMaxSec = 350) + theme_bw())
+  panel = scramblase_assay_traces(x, timeMaxSec = 350) + theme_bw())
 figure1 <- AddPanel(
@@
 analysis_timing_function <- function(){
-  scramblaseAssayTraces(
+  scramblase_assay_traces(
     x,

### 2016-05-03 R/scramblaseAssayPlot.R

@@ -1,6 +1,6 @@
 #' @title scramblaseAssayPlot
 #' @aliases scrambalseAssayCalculations scramblaseAssayInputTemplate 
-#' scramblaseAssayPlot scramblaseAssayStats scramblaseAssayTraces
+#' scramblaseAssayPlot scramblaseAssayStats scramblase_assay_traces
 #' @description Functions for the presentation and evaluaton of dithionite 
 #' scramblase assays
 #' @details The \code{\link{data.frame}} accepted by the majority of the 
@@ -114,10 +114,10 @@
 #' @param forceThroughOrigin \code{\link{logical}} indicating whether to force 
 #' the fitted curve(s) to penetrate the origin (defaulting to \code{FALSE}).
 #' @param timeMinSec A single \code{\link{numeric}}. If given, 
-#' \code{\link{scramblaseAssayTraces}} produces a time/x axis trimmed to
+#' \code{\link{scramblase_assay_traces}} produces a time/x axis trimmed to
 #' this value (in seconds).
 #' @param timeMaxSec A single \code{\link{numeric}}. If given, 
-#' \code{\link{scramblaseAssayTraces}} produces a time/x axis trimmed to
+#' \code{\link{scramblase_assay_traces}} produces a time/x axis trimmed to
 #' this value (in seconds).
 #' @param adjust A single \code{\link{logical}}, indicating whether (default) or 
 #' not spectral traces to be plotted are algorithmically aligned at the time
@@ -161,7 +161,7 @@
 #'   exdir = tmpDir)
 #' setwd(tmpDir)
 #' # Plot the spectal traces
-#' scramblaseAssayTraces(
+#' scramblase_assay_traces(
 #'   "inputTable.txt",
 #'   timeMaxSec = 350)
 #' # Plot the PPR plot(s) faceting by experiment

### 2016-05-03 R/scramblase_assay_traces.R

@@ -3,25 +3,25 @@
 #' @importFrom assertive assert_is_a_number
 #' @importFrom plyr rbind.fill
 #' @export
-scramblaseAssayTraces <- function(
+scramblase_assay_traces <- function(
   x,
   timeMinSec=NA_real_,
   timeMaxSec=NA_real_,
   adjust = TRUE){
-  UseMethod("scramblaseAssayTraces", x)
+  UseMethod("scramblase_assay_traces", x)
 }
 #' @export
-scramblaseAssayTraces.data.frame <- function(
+scramblase_assay_traces.data.frame <- function(
   x,
   ...){
-  baseFunctionScramblaseAssayTraces(x, ...)
+  base_function_scramblase_assay_traces(x, ...)
 }
 #' @export
-scramblaseAssayTraces.character <- function(x, ...){
+scramblase_assay_traces.character <- function(x, ...){
   parsedInputFile <- readScramblaseInputFile(x)
-  baseFunctionScramblaseAssayTraces(x=parsedInputFile, ...)
+  base_function_scramblase_assay_traces(x=parsedInputFile, ...)
 }
-baseFunctionScramblaseAssayTraces <- function(
+base_function_scramblase_assay_traces <- function(
   x,
   timeMinSec=NA_real_,
   timeMaxSec=NA_real_,

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "scramblaseAssayPlot" to "scramblase_assay_plot";

@@
 
-```{r, code = formatR::usage('scramblaseAssayPlot'), eval = FALSE}
+```{r, code = formatR::usage('scramblase_assay_plot'), eval = FALSE}
 ```
@@
 
-with the same modifying arguments to the function as for `scramblaseAssayPlot`.
+with the same modifying arguments to the function as for `scramblase_assay_plot`.
 
@@
   rightPanel = 3, 
-  panel = scramblaseAssayPlot(x, generation_of_algorithm = 1) + 
+  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
     theme_bw() + 
@@
   rightPanel = 2,
-  panel = scramblaseAssayPlot(x, generation_of_algorithm = 1,  splitByExperiment = FALSE) + 
+  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  splitByExperiment = FALSE) + 
     theme_bw() + 
@@
 # Plot PPR plot (Figure 1B)
-scramblaseAssayPlot("inputTable.txt", generation_of_algorithm = 1) + xlim(0, 2)
+scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 1) + xlim(0, 2)
 ```
@@
 # Plot PPR plot (Figure 1C)
-scramblaseAssayPlot("inputTable.txt",
+scramblase_assay_plot("inputTable.txt",
   generation_of_algorithm = 1,
@@
 Recapitulation of the calculations underlying PPR plot generation for Figure 1C
-by `scramblaseAssayPlot` in a call to `scramblaseAssayStats`, this is achieved
+by `scramblase_assay_plot` in a call to `scramblaseAssayStats`, this is achieved
 and produces tabular output represented in Table 1.
@@
     timeMaxSec = 350)
-  scramblaseAssayPlot(
+  scramblase_assay_plot(
     x,
     generation_of_algorithm = 1)
-  scramblaseAssayPlot(
+  scramblase_assay_plot(
     x,

### 2016-05-03 R/scramblaseAssayInputTemplate.R

@@ -1,4 +1,4 @@
-#' @rdname scramblaseAssayPlot
+#' @rdname scramblase_assay_plot
 #' @importFrom assertive assert_any_are_existing_files
 #' @importFrom assertive assert_is_a_non_empty_string
 #' @importFrom plyr rbind.fill

### 2016-05-03 R/scramblaseAssayStats.R

@@ -1,4 +1,4 @@
-#' @rdname scramblaseAssayPlot
+#' @rdname scramblase_assay_plot
 #' @importFrom plyr rbind.fill
 #' @export
 scramblaseAssayStats <- function(

### 2016-05-03 R/scramblase_assay_plot.R

@@ -1,6 +1,6 @@
-#' @title scramblaseAssayPlot
+#' @title scramblase_assay_plot
 #' @aliases scrambalseAssayCalculations scramblaseAssayInputTemplate 
-#' scramblaseAssayPlot scramblaseAssayStats scramblase_assay_traces
+#' scramblase_assay_plot scramblaseAssayStats scramblase_assay_traces
 #' @description Functions for the presentation and evaluaton of dithionite 
 #' scramblase assays
 #' @details The \code{\link{data.frame}} accepted by the majority of the 
@@ -128,7 +128,7 @@
 #' experiments included is used for a single calculation/plot per experimental
 #' series (\code{FALSE}). While the former emphasizes reproducibility, the
 #' latter likely produces a more reliable fit.
-#' @return \code{scrambalseAssayTraces} and \code{scramblaseAssayPlot} return 
+#' @return \code{scrambalse_assay_traces} and \code{scramblase_assay_plot} return 
 #' \code{\link{ggplot}} objects representing the raw fluorescence traces and a
 #' complete PPR plot, respectively. \code{scrambalseAssayInputTemplate} 
 #' generates a tab-delimited \code{ASCII} file in the file system and does not
@@ -165,31 +165,31 @@
 #'   "inputTable.txt",
 #'   timeMaxSec = 350)
 #' # Plot the PPR plot(s) faceting by experiment
-#' scramblaseAssayPlot("inputTable.txt")
+#' scramblase_assay_plot("inputTable.txt")
 #' # Generate tabular results
 #' scramblaseAssayStats("inputTable.txt")
 #' # Plot the PPR plot(s) forgoing faceting by experiment
-#' scramblaseAssayPlot("inputTable.txt", splitByExperiment = FALSE)
+#' scramblase_assay_plot("inputTable.txt", splitByExperiment = FALSE)
 #' # Generate tabular results
 #' scramblaseAssayStats("inputTable.txt", splitByExperiment = FALSE)
-scramblaseAssayPlot <- function(
+scramblase_assay_plot <- function(
   x,
   scaleTo = c("model","data"),
   forceThroughOrigin = FALSE,
   generation_of_algorithm = c(2, 1),
   splitByExperiment = TRUE){
-  UseMethod("scramblaseAssayPlot",x)
+  UseMethod("scramblase_assay_plot",x)
 }
 #' @export
[…]

### 2016-05-03 R/scramblase_assay_traces.R

@@ -1,4 +1,4 @@
-#' @rdname scramblaseAssayPlot
+#' @rdname scramblase_assay_plot
 #' @import ggplot2
 #' @importFrom assertive assert_is_a_number
 #' @importFrom plyr rbind.fill

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "timeMinSec" to "time_min_sec";

@@
 time of dithionite addition. Acquisition time coverage of the plot may be tuned 
-by user-provided minimal (`timeMinSec` ) and maximal (`timeMaxSec`) time points
+by user-provided minimal (`time_min_sec` ) and maximal (`timeMaxSec`) time points
 to be included (in seconds).

### 2016-05-03 R/scramblase_assay_plot.R

@@ -113,7 +113,7 @@
 #' \code{model}. See "Details".
 #' @param forceThroughOrigin \code{\link{logical}} indicating whether to force 
 #' the fitted curve(s) to penetrate the origin (defaulting to \code{FALSE}).
-#' @param timeMinSec A single \code{\link{numeric}}. If given, 
+#' @param time_min_sec A single \code{\link{numeric}}. If given, 
 #' \code{\link{scramblase_assay_traces}} produces a time/x axis trimmed to
 #' this value (in seconds).
 #' @param timeMaxSec A single \code{\link{numeric}}. If given, 

### 2016-05-03 R/scramblase_assay_traces.R

@@ -5,7 +5,7 @@
 #' @export
 scramblase_assay_traces <- function(
   x,
-  timeMinSec=NA_real_,
+  time_min_sec=NA_real_,
   timeMaxSec=NA_real_,
   adjust = TRUE){
   UseMethod("scramblase_assay_traces", x)
@@ -23,7 +23,7 @@ scramblase_assay_traces.character <- function(x, ...){
 }
 base_function_scramblase_assay_traces <- function(
   x,
-  timeMinSec=NA_real_,
+  time_min_sec=NA_real_,
   timeMaxSec=NA_real_,
   adjust = TRUE){
 # Check Prerequisites -----------------------------------------------------
@@ -35,7 +35,7 @@ base_function_scramblase_assay_traces <- function(
     splitByExperiment = TRUE,
     verbose = FALSE)
   x <- validatedParams[["x"]]
-  assert_is_a_number(timeMinSec)
+  assert_is_a_number(time_min_sec)
   assert_is_a_number(timeMaxSec)
 
 # Processing --------------------------------------------------------------
@@ -76,9 +76,9 @@ base_function_scramblase_assay_traces <- function(
   # Plot traces with lines
   plotOutput <- plotOutput + geom_line()
   # Restrict x axis as requested
-  if(any(!is.na(c(timeMinSec,timeMaxSec)))){
+  if(any(!is.na(c(time_min_sec,timeMaxSec)))){
     xRange <- range(mergedData$Time.in.sec, na.rm=TRUE)
-    if(!is.na(timeMinSec)){xRange[1] <- timeMinSec}
+    if(!is.na(time_min_sec)){xRange[1] <- time_min_sec}
     if(!is.na(timeMaxSec)){xRange[2] <- timeMaxSec}
     plotOutput <- plotOutput + xlim(xRange)
   }

### 2016-05-03 R/scramblase_assay_plot.R
Rename "timeMaxSec" to "time_max_sec";

@@ -116,7 +116,7 @@
 #' @param time_min_sec A single \code{\link{numeric}}. If given, 
 #' \code{\link{scramblase_assay_traces}} produces a time/x axis trimmed to
 #' this value (in seconds).
-#' @param timeMaxSec A single \code{\link{numeric}}. If given, 
+#' @param time_max_sec A single \code{\link{numeric}}. If given, 
 #' \code{\link{scramblase_assay_traces}} produces a time/x axis trimmed to
 #' this value (in seconds).
 #' @param adjust A single \code{\link{logical}}, indicating whether (default) or 
@@ -163,7 +163,7 @@
 #' # Plot the spectal traces
 #' scramblase_assay_traces(
 #'   "inputTable.txt",
-#'   timeMaxSec = 350)
+#'   time_max_sec = 350)
 #' # Plot the PPR plot(s) faceting by experiment
 #' scramblase_assay_plot("inputTable.txt")
 #' # Generate tabular results

### 2016-05-03 R/scramblase_assay_traces.R

@@ -6,7 +6,7 @@
 scramblase_assay_traces <- function(
   x,
   time_min_sec=NA_real_,
-  timeMaxSec=NA_real_,
+  time_max_sec=NA_real_,
   adjust = TRUE){
   UseMethod("scramblase_assay_traces", x)
 }
@@ -24,7 +24,7 @@ scramblase_assay_traces.character <- function(x, ...){
 base_function_scramblase_assay_traces <- function(
   x,
   time_min_sec=NA_real_,
-  timeMaxSec=NA_real_,
+  time_max_sec=NA_real_,
   adjust = TRUE){
 # Check Prerequisites -----------------------------------------------------
   validatedParams <- scramblaseAssayInputValidation(
@@ -36,7 +36,7 @@ base_function_scramblase_assay_traces <- function(
     verbose = FALSE)
   x <- validatedParams[["x"]]
   assert_is_a_number(time_min_sec)
-  assert_is_a_number(timeMaxSec)
+  assert_is_a_number(time_max_sec)
 
 # Processing --------------------------------------------------------------
   # Perform assay calculations to retrive PPR
@@ -76,10 +76,10 @@ base_function_scramblase_assay_traces <- function(
   # Plot traces with lines
   plotOutput <- plotOutput + geom_line()
   # Restrict x axis as requested
-  if(any(!is.na(c(time_min_sec,timeMaxSec)))){
+  if(any(!is.na(c(time_min_sec,time_max_sec)))){
     xRange <- range(mergedData$Time.in.sec, na.rm=TRUE)
     if(!is.na(time_min_sec)){xRange[1] <- time_min_sec}
-    if(!is.na(timeMaxSec)){xRange[2] <- timeMaxSec}
+    if(!is.na(time_max_sec)){xRange[2] <- time_max_sec}
     plotOutput <- plotOutput + xlim(xRange)
   }
   # Render color scale friendly to the color blind

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "scramblaseAssayStats" to "scramblase_assay_stats";

@@
 
-```{r, code = formatR::usage('scramblaseAssayStats'), eval = FALSE}
+```{r, code = formatR::usage('scramblase_assay_stats'), eval = FALSE}
 ```
@@
 Recapitulation of the calculations underlying PPR plot generation for Figure 1C
-by `scramblase_assay_plot` in a call to `scramblaseAssayStats`, this is achieved
+by `scramblase_assay_plot` in a call to `scramblase_assay_stats`, this is achieved
 and produces tabular output represented in Table 1.
@@
 # Write out results in tabular manner (Table 1)
-scramblaseAssayStats("inputTable.txt", generation_of_algorithm = 1, splitByExperiment = FALSE)
+scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, splitByExperiment = FALSE)
 ```
@@
 ```{r, echo = FALSE}
-ppr_results <- scramblaseAssayStats(x, generation_of_algorithm = 1, splitByExperiment = FALSE)
+ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, splitByExperiment = FALSE)
 ppr_results_names <- ppr_results$`Experimental Series` %>%
@@
   row.names = FALSE,
-  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblaseAssayStats`.")
+  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblase_assay_stats`.")
 ```
@@
     splitByExperiment = FALSE)
-  scramblaseAssayStats(
+  scramblase_assay_stats(
     x,

### 2016-05-03 R/scramblase_assay_plot.R

@@ -1,6 +1,6 @@
 #' @title scramblase_assay_plot
 #' @aliases scrambalseAssayCalculations scramblaseAssayInputTemplate 
-#' scramblase_assay_plot scramblaseAssayStats scramblase_assay_traces
+#' scramblase_assay_plot scramblase_assay_stats scramblase_assay_traces
 #' @description Functions for the presentation and evaluaton of dithionite 
 #' scramblase assays
 #' @details The \code{\link{data.frame}} accepted by the majority of the 
@@ -167,11 +167,11 @@
 #' # Plot the PPR plot(s) faceting by experiment
 #' scramblase_assay_plot("inputTable.txt")
 #' # Generate tabular results
-#' scramblaseAssayStats("inputTable.txt")
+#' scramblase_assay_stats("inputTable.txt")
 #' # Plot the PPR plot(s) forgoing faceting by experiment
 #' scramblase_assay_plot("inputTable.txt", splitByExperiment = FALSE)
 #' # Generate tabular results
-#' scramblaseAssayStats("inputTable.txt", splitByExperiment = FALSE)
+#' scramblase_assay_stats("inputTable.txt", splitByExperiment = FALSE)
 scramblase_assay_plot <- function(
   x,
   scaleTo = c("model","data"),

### 2016-05-03 R/scramblase_assay_stats.R

@@ -1,24 +1,24 @@
 #' @rdname scramblase_assay_plot
 #' @importFrom plyr rbind.fill
 #' @export
-scramblaseAssayStats <- function(
+scramblase_assay_stats <- function(
   x,
   scaleTo = c("model","data"),
   forceThroughOrigin = FALSE,
   generation_of_algorithm = c(2, 1),
   splitByExperiment = TRUE){
-  UseMethod("scramblaseAssayStats",x)
+  UseMethod("scramblase_assay_stats",x)
 }
 #' @export
-scramblaseAssayStats.data.frame <- function(x, ...){
-  baseFunctionScramblaseAssayStats(x, ...)
+scramblase_assay_stats.data.frame <- function(x, ...){
+  base_function_scramblase_assay_stats(x, ...)
 }
 #' @export
-scramblaseAssayStats.character <- function(x, ...){
+scramblase_assay_stats.character <- function(x, ...){
   parsedInputFile <- readScramblaseInputFile(x)
-  baseFunctionScramblaseAssayStats(x=parsedInputFile, ...)
+  base_function_scramblase_assay_stats(x=parsedInputFile, ...)
 }
-baseFunctionScramblaseAssayStats <- function(
+base_function_scramblase_assay_stats <- function(
   x,
   scaleTo = c("model","data"),
   forceThroughOrigin = FALSE,

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "scaleTo" to "scale_to";

@@
 case where the protein/phospholipid titration did not reach the plateau of the 
-saturation curve. The behavior is adjustable using the `scaleTo` parameter of 
+saturation curve. The behavior is adjustable using the `scale_to` parameter of 
 the corresponding functions (see below). Next a monoexponential curve is fitted
@@
 adjusted to use scramblase-mediated fluorescence reduction normalized to either
-the maximum measurement in the series (`scaleTo = "data"`) or the plateau of an
-exponential fit to it (`scaleTo = "model"`; for reasoning see above) and whether
+the maximum measurement in the series (`scale_to = "data"`) or the plateau of an
+exponential fit to it (`scale_to = "model"`; for reasoning see above) and whether
 or not to require the exponential curve fitted to the data to go through the

### 2016-05-03 R/scramblaseAssayCalculations.R

@@ -1,7 +1,7 @@
 #' @importFrom minpack.lm nlsLM
 scramblaseAssayCalculations <- function(
   x,
-  scaleTo,
+  scale_to,
   generation_of_algorithm = 2,
   forceThroughOrigin = FALSE,
   splitByExperiment = TRUE){
@@ -116,7 +116,7 @@ scramblaseAssayCalculations <- function(
       ## Calculate p>=1Scramblase/Liposome
       y <- z[["Relative Fluorescence Reduction"]]
       y0 <- z[["Relative Fluorescence Reduction"]][indexOfLiposomesOnlyData]
-      if(scaleTo == "model"){
+      if(scale_to == "model"){
         subsetForFit <- data.frame(
           x=z[["Protein per Phospholipid (mg/mmol)"]],
           y=z[["Relative Fluorescence Reduction"]])

### 2016-05-03 R/scramblaseAssayInputValidation.R

@@ -3,7 +3,7 @@
 #' @importFrom assertive assert_is_data.frame
 scramblaseAssayInputValidation <- function(
   x,
-  scaleTo,
+  scale_to,
   generation_of_algorithm,
   forceThroughOrigin,
   splitByExperiment,
@@ -114,12 +114,12 @@ scramblaseAssayInputValidation <- function(
       "'.")
   }
 
-  # Check scaleTo
-  scaleTo <- match.arg(
-    arg=scaleTo,
+  # Check scale_to
+  scale_to <- match.arg(
+    arg=scale_to,
     choices=c("model","data"),
     several.ok=FALSE)
-  if(scaleTo == "model" & verbose){
+  if(scale_to == "model" & verbose){
     message("Data will be scaled to the plateau of its monoexponential fit.")
   }
   # Check generation_of_algorithm
@@ -147,7 +147,7 @@ scramblaseAssayInputValidation <- function(
   return(
     list(
       x = x,
-      scaleTo = scaleTo,
+      scale_to = scale_to,
       generation_of_algorithm = generation_of_algorithm,
       forceThroughOrigin = forceThroughOrigin,
       splitByExperiment = splitByExperiment))

### 2016-05-03 R/scramblase_assay_plot.R

@@ -75,10 +75,10 @@
 #'    \deqn{\frac{y-y_0}{y_{\mbox{\scriptsize max}}-y_0}}{(y - y0)/(ymax - y0)}
 #'    where \eqn{y} is the \code{Relative Fluorescence Reduction} and \eqn{y_0}{y0}
 #'    is the \code{Relative Fluorescence Reduction} in an experiment without
-#'    addition of protein extract. Depending on the \code{scaleTo} parameter, 
+#'    addition of protein extract. Depending on the \code{scale_to} parameter, 
 #'    \eqn{y_{\mbox{\scriptsize max}}}{ymax} is either the maximal \code{Relative Fluorescence Reduction} 
-#'    in the series (\code{scaleTo = "data"}) or derived from a 
-#'    mono-exponential fit to the data (\code{scaleTo = "model"}). The latter 
+#'    in the series (\code{scale_to = "data"}) or derived from a 
+#'    mono-exponential fit to the data (\code{scale_to = "model"}). The latter 
 #'    (default) is a precaution for the case where the protein/phospholipid
 #'    titration did not reach the plateau of the saturation curve.}
 #'  \item{A monoexponential curve is fitted unsig \code{\link{nlsLM}} to either
@@ -109,7 +109,7 @@
 #' template for a spreadsheet that can provide \code{x}.
 #' @param x \code{\link{data.frame}} or path to a tab delimited file 
 #' representing it (see "Details").
-#' @param scaleTo Defines the source of \code{ymax}, defaulting to 
+#' @param scale_to Defines the source of \code{ymax}, defaulting to 
 #' \code{model}. See "Details".
 #' @param forceThroughOrigin \code{\link{logical}} indicating whether to force 
 #' the fitted curve(s) to penetrate the origin (defaulting to \code{FALSE}).
@@ -174,7 +174,7 @@
 #' scramblase_assay_stats("inputTable.txt", splitByExperiment = FALSE)
 scramblase_assay_plot <- function(
   x,
-  scaleTo = c("model","data"),
+  scale_to = c("model","data"),
   forceThroughOrigin = FALSE,
   generation_of_algorithm = c(2, 1),
   splitByExperiment = TRUE){
@@ -191,19 +191,19 @@ scramblase_assay_plot.character <- function(x, ...){
 }
 base_function_scramblase_assay_plot <- function(
   x,
-  scaleTo = c("model","data"),
+  scale_to = c("model","data"),
   forceThroughOrigin = FALSE,
[…]

### 2016-05-03 R/scramblase_assay_stats.R

@@ -3,7 +3,7 @@
 #' @export
 scramblase_assay_stats <- function(
   x,
-  scaleTo = c("model","data"),
+  scale_to = c("model","data"),
   forceThroughOrigin = FALSE,
   generation_of_algorithm = c(2, 1),
   splitByExperiment = TRUE){
@@ -20,19 +20,19 @@ scramblase_assay_stats.character <- function(x, ...){
 }
 base_function_scramblase_assay_stats <- function(
   x,
-  scaleTo = c("model","data"),
+  scale_to = c("model","data"),
   forceThroughOrigin = FALSE,
   generation_of_algorithm = c(2, 1),
   splitByExperiment = TRUE){
 # Check Prerequisites -----------------------------------------------------
   validatedParams <- scramblaseAssayInputValidation(
     x = x,
-    scaleTo = scaleTo,
+    scale_to = scale_to,
     forceThroughOrigin = forceThroughOrigin,
     generation_of_algorithm = generation_of_algorithm,
     splitByExperiment = splitByExperiment)
   x <- validatedParams[["x"]]
-  scaleTo <- validatedParams[["scaleTo"]]
+  scale_to <- validatedParams[["scale_to"]]
   forceThroughOrigin <- validatedParams[["forceThroughOrigin"]]
   generation_of_algorithm <- validatedParams[["generation_of_algorithm"]]
   splitByExperiment <- validatedParams[["splitByExperiment"]]
@@ -40,7 +40,7 @@ base_function_scramblase_assay_stats <- function(
 # Processing --------------------------------------------------------------
   processedListFromX <- scramblaseAssayCalculations(
     x = x,
-    scaleTo = scaleTo,
+    scale_to = scale_to,
     forceThroughOrigin = forceThroughOrigin,
     generation_of_algorithm = generation_of_algorithm,
     splitByExperiment = splitByExperiment)

### 2016-05-03 R/scramblase_assay_traces.R

@@ -29,7 +29,7 @@ base_function_scramblase_assay_traces <- function(
 # Check Prerequisites -----------------------------------------------------
   validatedParams <- scramblaseAssayInputValidation(
     x = x,
-    scaleTo = "data",
+    scale_to = "data",
     forceThroughOrigin = FALSE,
     generation_of_algorithm = 2,
     splitByExperiment = TRUE,

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "splitByExperiment" into "split_by_experiment";

@@
 or not to require the exponential curve fitted to the data to go through the
-origin. The `splitByExperiment` argument is used to indicate whether independent
-experiments are integrated into a single analysis (`splitByExperiment = FALSE`)
-or treated separately (`splitByExperiment = TRUE`; see below for example usage).
+origin. The `split_by_experiment` argument is used to indicate whether independent
+experiments are integrated into a single analysis (`split_by_experiment = FALSE`)
+or treated separately (`split_by_experiment = TRUE`; see below for example usage).
 
@@
   rightPanel = 2,
-  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  splitByExperiment = FALSE) + 
+  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  split_by_experiment = FALSE) + 
     theme_bw() + 
@@
   generation_of_algorithm = 1,
-  splitByExperiment = FALSE) + 
+  split_by_experiment = FALSE) + 
 xlim(0, 2)
@@
 # Write out results in tabular manner (Table 1)
-scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, splitByExperiment = FALSE)
+scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, split_by_experiment = FALSE)
 ```
@@
 ```{r, echo = FALSE}
-ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, splitByExperiment = FALSE)
+ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, split_by_experiment = FALSE)
 ppr_results_names <- ppr_results$`Experimental Series` %>%
@@
     generation_of_algorithm = 1,
-    splitByExperiment = FALSE)
+    split_by_experiment = FALSE)
   scramblase_assay_stats(
@@
     generation_of_algorithm = 1, 
-    splitByExperiment = FALSE)
+    split_by_experiment = FALSE)
 }

### 2016-05-03 R/scramblaseAssayCalculations.R

@@ -4,7 +4,7 @@ scramblaseAssayCalculations <- function(
   scale_to,
   generation_of_algorithm = 2,
   force_through_origin = FALSE,
-  splitByExperiment = TRUE){
+  split_by_experiment = TRUE){
 # Set parameters ----------------------------------------------------------
   nlsControl <- list(
     minFactor=1/20480,
@@ -151,7 +151,7 @@ scramblaseAssayCalculations <- function(
       return(z)
     })
   # Is separate handling of experiments required?
-  if(!splitByExperiment){
+  if(!split_by_experiment){
     processedListFromX <- rbind.fill(processedListFromX)
     processedListFromX <- split(processedListFromX,processedListFromX$"Experimental Series")
   }

### 2016-05-03 R/scramblaseAssayInputValidation.R

@@ -6,7 +6,7 @@ scramblaseAssayInputValidation <- function(
   scale_to,
   generation_of_algorithm,
   force_through_origin,
-  splitByExperiment,
+  split_by_experiment,
   verbose=TRUE){
   # Check verbose
   assert_is_a_bool(verbose)
@@ -141,8 +141,8 @@ scramblaseAssayInputValidation <- function(
   }
   # Check force_through_origin
   assert_is_a_bool(force_through_origin)
-  # Check splitByExperiment
-  assert_is_a_bool(splitByExperiment)
+  # Check split_by_experiment
+  assert_is_a_bool(split_by_experiment)
   # Return
   return(
     list(
@@ -150,5 +150,5 @@ scramblaseAssayInputValidation <- function(
       scale_to = scale_to,
       generation_of_algorithm = generation_of_algorithm,
       force_through_origin = force_through_origin,
-      splitByExperiment = splitByExperiment))
+      split_by_experiment = split_by_experiment))
 }

### 2016-05-03 R/scramblase_assay_plot.R

@@ -65,11 +65,11 @@
 #'    to the liposomes-only/no-protein control).}
 #'  \item{A \code{Protein per Phospholipid (mg/mmol)} ratio (\code{PPR}) is 
 #'    calculated.}
-#'  \item{Depending on \code{splitByExperiment}, data are \code{\link{split}} 
+#'  \item{Depending on \code{split_by_experiment}, data are \code{\link{split}} 
 #'    for parallel treatment using either \code{Experimental Series}
-#'    (\code{splitByExperiment = TRUE}) or a combined
+#'    (\code{split_by_experiment = TRUE}) or a combined
 #'     \code{Experimental Series}/\code{Experiment}
-#'     (\code{splitByExperiment = FALSE}) identifier (see above).}
+#'     (\code{split_by_experiment = FALSE}) identifier (see above).}
 #'  \item{A probability for a liposome holding \eqn{\geq 1}{\ge 1} scramblase 
 #'    molecules is calculated using 
 #'    \deqn{\frac{y-y_0}{y_{\mbox{\scriptsize max}}-y_0}}{(y - y0)/(ymax - y0)}
@@ -102,7 +102,7 @@
 #'        datapoints. \code{color} is used to differentiate 
 #'        \code{Experimental Series}.}
 #'      \item{Plots are finally \code{\link{facet_wrap}}ed by \code{Experiment} 
-#'        (if \code{splitByExperiment = TRUE}) and labels adjusted
+#'        (if \code{split_by_experiment = TRUE}) and labels adjusted
 #'        cosmetically.}}
 #'  }}
 #' @param path \code{\link{character}} object giving the path of an \bold{empty}
@@ -122,7 +122,7 @@
 #' @param adjust A single \code{\link{logical}}, indicating whether (default) or 
 #' not spectral traces to be plotted are algorithmically aligned at the time
 #' point of dithionite addition.
-#' @param splitByExperiment A single \code{\link{logical}}, indicating whether or
+#' @param split_by_experiment A single \code{\link{logical}}, indicating whether or
 #' not calculations and plots will treat experimental series from different
 #' experiments separately (\code{TRUE}, default) or whether data from all
 #' experiments included is used for a single calculation/plot per experimental
@@ -169,15 +169,15 @@
 #' # Generate tabular results
 #' scramblase_assay_stats("inputTable.txt")
 #' # Plot the PPR plot(s) forgoing faceting by experiment
[…]

### 2016-05-03 R/scramblase_assay_stats.R

@@ -6,7 +6,7 @@ scramblase_assay_stats <- function(
   scale_to = c("model","data"),
   force_through_origin = FALSE,
   generation_of_algorithm = c(2, 1),
-  splitByExperiment = TRUE){
+  split_by_experiment = TRUE){
   UseMethod("scramblase_assay_stats",x)
 }
 #' @export
@@ -23,19 +23,19 @@ base_function_scramblase_assay_stats <- function(
   scale_to = c("model","data"),
   force_through_origin = FALSE,
   generation_of_algorithm = c(2, 1),
-  splitByExperiment = TRUE){
+  split_by_experiment = TRUE){
 # Check Prerequisites -----------------------------------------------------
   validatedParams <- scramblaseAssayInputValidation(
     x = x,
     scale_to = scale_to,
     force_through_origin = force_through_origin,
     generation_of_algorithm = generation_of_algorithm,
-    splitByExperiment = splitByExperiment)
+    split_by_experiment = split_by_experiment)
   x <- validatedParams[["x"]]
   scale_to <- validatedParams[["scale_to"]]
   force_through_origin <- validatedParams[["force_through_origin"]]
   generation_of_algorithm <- validatedParams[["generation_of_algorithm"]]
-  splitByExperiment <- validatedParams[["splitByExperiment"]]
+  split_by_experiment <- validatedParams[["split_by_experiment"]]
 
 # Processing --------------------------------------------------------------
   processedListFromX <- scramblaseAssayCalculations(
@@ -43,17 +43,17 @@ base_function_scramblase_assay_stats <- function(
     scale_to = scale_to,
     force_through_origin = force_through_origin,
     generation_of_algorithm = generation_of_algorithm,
-    splitByExperiment = splitByExperiment)
+    split_by_experiment = split_by_experiment)
   processedListFromX <- lapply(processedListFromX,function(y){y[["Raw"]]})
 
 # Assemble the output -----------------------------------------
   output <- plyr::rbind.fill(processedListFromX)
-  if(splitByExperiment){
+  if(split_by_experiment){
    output <- output[!duplicated(output$CombinedId),]
   } else {
     output <- output[!duplicated(output$`Experimental Series`),]
   }
-  if(splitByExperiment){
+  if(split_by_experiment){
     columns <- c("Fit Constant (a)","Experimental Series","Experiment")
   } else {
     columns <- c("Fit Constant (a)","Experimental Series")

### 2016-05-03 R/scramblase_assay_traces.R

@@ -32,7 +32,7 @@ base_function_scramblase_assay_traces <- function(
     scale_to = "data",
     force_through_origin = FALSE,
     generation_of_algorithm = 2,
-    splitByExperiment = TRUE,
+    split_by_experiment = TRUE,
     verbose = FALSE)
   x <- validatedParams[["x"]]
   assert_is_a_number(time_min_sec)

### 2016-05-03 R/scramblase_assay_input_template.R
Rename "scramblaseAssayInputTemplate" to "scramblase_assay_input_template";

@@ -3,7 +3,7 @@
 #' @importFrom assertive assert_is_a_non_empty_string
 #' @importFrom plyr rbind.fill
 #' @export
-scramblaseAssayInputTemplate <- function(path="scramblaseAssayInputTemplate.txt"){
+scramblase_assay_input_template <- function(path="scramblase_assay_input_template.txt"){
 # Check input -------------------------------------------------------------
   assert_is_a_non_empty_string(path)
   assert_any_are_existing_files(path)

### 2016-05-03 R/scramblase_assay_plot.R

@@ -1,5 +1,5 @@
 #' @title scramblase_assay_plot
-#' @aliases scrambalseAssayCalculations scramblaseAssayInputTemplate 
+#' @aliases scrambalseAssayCalculations scramblase_assay_input_template 
 #' scramblase_assay_plot scramblase_assay_stats scramblase_assay_traces
 #' @description Functions for the presentation and evaluaton of dithionite 
 #' scramblase assays

### 2016-05-03 inst/manuscript/manuscript.rmd
Rename "scramblaseAssayInputTemplate" to "scramblase_assay_input_template";
Rename "readScramblaseInputFile" to "read_scramblase_input_file";

@@
 
-```{r, code=formatR::usage('scramblaseAssayInputTemplate'), eval=FALSE}
+```{r, code=formatR::usage('scramblase_assay_input_template'), eval=FALSE}
 ```
@@
 In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
-x <- flippant:::readScramblaseInputFile(
+x <- flippant:::read_scramblase_input_file(
   file.path(tmpDir,"inputTable.txt"))

### 2016-05-03 R/read_scramblase_input_file.R

@@ -1,6 +1,6 @@
 #' @importFrom assertive assert_all_are_readable_files
 #' @importFrom assertive assert_is_a_non_empty_string
-readScramblaseInputFile <- function(x){
+read_scramblase_input_file <- function(x){
   assert_is_a_non_empty_string(x)
   assert_all_are_readable_files(x)
   output <- read.delim(

### 2016-05-03 R/scramblase_assay_plot.R

@@ -186,7 +186,7 @@ scramblase_assay_plot.data.frame <- function(x, ...){
 }
 #' @export
 scramblase_assay_plot.character <- function(x, ...){
-  parsedInputFile <- readScramblaseInputFile(x)
+  parsedInputFile <- read_scramblase_input_file(x)
   base_function_scramblase_assay_plot(x=parsedInputFile, ...)
 }
 base_function_scramblase_assay_plot <- function(

### 2016-05-03 R/scramblase_assay_stats.R

@@ -15,7 +15,7 @@ scramblase_assay_stats.data.frame <- function(x, ...){
 }
 #' @export
 scramblase_assay_stats.character <- function(x, ...){
-  parsedInputFile <- readScramblaseInputFile(x)
+  parsedInputFile <- read_scramblase_input_file(x)
   base_function_scramblase_assay_stats(x=parsedInputFile, ...)
 }
 base_function_scramblase_assay_stats <- function(

### 2016-05-03 R/scramblase_assay_traces.R

@@ -18,7 +18,7 @@ scramblase_assay_traces.data.frame <- function(
 }
 #' @export
 scramblase_assay_traces.character <- function(x, ...){
-  parsedInputFile <- readScramblaseInputFile(x)
+  parsedInputFile <- read_scramblase_input_file(x)
   base_function_scramblase_assay_traces(x=parsedInputFile, ...)
 }
 base_function_scramblase_assay_traces <- function(

### 2016-05-03 R/parseFelix32Output.R
Rename "parseManualOutput" to "parse_manual_output";

@@ -8,7 +8,7 @@
 #' @return See \code{\link{parseFluorimeterOutput}}.
 #' @seealso \code{\link{parseFluorimeterOutput}}, 
 #' \code{\link[flippant]{parseFelixGxOutput}},
-#' \code{\link[flippant]{parseManualOutput}}
+#' \code{\link[flippant]{parse_manual_output}}
 #' @importFrom assertive assert_all_are_non_missing_nor_empty_character
 #' @importFrom assertive assert_is_not_null
 #' @author Johannes Graumann

### 2016-05-03 R/parseFelixGxOutput.R

@@ -8,7 +8,7 @@
 #' @return See \code{\link{parseFluorimeterOutput}}.
 #' @seealso \code{\link{parseFluorimeterOutput}}, 
 #' \code{\link[flippant]{parseFelix32Output}},
-#' \code{\link[flippant]{parseManualOutput}}
+#' \code{\link[flippant]{parse_manual_output}}
 #' @importFrom assertive assert_all_are_non_missing_nor_empty_character
 #' @importFrom assertive assert_is_not_null
 #' @author Johannes Graumann

### 2016-05-03 R/parseFluorimeterOutput.R

@@ -43,7 +43,7 @@
 #' @seealso \code{scramblase_assay_input_validation},
 #' \code{\link[flippant]{parseFelixGxOutput}}, 
 #' \code{\link[flippant]{parseFelix32Output}},
-#' \code{\link[flippant]{parseManualOutput}}
+#' \code{\link[flippant]{parse_manual_output}}
 #' @author Johannes Graumann
 #' @keywords manip IO file
 #' @examples
@@ -98,7 +98,7 @@ parseFluorimeterOutput <- function(
   } else if(formatOfSpecFile == "Felix32v1.20"){
     output <- parseFelix32Output(linesInSpecFile)
   } else if(formatOfSpecFile == "Manual"){
-    output <- parseManualOutput(linesInSpecFile)
+    output <- parse_manual_output(linesInSpecFile)
   }
   # Determine timepoint of dithionite addition and adjust time axis accordingly
   #############################################################################

### 2016-05-03 R/parse_manual_output.R

@@ -1,4 +1,4 @@
-#' @title parseManualOutput
+#' @title parse_manual_output
 #' @description Parse spectra from files provided in a manually assembled 
 #' format.
 #' @details A helper function to \code{\link{parseFluorimeterOutput}}.
@@ -14,7 +14,7 @@
 #' @importFrom assertive assert_is_not_null
 #' @author Johannes Graumann
 #' @keywords manip IO file
-parseManualOutput <- function(x = NULL){
+parse_manual_output <- function(x = NULL){
   #######################
   # Check Prerequisites #
   #######################

### 2016-05-03 inst/manuscript/manuscript.rmd
- more de-camelcasing of non-exported functions; - cull "::" calls; - make "devtools" suggested; - increment version further;

@@
     check.names = FALSE) %>%
-  flippant:::calculatePpr() %>%
+  flippant:::calculate_ppr() %>%
   max(

### 2016-05-03 R/scramblase_assay_calculations.R

@@ -112,7 +112,7 @@ scramblase_assay_calculations <- function(
       ## Calcualte the relative fluorescence reduction
       z[["Relative Fluorescence Reduction"]] <- z[["Fluorescence Reduction"]] - z[["Fluorescence Reduction"]][indexOfLiposomesOnlyData]
       ## Calculate PPR
-      z[["Protein per Phospholipid (mg/mmol)"]] <- flippant:::calculatePpr(z)
+      z[["Protein per Phospholipid (mg/mmol)"]] <- calculate_ppr(z)
       ## Calculate p>=1Scramblase/Liposome
       y <- z[["Relative Fluorescence Reduction"]]
       y0 <- z[["Relative Fluorescence Reduction"]][indexOfLiposomesOnlyData]
@@ -273,6 +273,6 @@ scramblase_assay_calculations <- function(
 
 }
 
-calculatePpr <- function(x){
+calculate_ppr <- function(x){
   return(x[["Protein in Reconstitution (mg)"]]/x[["Lipid in Reconstitution (mmol)"]])
 }

### 2016-05-03 R/scramblase_assay_plot.R

@@ -196,7 +196,7 @@ base_function_scramblase_assay_plot <- function(
   generation_of_algorithm = c(2, 1),
   split_by_experiment = TRUE){
 # Check Prerequisites -----------------------------------------------------
-  validatedParams <- flippant:::scramblase_assay_input_validation(
+  validatedParams <- scramblase_assay_input_validation(
     x = x ,
     scale_to = scale_to,
     force_through_origin = force_through_origin,
@@ -209,7 +209,7 @@ base_function_scramblase_assay_plot <- function(
   split_by_experiment <- validatedParams[["split_by_experiment"]]
   
 # Processing --------------------------------------------------------------
-  processedListFromX <- flippant:::scramblase_assay_calculations(
+  processedListFromX <- scramblase_assay_calculations(
     x = x,
     scale_to = scale_to,
     force_through_origin = force_through_origin,

### 2016-05-03 R/scramblase_assay_traces.R

@@ -41,7 +41,7 @@ base_function_scramblase_assay_traces <- function(
 # Processing --------------------------------------------------------------
   # Perform assay calculations to retrive PPR
   processedX <- x
-  processedX$"Protein per Phospholipid (mg/mmol)" <- calculatePpr(x)
+  processedX$"Protein per Phospholipid (mg/mmol)" <- calculate_ppr(x)
   processedX <- processedX[c("Path","Experimental Series","Experiment","Protein per Phospholipid (mg/mmol)")]
   # Parse the fluorimeter data and whip it into shape
   rawFluorimeterOutput <- lapply(processedX$Path,parse_fluorimeter_output,adjust = adjust)

### 2016-05-03 inst/manuscript/manuscript.rmd
Make usage of latest version of multipanelfigure possible and adapt function calls;

@@
 
-figure1 <- MultiPanelFigure(
+figure1 <- multi_panel_figure(
   widths = rep(17.22/3-2*0.25, 3), 
   heights = rep(27/7-5*0.25, 7), 
-  units = "cm",
-  interPanelSpacing = 0.25)
+  unit = "cm",
+  inter_row_spacing = c(0, rep(0.5, 6)),
+  inter_column_spacing = c(0, rep(0.5, 2)))
 
@@
 x[["Path"]] <- file.path(tmpDir, x[["Path"]])
-figure1 <- AddPanel(
+figure1 <- add_panel(
   figure = figure1,
-  topPanel = 1,
-  bottomPanel = 3,
-  leftPanel = 1, 
-  rightPanel = 3, 
-  panel = scramblase_assay_traces(x, timeMaxSec = 350) + theme_bw())
-figure1 <- AddPanel(
+  top_panel = 1,
+  bottom_panel = 3,
+  left_panel = 1, 
+  right_panel = 3, 
+  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
+figure1 <- add_panel(
   figure = figure1,
-  topPanel = 4,
-  bottomPanel = 5,
-  leftPanel = 1, 
-  rightPanel = 3, 
+  top_panel = 4,
+  bottom_panel = 5,
+  left_panel = 1, 
+  right_panel = 3, 
   panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
@@
     ylab(expression(P[{phantom()>=1}])))
-figure1 <- AddPanel(
+figure1 <- add_panel(
   figure = figure1,
-  topPanel = 6,
-  bottomPanel = 7,
-  leftPanel = 1,
-  rightPanel = 2,
+  top_panel = 6,
+  bottom_panel = 7,
+  left_panel = 1,
+  right_panel = 2,
   panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  split_by_experiment = FALSE) + 

### 2016-05-03 inst/manuscript/manuscript.rmd
Finalize intra-manuscript transition away from camelCase;

@@
 time of dithionite addition. Acquisition time coverage of the plot may be tuned 
-by user-provided minimal (`time_min_sec` ) and maximal (`timeMaxSec`) time points
+by user-provided minimal (`time_min_sec` ) and maximal (`time_max_sec`) time points
 to be included (in seconds).
@@
 # Plot spectral traces (Figure 1A)
-scramblase_assay_traces("inputTable.txt", timeMaxSec = 350)
+scramblase_assay_traces("inputTable.txt", time_max_sec = 350)
 ```
@@
     x,
-    timeMaxSec = 350)
+    time_max_sec = 350)
   scramblase_assay_plot(

### 2016-05-03 inst/manuscript/manuscript.rmd
Homoginizing of title formatting;

@@
 
-#Abstract
+# Abstract
 Dithionite scramblase assays are an established means of probing the lipid 
@@
 
-#Availablility and Implementation
+# Availablility and Implementation
 *flippant* has been implemented in R [@r_core_team_r:_2015] and integrated 
@@
 
-#Input Data and Data Processing
+# Input Data and Data Processing
 To analyse raw data stemming from dithionite scramblase assays, *flippant* 
@@
 
-#Main Features
-##Template Generation for Data Input
+# Main Features
+## Template Generation for Data Input
 Supporting the user in providing the input data needed, the following function 
@@
 
-##Graphic Representation of Spectral Traces
+## Graphic Representation of Spectral Traces
 In a first, graphical data analytic step of a scramblase assay-derived data 
@@
 
-##Scramblase Assay Analysis
+## Scramblase Assay Analysis
 Plotting protein to phospholipid ratio (PPR) against the likelihood for a given
@@
 
-#Case Study
+# Case Study
 *Retinitis pigmentosa* is a degenerative disease of the retina, the majority of 
@@
 
-#Conclusion
+# Conclusion
 
@@
 
-#Funding
+# Funding
 J.G., R.J.C. and the Proteomics Core at WCMC-Q are supported by ``Biomedical 
@@
 
-#Acknowledgements
+# Acknowledgements
 
-#References
+# References

### 2016-05-03 inst/manuscript/manuscript.rmd
Name all R chunks;

@@
 
-```{r, echo = FALSE}
+```{r setting_up_r, echo = FALSE}
 library(flippant, quietly = TRUE)
@@
 
-```{r, eval = FALSE}
+```{r noeval_demonstrate_installation, eval = FALSE}
 source("http://bioconductor.org/biocLite.R")
@@
 
-```{r, code=formatR::usage('scramblase_assay_input_template'), eval=FALSE}
+```{r noeval_template_generation_call, code=formatR::usage('scramblase_assay_input_template'), eval=FALSE}
 ```
@@
 
-```{r, code = formatR::usage('scramblase_assay_traces'), eval = FALSE}
+```{r noeval_traces_call, code = formatR::usage('scramblase_assay_traces'), eval = FALSE}
 ```
@@
 
-```{r, code = formatR::usage('scramblase_assay_plot'), eval = FALSE}
+```{r noeval_plot_call, code = formatR::usage('scramblase_assay_plot'), eval = FALSE}
 ```
@@
 
-```{r, code = formatR::usage('scramblase_assay_stats'), eval = FALSE}
+```{r noeval_stats_call, code = formatR::usage('scramblase_assay_stats'), eval = FALSE}
 ```
@@
 
-```{r, eval = FALSE}
+```{r noeval_demonstrate_traces, eval = FALSE}
 # Plot spectral traces (Figure 1A)
@@
 
-```{r, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details).
+```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details).
 In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
@@
 
-```{r, eval = FALSE}
+```{r noeval_demonstrate_plot, eval = FALSE}
 # Plot PPR plot (Figure 1B)
@@
 
-```{r, echo = FALSE}
+```{r calculate_pprs, echo = FALSE}
 max_PPR <- read.delim(
@@
 
-```{r, eval = FALSE}
+```{r noeval_demonstrate_plot2, eval = FALSE}
 # Plot PPR plot (Figure 1C)
@@
 
-```{r, eval = FALSE}
+```{r noeval_demonstrate_tabular_writeout, eval = FALSE}
 # Write out results in tabular manner (Table 1)
@@
 
-```{r, echo = FALSE}
+```{r analysis_tabular_output, echo = FALSE}
 ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, split_by_experiment = FALSE)
@@
 
-```{r, echo = FALSE, cache = TRUE}
+```{r analysis_timing, echo = FALSE, cache = TRUE}
 

### 2016-05-19 inst/manuscript/manuscript.rmd
Switch to "WCM-Q";

@@
 :    \
-    Research Division, Weill Cornell Medical College in Qatar, P.O.Box 24144, Doha, State of Qatar
+    Research Division, Weill Cornell Medicine -- Qatar, P.O.Box 24144, Doha, State of Qatar
 
@@
 # Funding
-J.G., R.J.C. and the Proteomics Core at WCMC-Q are supported by ``Biomedical 
-Research Program'' funds at Weill Cornell Medical College in Qatar, a program 
+J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
+Research Program'' funds at Weill Cornell Medicine -- Qatar, a program 
 funded by Qatar Foundation. This study was made possible by NPRP grant

### 2016-05-19 inst/manuscript/manuscript.rmd
Switch to "--" (en-dash) usage;

@@
 functional validation of candidate scramblases, stoichiometry of scramblase 
-complexes and probe ATP-dependence of flippases, data analysis in its context 
+complexes and probe ATP--dependence of flippases, data analysis in its context 
 has remained a task involving many manual steps. With the extension package 
@@
 graphics, we introduce an integrated solution for the analysis and 
-publication-grade graphical presentation of dithionite scramblase assays and 
+publication--grade graphical presentation of dithionite scramblase assays and 
 demonstrate its utility in revisiting an originally manual analysis from the 
@@
 # Introduction
-Scramblases are proteins mediating the bidirectional, mass-action driven 
+Scramblases are proteins mediating the bidirectional, mass--action driven 
 equilibration of lipids between the leaflets of lipid bilayers that constitute 
@@
 [@menon_opsin_2011;@goren_constitutive_2014], TMEM16 
-[@malvezzi_ca2-dependent_2013], $\beta$ 2-adrenergic and adenosine A2A 
+[@malvezzi_ca2-dependent_2013], $\beta$ 2--adrenergic and adenosine A2A 
 receptors [both @goren_constitutive_2014]. Extrapolating from the latter findings 
 and the opsin/rhodopsin case, one may speculate that lipid scrambling may, in
-fact, be an intrinsic property of G-protein coupled receptors in general 
+fact, be an intrinsic property of G--protein coupled receptors in general 
 [@goren_constitutive_2014].
@@
 of nitrobenzoxadiazole (NBD) labeled fluorescent lipids [@chang_chemical_2004].
-Upon addition of membrane-impermeable reducing agents such as dithionite to 
-these liposomes, fluorophores in the external leaflet are quenched and fluorescence in scramblase-free liposomes accordingly quickly drops to approximately 50% of the 
+Upon addition of membrane--impermeable reducing agents such as dithionite to 
+these liposomes, fluorophores in the external leaflet are quenched and fluorescence in scramblase--free liposomes accordingly quickly drops to approximately 50% of the 
 initial value. However, for proteoliposomes reconstituted with proteins 
 conferring a scramblase activity, fluorescence disappears entirely, as
-fast scramblase-mediated equilibration between outer (exposed) and inner
+fast scramblase--mediated equilibration between outer (exposed) and inner
 (protected) leaflet of the bilayer renders all fluorescent lipids
@@
 assay has also been used to characterize the stoichiometry of scramblase 
-homo-multimers reconstituting into the proteoliposomes 
-[@ploier_perturbed_submitted] and probe the ATP-dependence of flippases, 
-molecules that under energy-consumption flip lipids against a concentration 
+homo--multimers reconstituting into the proteoliposomes 
+[@ploier_perturbed_submitted] and probe the ATP--dependence of flippases, 
+molecules that under energy--consumption flip lipids against a concentration 
 gradient between bilayer leaflets [@soupene_atp8a1_2008].
 
-Starting with the identification of baseline and post-reduction fluorescence 
-from fluorometer-generated spectra, via the calculation of the underlying 
-statistics and through publication-grade representation of the results, data 
+Starting with the identification of baseline and post--reduction fluorescence 
+from fluorometer--generated spectra, via the calculation of the underlying 
+statistics and through publication--grade representation of the results, data 
 analysis in the context of this assay has until now involved an extensive series
 of manual steps, at most supported by spreadsheet calculation facilities
-[see @menon_opsin_2011;@goren_constitutive_2014 for extensive step-wise discussion].
+[see @menon_opsin_2011;@goren_constitutive_2014 for extensive step--wise discussion].
 Based on the R free software environment for statistical computing and 
@@
 *flippant* has been implemented in R [@r_core_team_r:_2015] and integrated 
-into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install- and loadable as follows from 
+into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
 within a functional R environment:
@@
 requires for each data point information on the path to the 
-fluorometer-generated spectrum, the amount of protein used to reconstitute 
+fluorometer--generated spectrum, the amount of protein used to reconstitute 
 proteoliposomes, the assay volume before and after addition of 
@@
 versions FelixGX v4.1 and Felix32 v1.20, respectively, as well as a simple 
-generic tab-delimited spectrum representing file format with time (in seconds) 
+generic tab--delimited spectrum representing file format with time (in seconds) 
 and fluorescence intensity representing columns are currently supported. The 
@@
 time point henceforth corresponds to the time of addition. 
-Pre-dithionite-addition baseline fluorescence $F_{\text{baseline}}$ is 
+Pre--dithionite--addition baseline fluorescence $F_{\text{baseline}}$ is 
 determined for each spectrum by averaging (median) over the ten values preceding
-dithionite addition. Post-dithionite-addition minimum fluorescence 
+dithionite addition. Post--dithionite--addition minimum fluorescence 
 $F_{\text{min}}$ is analogously calculated from the last ten data points before 
 (and including) a default 400 s or the time point of measurement supplied by the
-user in the parameter spreadsheet. $F_{\text{min}}$ is volume-corrected based on
+user in the parameter spreadsheet. $F_{\text{min}}$ is volume--corrected based on
 supplied reaction volumes with and without dithionite and for each spectrum/data
@@
 $$
-A relative fluorescence reduction $y$ is calculated scaled to a (required) liposomes-only/no-protein control and the probability $P_{\geq 1}$ for a 
+A relative fluorescence reduction $y$ is calculated scaled to a (required) liposomes--only/no--protein control and the probability $P_{\geq 1}$ for a 
 liposome to contain at least one scramblase molecules is calculated using
@@
 where $y$ is the relative fluorescence reduction for the proteoliposome 
-measurement and $y_0$ for a measurement of protein-free liposomes. 
+measurement and $y_0$ for a measurement of protein--free liposomes. 
 $y_{\text{max}}$ refers to either the maximal $y$ in the experiment or is 
@@
 to the relationship of $P_{\geq 1}$ to the protein to phospholipid ratio (PPR; 
-(mg/mmol)), providing the scramblase-characterizing fit factor $\alpha$.
+(mg/mmol)), providing the scramblase--characterizing fit factor $\alpha$.
 
@@
 Supporting the user in providing the input data needed, the following function 
-generates a spreadsheet program-compatible tab-delimited plain text template, 
+generates a spreadsheet program--compatible tab--delimited plain text template, 
 including column names, commentary, expected data type and the default used when
@@
 
-The application agnostic tab-delimited format must be maintained for the 
+The application agnostic tab--delimited format must be maintained for the 
 completed table, which is subjected to extensive input checks when read by 
@@
 ## Graphic Representation of Spectral Traces
-In a first, graphical data analytic step of a scramblase assay-derived data 
-set, fluorescent spectra or traces may be plotted in publication-appropriate
-quality with acquisition time on the x- and fluorescence intensity on the y-axis
+In a first, graphical data analytic step of a scramblase assay--derived data 
+set, fluorescent spectra or traces may be plotted in publication--appropriate
+quality with acquisition time on the x-- and fluorescence intensity on the y--axis
 using
@@
 data (`x`). The `adjust` argument to the function call serves to selectively 
-inactivate *wmtsa*-provided (see above) alignment of multiple spectra to the 
+inactivate *wmtsa*--provided (see above) alignment of multiple spectra to the 
 time of dithionite addition. Acquisition time coverage of the plot may be tuned 
-by user-provided minimal (`time_min_sec` ) and maximal (`time_max_sec`) time points
+by user--provided minimal (`time_min_sec` ) and maximal (`time_max_sec`) time points
 to be included (in seconds).
@@
 [i.e. are active; @goren_constitutive_2014]. The behavior of the function may be
-adjusted to use scramblase-mediated fluorescence reduction normalized to either
+adjusted to use scramblase--mediated fluorescence reduction normalized to either
 the maximum measurement in the series (`scale_to = "data"`) or the plateau of an
@@
 *Retinitis pigmentosa* is a degenerative disease of the retina, the majority of 
-cases of which is linked to mutant forms of the G-protein coupled receptor 
+cases of which is linked to mutant forms of the G--protein coupled receptor 
 rhodopsin [@mendes_mechanisms_2005]. Motivated by the recent discovery that 
@@
 
-```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x-axis trimmed to a maximum value of 2 (see text for details).
+```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details).
 In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
@@
 Figure 1B. Using the customization facilities provided by `ggplot2` 
-[@wickham_ggplot2_2009] as a plotting system the plot's x-axis is trimmed to
+[@wickham_ggplot2_2009] as a plotting system the plot's x--axis is trimmed to
 avoid visual compression of all data by a single data point from the wild type 
@@
   row.names = FALSE,
-  caption = "**Tabular output of *flippant*-based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text-version of this output is produced by calling `scramblase_assay_stats`.")
+  caption = "**Tabular output of *flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
 ```
@@
 [@r_core_team_r:_2015], scientists can quickly analyse such data and arrive at 
-publication-grade graphics that offer extensive facilities for individual 
+publication--grade graphics that offer extensive facilities for individual 
 optimization and adaptation [@wickham_ggplot2_2009]. On a laptop system with 
@@
 
-Results from *flippant*-driven analysis track prior manual analysis well. 
+Results from *flippant*--driven analysis track prior manual analysis well. 
 Deviations observed may stem from algorithmic differences such as the fitting 
@@
 in the context of dithionite scramblase analysis and a platform for review, 
-dissemination and extension of the strategies it employs. As BSA-back 
+dissemination and extension of the strategies it employs. As BSA--back 
 extraction, a different assay for lipid translocation across liposome bilayers
@@
 funded by Qatar Foundation. This study was made possible by NPRP grant
-5-669-1-112 from the Qatar National Research Fund (a member of Qatar 
-Foundation).The statements made herein are solely the responsibility of the
+5--669--1--112 from the Qatar National Research Fund (a member of Qatar 
+Foundation). The statements made herein are solely the responsibility of the
 authors. B.P. was also supported by the Austrian Science Fund (FWF), project
-J3686-B21.
+J3686--B21.
 

### 2016-05-19 R/scramblase_assay_traces.R
Add 'adj. PPR' as label when 'ppr_scale_factor' is used;

@@ -92,8 +92,16 @@ base_function_scramblase_assay_traces <- function(
   plotOutput <- plotOutput +
     labs(
       x="Acquisition Time (s)",
-      y="Relative Fluorescence Intensity",
-      colour=expression("PPR "*bgroup("(",frac("mg","mmol"),")")))
+      y="Relative Fluorescence Intensity")
+  if(is.null(ppr_scale_factor)){
+    plotOutput <- plotOutput +
+      labs(
+        colour=expression("PPR "*bgroup("(",frac("mg","mmol"),")")))
+  } else {
+    plotOutput <- plotOutput +
+      labs(
+        colour=expression("adj. PPR "*bgroup("(",frac("mg","mmol"),")")))
+  }
   # Facetting
   hasExperiment <- any(!is.na(mergedData$Experiment))
   hasSeries <- any(!is.na(mergedData$Experimental.Series))

### 2016-05-19 inst/manuscript/manuscript.rmd
Start phasing 'ppr_scale_factor' into the manuscript;

@@
 
-Based on @menon_opsin_2011 and @goren_constitutive_2014 and largely keeping with
-nomenclature used therein, data is processed as follows. Input is format checked
-and defaults are injected for facultative parameters/columns as appropriate. 
+Based on @menon_opsin_2011, @goren_constitutive_2014 and
+@ploier_perturbed_submitted and largely keeping with nomenclature used therein,
+data is processed as follows. Input is format checked and defaults are injected
+for facultative parameters/columns as appropriate. 
 Fluorescence spectra are parsed. This includes algorithmic determination of when 
@@
 to the relationship of $P_{\geq 1}$ to the protein to phospholipid ratio (PPR; 
-(mg/mmol)), providing the scramblase--characterizing fit factor $\alpha$.
+(mg/mmol)), providing the scramblase--characterizing fit factor $\alpha$. By
+default and following @ploier_perturbed_submitted, PPR is scaled by a factor of
+0.65 to account for a fraction of the vesicle pool used that is refractory to
+scramblase reconstitution. This behavior can be modified using the 
+`ppr_scale_factor` parameter and avoided alltogether setting it to `NULL`.
 
@@
 inactivate *wmtsa*--provided (see above) alignment of multiple spectra to the 
-time of dithionite addition. Acquisition time coverage of the plot may be tuned 
-by user--provided minimal (`time_min_sec` ) and maximal (`time_max_sec`) time points
-to be included (in seconds).
+time of dithionite addition, while the `ppr_scale_factor` parameter is used to
+scale PPR (see above) and is needed here as the traces are colored by that
+measure. Acquisition time coverage of the plot may be tuned  by user--provided
+minimal (`time_min_sec` ) and maximal (`time_max_sec`) time points to be
+included (in seconds).
 
@@
 or not to require the exponential curve fitted to the data to go through the
-origin. The `split_by_experiment` argument is used to indicate whether independent
+origin. `ppr_scale_factor` allows for the modification of scaling to account for
+a pool of vesicles that is scramblase--inaccessible (see above). The
+`split_by_experiment` argument is used to indicate whether independent
 experiments are integrated into a single analysis (`split_by_experiment = FALSE`)
@@
 custom trimming of the time axis to account for divergent acquisition 
-times between experiments.
+times between experiments. PPR scaling is used with the default factor of 0.65.
 
@@
 ```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details).
-In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit."}
+In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit.
+'adj.
+PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
 x <- flippant:::read_scramblase_input_file(
@@
     xlim(0, 2) + 
-    xlab(expression("PPR"~~("mg"/"mmol"))) +
+    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
     ylab(expression(P[{phantom()>=1}])))

### 2016-05-21 R/parse_felix_32_output.R
Switch away from "assertive" to component packages that are actually used;

@@ -9,8 +9,8 @@
 #' @seealso \code{\link{parse_fluorimeter_output}}, 
 #' \code{\link[flippant]{parse_felix_gx_output}},
 #' \code{\link[flippant]{parse_manual_output}}
-#' @importFrom assertive assert_all_are_non_missing_nor_empty_character
-#' @importFrom assertive assert_is_not_null
+#' @importFrom assertive.properties assert_is_not_null
+#' @importFrom assertive.strings assert_all_are_non_missing_nor_empty_character
 #' @author Johannes Graumann
 #' @keywords manip IO file
 parse_felix_32_output <- function(x = NULL){

### 2016-05-21 R/parse_felix_gx_output.R

@@ -9,8 +9,8 @@
 #' @seealso \code{\link{parse_fluorimeter_output}}, 
 #' \code{\link[flippant]{parse_felix_32_output}},
 #' \code{\link[flippant]{parse_manual_output}}
-#' @importFrom assertive assert_all_are_non_missing_nor_empty_character
-#' @importFrom assertive assert_is_not_null
+#' @importFrom assertive.properties assert_is_not_null
+#' @importFrom assertive.strings assert_all_are_non_missing_nor_empty_character
 #' @author Johannes Graumann
 #' @keywords manip IO file
 parse_felix_gx_output <- function(x = NULL){

### 2016-05-21 R/parse_fluorimeter_output.R

@@ -48,9 +48,9 @@
 #' @keywords manip IO file
 #' @examples
 #' # stop("Function is missing examples!")
-#' @importFrom assertive assert_all_are_readable_files
-#' @importFrom assertive assert_is_a_bool
-#' @importFrom assertive assert_is_a_string
+#' @importFrom assertive.files assert_all_are_readable_files
+#' @importFrom assertive.types assert_is_a_bool
+#' @importFrom assertive.types assert_is_a_string
 #' @importFrom RcppRoll roll_mean
 #' @importFrom utils tail
 #' @importFrom wmtsa wavCWT

### 2016-05-21 R/parse_manual_output.R

@@ -10,8 +10,8 @@
 #' @seealso \code{\link{parse_fluorimeter_output}},
 #' \code{\link[flippant]{parse_felix_gx_output}}, 
 #' \code{\link[flippant]{parse_felix_32_output}}
-#' @importFrom assertive assert_all_are_non_missing_nor_empty_character
-#' @importFrom assertive assert_is_not_null
+#' @importFrom assertive.properties assert_is_not_null
+#' @importFrom assertive.strings assert_all_are_non_missing_nor_empty_character
 #' @author Johannes Graumann
 #' @keywords manip IO file
 parse_manual_output <- function(x = NULL){

### 2016-05-21 R/read_scramblase_input_file.R

@@ -1,5 +1,5 @@
-#' @importFrom assertive assert_all_are_readable_files
-#' @importFrom assertive assert_is_a_non_empty_string
+#' @importFrom assertive.files assert_all_are_readable_files
+#' @importFrom assertive.strings assert_is_a_non_empty_string
 #' @importFrom magrittr %>%
 #' @importFrom utils read.delim
 read_scramblase_input_file <- function(x){

### 2016-05-21 R/scramblase_assay_input_template.R

@@ -1,6 +1,6 @@
 #' @rdname scramblase_assay_plot
-#' @importFrom assertive assert_any_are_existing_files
-#' @importFrom assertive assert_is_a_non_empty_string
+#' @importFrom assertive.files assert_any_are_existing_files
+#' @importFrom assertive.strings assert_is_a_non_empty_string
 #' @importFrom magrittr %>%
 #' @importFrom magrittr extract
 #' @importFrom magrittr extract2

### 2016-05-21 R/scramblase_assay_input_validation.R

@@ -1,7 +1,7 @@
-#' @importFrom assertive assert_has_rows
-#' @importFrom assertive assert_is_a_bool
-#' @importFrom assertive assert_is_a_number
-#' @importFrom assertive assert_is_data.frame
+#' @importFrom assertive.properties assert_has_rows
+#' @importFrom assertive.types assert_is_a_bool
+#' @importFrom assertive.types assert_is_a_number
+#' @importFrom assertive.types assert_is_data.frame
 scramblase_assay_input_validation <- function(
   x,
   scale_to,

### 2016-05-21 R/scramblase_assay_plot.R

@@ -146,7 +146,7 @@
 #' @export
 #' @seealso \code{\link{parse_fluorimeter_output}} \code{\link{nlsLM}}
 #' @import ggplot2
-#' @importFrom assertive assert_is_a_string
+#' @importFrom assertive.types assert_is_a_string
 #' @importFrom plyr rbind.fill
 #' @examples
 #' stop("Cite Birgit's paper.")

### 2016-05-21 R/scramblase_assay_traces.R

@@ -1,6 +1,6 @@
 #' @rdname scramblase_assay_plot
 #' @import ggplot2
-#' @importFrom assertive assert_is_a_number
+#' @importFrom assertive.types assert_is_a_number
 #' @importFrom plyr rbind.fill
 #' @export
 scramblase_assay_traces <- function(

### 2016-05-21 inst/manuscript/manuscript.rmd
Minor reormatting;
en-dash to em-dash;

@@
 ---
-title: '*flippant* -- An R package for the automated analysis of dithionite scramblase
+title: '*flippant* --- An R package for the automated analysis of dithionite scramblase
   assays'
@@
 set, fluorescent spectra or traces may be plotted in publication--appropriate
-quality with acquisition time on the x-- and fluorescence intensity on the y--axis
-using
+quality with acquisition time on the x-- and fluorescence intensity on the
+y--axis using
 
@@
 comparison of specific scramblase activity between interrogated experimental
-series, which may, for example, be representative of protein preparations including 
-mutant protein forms or crude extracts with or without depletion of a candidate
-scramblase.
+series, which may, for example, be representative of protein preparations
+including mutant protein forms or crude extracts with or without depletion of a
+candidate scramblase.
 

### 2016-06-09 R/scramblase_assay_calculations.R
Reformatting;

@@ -118,10 +118,14 @@ scramblase_assay_calculations <- function(
     )
 
   # Apply volume correction factors as needed
-  volumeCorrectionFactor <- x[["Fluorescence Assay Vol. with DT (ul)"]]/x[["Fluorescence Assay Vol. w/o DT (ul)"]]
-  x[["Minimum Fluorescence, Volume Corrected"]] <- x[["Minimum Fluorescence"]] * volumeCorrectionFactor
+  volumeCorrectionFactor <- x[["Fluorescence Assay Vol. with DT (ul)"]] / 
+    x[["Fluorescence Assay Vol. w/o DT (ul)"]]
+  x[["Minimum Fluorescence, Volume Corrected"]] <- x[["Minimum Fluorescence"]] *
+    volumeCorrectionFactor
   ## Calculate activity reduction
-  x[["Fluorescence Reduction"]] <- 1 - x[["Minimum Fluorescence, Volume Corrected"]]/x[["Baseline Fluorescence"]]
+  x[["Fluorescence Reduction"]] <- 1 - 
+    x[["Minimum Fluorescence, Volume Corrected"]] / 
+    x[["Baseline Fluorescence"]]
 
 # Generate PPR v.s P(>=1 Scramblase/Liposome) -------------------------------
   # Split by Experiment

### 2016-06-09 R/scramblase_assay_stats.R
Make significant digits of return depend on algorithm used;

@@ -64,7 +64,7 @@ base_function_scramblase_assay_stats <- function(
     columns <- c("Fit Constant (a)","Experimental Series")
   }
   output <- output[which(names(output) %in% columns)]
-  output["Fit Constant (a)"] <- signif(output["Fit Constant (a)"], digits = 2)
+  output["Fit Constant (a)"] <- signif(output["Fit Constant (a)"], digits = generation_of_algorithm * 2)
   names(output)[which(names(output) == "Fit Constant (a)")] <- "Fit Constant"
 # Return ------------------------------------------------------------------
   return(output)

### 2016-06-09 R/scramblase_assay_calculations.R
Fix generalization of fit_prep;

@@ -171,7 +171,7 @@ scramblase_assay_calculations <- function(
           z[["Fluorescence Reduction"]][indexOfLiposomesOnlyData]
         ## Calculate PPR
         z[["Protein per Phospholipid (mg/mmol)"]] <- z %>%
-          calculate_ppr(ppr_scale_factor = ppr_scale_factor)
+          flippant:::calculate_ppr(ppr_scale_factor = ppr_scale_factor)
         ## Calculate p>=1Scramblase/Liposome
         y <- z %>%
           extract2("Relative Fluorescence Reduction")
@@ -179,7 +179,7 @@ scramblase_assay_calculations <- function(
           extract(indexOfLiposomesOnlyData)
         if(scale_to == "model"){
           fit_prep <- z %>%
-            fit_prep()
+            flippant:::fit_prep(y = "Relative Fluorescence Reduction")
           fitStart <- if(force_through_origin){
             list(
               a = fit_prep[["estimated_a"]],
@@ -218,7 +218,7 @@ scramblase_assay_calculations <- function(
     lapply(
       function(z){
         fit_prep <- z %>%
-          fit_prep()
+          flippant:::fit_prep(y = "Probability >= 1 Scramblase in Vesicle")
         ##> The dependence of p(≥1 flippase) on PPR was analyzed as follows.
         ##> Definitions:
         ##>   f, number of flippases used for reconstitution
@@ -310,11 +310,17 @@ calculate_ppr <- function(x, ppr_scale_factor = 0.65){
 
 
 # Helper Functions --------------------------------------------------------
-fit_prep <- function(z){
+fit_prep <- function(z, y = c("Relative Fluorescence Reduction", "Probability >= 1 Scramblase in Vesicle")){
+  y %<>%
+    match.arg(
+      choices = c(
+        "Relative Fluorescence Reduction",
+        "Probability >= 1 Scramblase in Vesicle"),
+      several.ok =  FALSE)
   fit_set <- z %>%
-    extract2(
+    extract(
       c("Protein per Phospholipid (mg/mmol)",
-        "Probability >= 1 Scramblase in Vesicle")) %>%
+        y)) %>%
     set_names(c("x", "y"))
   ### Determine a sensible start point for 'a'
   pointSixY <- fit_set %>%
@@ -330,7 +336,7 @@ fit_prep <- function(z){
         abs() %>%
         which.min())
   estimated_b <- z %>%
[…]

### 2016-06-09 inst/manuscript/manuscript.rmd
Add a remark regarding "Force_through_origin" (is laready in the package doc);
Typo;

@@
 `split_by_experiment` argument is used to indicate whether independent
-experiments are integrated into a single analysis (`split_by_experiment = FALSE`)
-or treated separately (`split_by_experiment = TRUE`; see below for example usage).
+experiments are integrated into a single analysis
+(`split_by_experiment = FALSE`) or treated separately
+(`split_by_experiment = TRUE`; see below for example usage). The
+`force_through_origin` parameter may be used to employ a fit with more degrees
+of freedom. While the non--default `force_through_origin = FALSE` allows for a
+better fit to some experimental data, its mechanistic implications are unclear.
 
@@
 ```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details).
-In (B) data is separately plotted for independent experiments, while (C) combines all dat points, aiming for reliability of fit.
+In (B) data is separately plotted for independent experiments, while (C) combines all data points, aiming for reliability of fit.
 'adj.

### 2016-06-09 inst/manuscript/manuscript.rmd
Transition to usage of algorithm 2;

@@
 ```{r setting_up_r, echo = FALSE}
+library(dplyr)
 library(flippant, quietly = TRUE)
@@
   right_panel = 3, 
-  panel = scramblase_assay_plot(x, generation_of_algorithm = 1) + 
+  panel = scramblase_assay_plot(x, generation_of_algorithm = 2) + 
     theme_bw() + 
@@
   left_panel = 1,
-  right_panel = 2,
-  panel = scramblase_assay_plot(x, generation_of_algorithm = 1,  split_by_experiment = FALSE) + 
+  right_panel = 3,
+  panel = scramblase_assay_plot(x, generation_of_algorithm = 2, split_by_experiment = FALSE) + 
     theme_bw() + 
@@
 # Plot PPR plot (Figure 1B)
-scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 1) + xlim(0, 2)
+scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 2) + xlim(0, 2)
 ```
@@
 scramblase_assay_plot("inputTable.txt",
-  generation_of_algorithm = 1,
+  generation_of_algorithm = 2,
   split_by_experiment = FALSE) + 
@@
 # Write out results in tabular manner (Table 1)
-scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 1, split_by_experiment = FALSE)
+scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 2, split_by_experiment = FALSE)
 ```
@@
 ```{r analysis_tabular_output, echo = FALSE}
-ppr_results <- scramblase_assay_stats(x, generation_of_algorithm = 1, split_by_experiment = FALSE)
-ppr_results_names <- ppr_results$`Experimental Series` %>%
+ppr_results <- scramblase_assay_stats(
+    x, generation_of_algorithm = 2, split_by_experiment = FALSE) %>%
+  mutate(`Fit Constant` = round(`Fit Constant` * 10E3, 2)) %>%
+  set_names(c("Experimental Series", "Fit Constant ($\\times 10^3$)"))
+ppr_results_names <- ppr_results %>%
+  extract2("Experimental Series") %>%
   head(n = nrow(ppr_results) - 1) %>%
@@
   paste(tail(ppr_results$`Experimental Series`, n = 1))
-ppr_results_alpha_print <- ppr_results$`Fit Constant` %>%
-  signif(2) %>%
+ppr_results_alpha_print <- ppr_results %>%
+  extract2("Fit Constant ($\\times 10^3$)") %>%
+  round(2) %>%
   head(n = nrow(ppr_results) - 1) %>%
@@
   paste("and") %>%
-  paste(tail(ppr_results$`Fit Constant`, n = 1))
+  paste(tail(ppr_results$`Fit Constant ($\\times 10^3$)`, n = 1))
 knitr::kable(
@@
 The resulting values for the fit constant $\alpha$ correspond with
-`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, very well
-to the prior manual analysis by @ploier_perturbed_submitted, where
-$\alpha \approx 0.13$ was reported for mutant and $\alpha \approx 0.26$ for wild
-type rhodopsin. Based on the manual analysis of the data we conclude in @ploier_perturbed_submitted that the mutant rhodopsins investigated are
+`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
+prior manual analysis by @ploier_perturbed_submitted (Table S2), where $\alpha
+\times 10^3 \approx 16$ was reported for mutant and $\alpha \times 10^3 \approx
+7$ for wild type rhodopsin. Based on the manual analysis of the data we conclude
+in @ploier_perturbed_submitted that the mutant rhodopsins investigated are
 reconstituted into proteoliposomes in monomeric form, contrary to the wild type,
@@
     x,
-    generation_of_algorithm = 1)
+    generation_of_algorithm = 2)
   scramblase_assay_plot(
     x,
-    generation_of_algorithm = 1,
+    generation_of_algorithm = 2,
     split_by_experiment = FALSE)
@@
     x,
-    generation_of_algorithm = 1, 
+    generation_of_algorithm = 2, 
     split_by_experiment = FALSE)

### 2016-06-09 inst/manuscript/manuscript.rmd
Start reformatting the figure;
Fix multiplication mistace;

@@
     xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
-    ylab(expression(P[{phantom()>=1}])))
+    ylab(expression(P[{phantom()>=1}])) +
+    facet_wrap(c("`Experimental Series`"))+
+    guides(colour = "none"))
 grid.draw(figure1)
@@
     x, generation_of_algorithm = 2, split_by_experiment = FALSE) %>%
-  mutate(`Fit Constant` = round(`Fit Constant` * 10E3, 2)) %>%
-  set_names(c("Experimental Series", "Fit Constant ($\\times 10^3$)"))
+  mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
+  set_names(c("Experimental Series", "Fit Constant ($\\times 10^4$)"))
 ppr_results_names <- ppr_results %>%
@@
 ppr_results_alpha_print <- ppr_results %>%
-  extract2("Fit Constant ($\\times 10^3$)") %>%
+  extract2("Fit Constant ($\\times 10^4$)") %>%
   round(2) %>%
@@
   paste("and") %>%
-  paste(tail(ppr_results$`Fit Constant ($\\times 10^3$)`, n = 1))
+  paste(tail(ppr_results$`Fit Constant ($\\times 10^4$)`, n = 1))
 knitr::kable(
@@
 prior manual analysis by @ploier_perturbed_submitted (Table S2), where $\alpha
-\times 10^3 \approx 16$ was reported for mutant and $\alpha \times 10^3 \approx
+\times 10^4 \approx 16$ was reported for mutant and $\alpha \times 10^4 \approx
 7$ for wild type rhodopsin. Based on the manual analysis of the data we conclude

### 2016-06-16 R/scramblase_assay_plot.R
Fix two missing 'r_bar', 'sigma_r_bar' references;

@@ -209,7 +209,9 @@ scramblase_assay_plot <- function(
   ppr_scale_factor = 0.65,
   force_through_origin = TRUE,
   generation_of_algorithm = c(2, 1),
-  split_by_experiment = TRUE){
+  split_by_experiment = TRUE,
+  r_bar = 88,
+  sigma_r_bar = 28){
   UseMethod("scramblase_assay_plot",x)
 }
 #' @export

### 2016-06-16 R/scramblase_assay_stats.R

@@ -7,7 +7,9 @@ scramblase_assay_stats <- function(
   ppr_scale_factor = 0.65,
   force_through_origin = TRUE,
   generation_of_algorithm = c(2, 1),
-  split_by_experiment = TRUE){
+  split_by_experiment = TRUE,
+  r_bar = 88,
+  sigma_r_bar = 28){
   UseMethod("scramblase_assay_stats",x)
 }
 #' @export

### 2016-06-16 inst/manuscript/manuscript.rmd
Make loading of 'dplyr' silent;

@@
 ```{r setting_up_r, echo = FALSE}
-library(dplyr)
+library(dplyr, quietly = TRUE)
 library(flippant, quietly = TRUE)

### 2016-06-16 inst/manuscript/manuscript.rmd
Reformat code chuncks in manuscript;

@@
 
-```{r noeval_template_generation_call, code=formatR::usage('scramblase_assay_input_template'), eval=FALSE}
+```{r noeval_template_generation_call, code=formatR::usage('scramblase_assay_input_template', width = 60), eval=FALSE}
 ```
@@
 
-```{r noeval_traces_call, code = formatR::usage('scramblase_assay_traces'), eval = FALSE}
+```{r noeval_traces_call, code = formatR::usage('scramblase_assay_traces', width = 60), eval = FALSE}
 ```
@@
 
-```{r noeval_plot_call, code = formatR::usage('scramblase_assay_plot'), eval = FALSE}
+```{r noeval_plot_call, code = formatR::usage('scramblase_assay_plot', width = 65), eval = FALSE}
 ```
@@
 
-```{r noeval_stats_call, code = formatR::usage('scramblase_assay_stats'), eval = FALSE}
+```{r noeval_stats_call, code = formatR::usage('scramblase_assay_stats', width = 65), eval = FALSE}
 ```
@@
 # Plot spectral traces (Figure 1A)
-scramblase_assay_traces("inputTable.txt", time_max_sec = 350)
+scramblase_assay_traces(
+  "inputTable.txt",
+  time_max_sec = 350)
 ```
@@
 PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
-x <- flippant:::read_scramblase_input_file(
-  file.path(tmpDir,"inputTable.txt"))
+x <- tmpDir %>%
+  file.path("inputTable.txt") %>%
+  flippant:::read_scramblase_input_file()
 x[["Path"]] <- file.path(tmpDir, x[["Path"]])
@@
 # Plot PPR plot (Figure 1B)
-scramblase_assay_plot("inputTable.txt", generation_of_algorithm = 2) + xlim(0, 2)
+scramblase_assay_plot(
+  "inputTable.txt",
+  generation_of_algorithm = 2) +
+xlim(0, 2)
 ```
@@
 # Plot PPR plot (Figure 1C)
-scramblase_assay_plot("inputTable.txt",
+scramblase_assay_plot(
+  "inputTable.txt",
   generation_of_algorithm = 2,
@@
 # Write out results in tabular manner (Table 1)
-scramblase_assay_stats("inputTable.txt", generation_of_algorithm = 2, split_by_experiment = FALSE)
+scramblase_assay_stats(
+  "inputTable.txt",
+  generation_of_algorithm = 2,
+  split_by_experiment = FALSE)
 ```

### 2016-06-16 inst/manuscript/manuscript.rmd
Change Author order;

@@
   assays'
-author: Johannes Graumann ^†,^*, Birgit Ploier ^‡^, Richard J. Cotton ^†^,
-  Michael A. Goren ^‡^ and Anant K. Menon ^‡^
+author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^,
+  Anant K. Menon ^‡^ and Johannes Graumann ^†,^*
 date: '`r format(Sys.Date(), "%B %d,%Y")`'

### 2016-06-16 inst/manuscript/manuscript.rmd
reformat "R" and package names;

@@
 ---
-title: '*flippant* --- An R package for the automated analysis of dithionite scramblase
+title: '`flippant` --- An `R` package for the automated analysis of dithionite scramblase
   assays'
@@
       c(
-        "*",
-        paste0(head(x, n = length(x) - 1), collapse = "*, *"),
-        "* and *",
+        "`",
+        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
+        "` and `",
         tail(x, n = 1),
-        "*"),
+        "`"),
       collapse = "")} )
@@
 has remained a task involving many manual steps. With the extension package 
-*flippant* to R, a free software environment for statistical computing and 
+`flippant` to `R`, a free software environment for statistical computing and 
 graphics, we introduce an integrated solution for the analysis and 
@@
 [see @menon_opsin_2011;@goren_constitutive_2014 for extensive step--wise discussion].
-Based on the R free software environment for statistical computing and 
+Based on the `R` free software environment for statistical computing and 
 graphics [@r_core_team_r:_2015] and prominently drawing on the power and 
 elegance of the `ggplot2` plotting system [@wickham_ggplot2_2009], we here 
-provide *flippant*, a package that comprehensively, fast and reproducibly covers
+provide `flippant`, a package that comprehensively, fast and reproducibly covers
 all data analysis and graphing needs from raw fluorescence spectra produced by 
@@
 # Availablility and Implementation
-*flippant* has been implemented in R [@r_core_team_r:_2015] and integrated 
+`flippant` has been implemented in `R` [@r_core_team_r:_2015] and integrated 
 into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
-within a functional R environment:
+within a functional `R` environment:
 
@@
 
-The package depends on the following packaged extensions to R base 
+The package depends on the following packaged extensions to `R` base 
 functionality, which are automatically satisfied on installation: 
@@
 # Input Data and Data Processing
-To analyse raw data stemming from dithionite scramblase assays, *flippant* 
+To analyse raw data stemming from dithionite scramblase assays, `flippant` 
 requires for each data point information on the path to the 
@@
 
-Spectral input data is read by *flippant* using the file paths provided in the
+Spectral input data is read by `flippant` using the file paths provided in the
 spreadsheet. Raw spectra produced by QuantaMaster fluorometer instruments 
@@
 dithionite was added to the sample using peak detection by continuous wavelet
-transformation as implemented in the *wmtsa* R package [@percival_wavelet_2000;@constantine_wmtsa:_2013]. 
+transformation as implemented in the `wmtsa` package [@percival_wavelet_2000;@constantine_wmtsa:_2013]. 
 Acquisition time is aligned for all spectra in the data set such that the zero 
@@
 completed table, which is subjected to extensive input checks when read by 
-*flippant*.
+`flippant`.
 
@@
 data (`x`). The `adjust` argument to the function call serves to selectively 
-inactivate *wmtsa*--provided (see above) alignment of multiple spectra to the 
+inactivate `wmtsa`--provided (see above) alignment of multiple spectra to the 
 time of dithionite addition, while the `ppr_scale_factor` parameter is used to
@@
 
-*flippant*s capabilities are demonstrated here by reanalyzing data underlying 
 Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
-step plots the corresponding spectral traces (Figure 1A). Note that algorithmic
+`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
+Figure 4C--F in @ploier_perturbed_submitted. The following work flow in a first 
 alignment to the time of dithionite addition is employed (default) as well as 
@@
 
-```{r figure1_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "***flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** (A) represents spectral traces as produced by a call to the function `scramblase_assay_traces`, while (B) and (C) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details).
-In (B) data is separately plotted for independent experiments, while (C) combines all data points, aiming for reliability of fit.
-'adj.
-PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
+```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying the data in Figure 4C--F from @ploier_perturbed_submitted.** See text for command and details."}
+# Plot spectral traces (Figure 1)
 x <- tmpDir %>%
@@
   row.names = FALSE,
-  caption = "**Tabular output of *flippant*--based reanalysis of data in Figure 4C/D from @ploier_perturbed_submitted.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
+  caption = "**Tabular output of `flippant`--based reanalysis of data in Figure 4C--F from @ploier_perturbed_submitted.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
 ```
@@
 which is reconstituting as a homodimer. 
-*flippant* analysis of the data shows identical trends and close matches of the
+`flippant` analysis of the data shows identical trends and close matches of the
 results, supporting identical conclusions.
@@
 
-With *flippant* we present an integrated solution for data analysis in the 
+With `flippant` we present an integrated solution for data analysis in the 
 context of dithionite scramblase assays. Requiring only basic familiarity with 
@@
 `r parallel::detectCores()` cores and 8 GB RAM (no SSD), running `Linux` and 
-R version `r paste(R.version[c("major","minor")], collapse = ".")`, the
+`R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
 statements generating equivalents to the plots and calculations presented here
@@
 
-Results from *flippant*--driven analysis track prior manual analysis well. 
+Results from `flippant`--driven analysis track prior manual analysis well. 
 Deviations observed may stem from algorithmic differences such as the fitting 
-routine used (*flippant* uses the the Marquardt nonlinear least squares
+routine used (`flippant` uses the the Marquardt nonlinear least squares
 algorithm as implemented by @elzhov_minpack.lm:_2015) and 
@@
 
-The choice of R for the implementation is not only motivated by the extensive
+The choice of `R` for the implementation is not only motivated by the extensive
 tool kit for statistic methodology and exquisite plotting environment it 
@@
 
-*flippant*, in conclusion, provides means for quick, reproducible data analysis
+`flippant`, in conclusion, provides means for quick, reproducible data analysis
 in the context of dithionite scramblase analysis and a platform for review, 
@@
 [@kubelt_transbilayer_2002;@vehring_flip-flop_2007], can utilize an essentially 
-identical data analysis workflow, *flippant* is expected to facilitate analysis
+identical data analysis workflow, `flippant` is expected to facilitate analysis
 of such experiments as well.

### 2016-06-16 inst/manuscript/manuscript.rmd
Make loading of "dplyr" silent;

@@
 
-```{r setting_up_r, echo = FALSE}
+```{r setting_up_r, echo = FALSE, message = FALSE}
 library(dplyr, quietly = TRUE)

### 2016-06-16 inst/manuscript/manuscript.rmd
Split figure into 2: one for traces, one for PPR plots;

@@
 
-figure1 <- multi_panel_figure(
-  widths = rep(17.22/3-2*0.25, 3), 
-  heights = rep(27/7-5*0.25, 7), 
+divisor <- 20
+figure2 <- multi_panel_figure(
+  widths = rep(17.22), 
+  heights = c(
+    18/divisor * 7 - 0.25,
+    18/divisor * 13 - 0.25), 
   unit = "cm",
-  inter_row_spacing = c(0, rep(0.5, 6)),
-  inter_column_spacing = c(0, rep(0.5, 2)))
+  inter_row_spacing = 0.5,
+  inter_column_spacing = 0.5)
 
@@
 Figure 4C--F in @ploier_perturbed_submitted. The following work flow in a first 
+step plots the corresponding spectral traces (Figure 1). Note that algorithmic
 alignment to the time of dithionite addition is employed (default) as well as 
@@
 ```{r noeval_demonstrate_traces, eval = FALSE}
-# Plot spectral traces (Figure 1A)
+# Plot spectral traces (Figure 1)
 scramblase_assay_traces(
@@
 x[["Path"]] <- file.path(tmpDir, x[["Path"]])
-figure1 <- add_panel(
-  figure = figure1,
+scramblase_assay_traces(
+  x,
+  time_max_sec = 350)
+```
+
+Scramblase activity analysis as described above is performed on the data set with
+the following calls.
+
+```{r noeval_demonstrate_plot, eval = FALSE}
+# Plot PPR plot (Figure 2A)
+scramblase_assay_plot(
+  "inputTable.txt") +
+xlim(0, 2)
+```
+
+```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of data in Figure 4C--F from @ploier_perturbed_submitted.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details).
+In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit.
+'adj.
+PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
+figure2 %<>% add_panel(
   top_panel = 1,
-  bottom_panel = 3,
-  left_panel = 1, 
-  right_panel = 3, 
-  panel = scramblase_assay_traces(x, time_max_sec = 350) + theme_bw())
-figure1 <- add_panel(
-  figure = figure1,
-  top_panel = 4,
-  bottom_panel = 5,
-  left_panel = 1, 
-  right_panel = 3, 
-  panel = scramblase_assay_plot(x, generation_of_algorithm = 2) + 
+  panel = scramblase_assay_plot(x) + 
     theme_bw() + 
@@
     ylab(expression(P[{phantom()>=1}])))
-figure1 <- add_panel(
-  figure = figure1,
-  top_panel = 6,
-  bottom_panel = 7,
-  left_panel = 1,
-  right_panel = 3,
-  panel = scramblase_assay_plot(x, generation_of_algorithm = 2, split_by_experiment = FALSE) + 
+figure2 %<>% add_panel(
+  top_panel = 2,
+  panel = scramblase_assay_plot(x, split_by_experiment = FALSE) + 
     theme_bw() + 
@@
     guides(colour = "none"))
-grid.draw(figure1)
-```
-
-Scramblase activity analysis as described above is performed on the data set with
-the following calls.
-
-```{r noeval_demonstrate_plot, eval = FALSE}
-# Plot PPR plot (Figure 1B)
-scramblase_assay_plot(
-  "inputTable.txt",
-  generation_of_algorithm = 2) +
-xlim(0, 2)
+figure2
 ```
@@
 The call results in the protein to phospholipid ratio (PPR) plot shown in
-Figure 1B. Using the customization facilities provided by `ggplot2` 
+Figure 2A. Using the customization facilities provided by `ggplot2` 
 [@wickham_ggplot2_2009] as a plotting system the plot's x--axis is trimmed to
@@
 
-Figure 1B emphasizes reproducibility between independent experiments
+Figure 2A emphasizes reproducibility between independent experiments
 ("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
@@
 following more closely the analysis in Figure 4C/D by
+following more closely the analysis in Figure 4C--F by
 @ploier_perturbed_submitted, a single fit may be performed for the combined data
-from all experiments as follows, resulting in Figure 1C:
+from all experiments as follows, resulting in Figure 2B:
 
 ```{r noeval_demonstrate_plot2, eval = FALSE}
-# Plot PPR plot (Figure 1C)
+# Plot PPR plot (Figure 2B)
 scramblase_assay_plot(
   "inputTable.txt",
-  generation_of_algorithm = 2,
   split_by_experiment = FALSE) + 
@@
 difficult to visually evaluate and easy access to the numeric values desirable.
-Recapitulation of the calculations underlying PPR plot generation for Figure 1C
+Recapitulation of the calculations underlying PPR plot generation for Figure 2B
 by `scramblase_assay_plot` in a call to `scramblase_assay_stats`, this is achieved

### 2016-06-16 inst/manuscript/manuscript.rmd
Various edits/corrections;

@@
 functional validation of candidate scramblases, stoichiometry of scramblase 
-complexes and probe ATP--dependence of flippases, data analysis in its context 
+complexes as well as ATP--dependence of flippases, data analysis in its context 
 has remained a task involving many manual steps. With the extension package 
@@
 [@menon_opsin_2011;@goren_constitutive_2014], TMEM16 
-[@malvezzi_ca2-dependent_2013], $\beta$ 2--adrenergic and adenosine A2A 
+[@malvezzi_ca2-dependent_2013], $\beta~2$--adrenergic and adenosine A2A 
 receptors [both @goren_constitutive_2014]. Extrapolating from the latter findings 
@@
 of manual steps, at most supported by spreadsheet calculation facilities
-[see @menon_opsin_2011;@goren_constitutive_2014 for extensive step--wise discussion].
+[see @menon_opsin_2011;@goren_constitutive_2014;@ploier_perturbed_submitted for
+extensive step--wise discussion].
 Based on the `R` free software environment for statistical computing and 
@@
 biocLite(pkgs = "flippant")
-library(flippant)
+library("flippant")
 ```
@@
 
-Based on @menon_opsin_2011, @goren_constitutive_2014 and
+Based on @menon_opsin_2011, @goren_constitutive_2014 as well as
 @ploier_perturbed_submitted and largely keeping with nomenclature used therein,
@@
 
-Figure 4C/D in @ploier_perturbed_submitted. The following work flow in a first 
 `flippant`s capabilities are demonstrated here by reanalyzing data underlying 
@@
 avoid visual compression of all data by a single data point from the wild type 
-rhodopsin series in experiment 1, where $\text{PPR}=`r max_PPR`$. Dashed lines
-are added automatically as graphical representations of the fit constant 
-$\alpha$.
+rhodopsin series in experiment 1, where $\text{PPR}=`r max_PPR`$.
 

### 2016-06-16 inst/manuscript/manuscript.rmd
Proper description of current parameter set;

@@
 allows for the complete generation of the PPR plot in publication quality from
-the user assembled spreadsheet of input data (`x`), including automatically
-added graphical representations the PPR value equal to the fit constant
-$\alpha$ ($P_{\geq 1} = 1 - e^{-1}$), which implies all liposomes on average
-carrying one scramblase and 63% have one or more 
-[i.e. are active; @goren_constitutive_2014]. The behavior of the function may be
-adjusted to use scramblase--mediated fluorescence reduction normalized to either
-the maximum measurement in the series (`scale_to = "data"`) or the plateau of an
-exponential fit to it (`scale_to = "model"`; for reasoning see above) and whether
-or not to require the exponential curve fitted to the data to go through the
-origin. `ppr_scale_factor` allows for the modification of scaling to account for
-a pool of vesicles that is scramblase--inaccessible (see above). The
+the user assembled spreadsheet of input data (`x`). The behavior of the function
+may be adjusted to use scramblase--mediated fluorescence reduction normalized to
+either the maximum measurement in the series (`scale_to = "data"`) or the
+plateau of an exponential fit to it (`scale_to = "model"`; default; for
+reasoning see above). `ppr_scale_factor` allows for the modification of scaling
+to account for a pool of vesicles that is scramblase--inaccessible (see above).
+The formula to which the data is fitted has evolved over time and `flippant`
+supports both the original (@menon_opsin_2011; @goren_constitutive_2014; `generation_of_algorithm = 1`), as well as the more recent iteration (@ploier_perturbed_submitted; default; `generation_of_algorithm = 2`), which
+takes into account the size distribution of the liposome polulation used and
+thus also requires parameters for liposome radius and its standard deviation 
+(`r_bar` and `sigma_r_bar`, respectively; in nm, both). The
 `split_by_experiment` argument is used to indicate whether independent

### 2016-06-16 inst/manuscript/manuscript.rmd
Proper reflection od "generation_of_algorithm = 2" as the default;

@@
 reproducibility analysis in favor of a potentially more reliable result and
-following more closely the analysis in Figure 4C/D by
 following more closely the analysis in Figure 4C--F by
@@
   "inputTable.txt",
-  generation_of_algorithm = 2,
   split_by_experiment = FALSE)
@@
 ppr_results <- scramblase_assay_stats(
-    x, generation_of_algorithm = 2, split_by_experiment = FALSE) %>%
+    x, split_by_experiment = FALSE) %>%
   mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
@@
   scramblase_assay_plot(
-    x,
-    generation_of_algorithm = 2)
+    x)
   scramblase_assay_plot(
     x,
-    generation_of_algorithm = 2,
     split_by_experiment = FALSE)
@@
     x,
-    generation_of_algorithm = 2, 
     split_by_experiment = FALSE)

### 2016-07-14 inst/manuscript/manuscript.rmd
Update to current dev environment; Attempt to entirely migrate to explicit function evocation in code ("x::y") - mainly for debugging without explicit import;

@@
 ```{r setting_up_r, echo = FALSE, message = FALSE}
-library(dplyr, quietly = TRUE)
-library(flippant, quietly = TRUE)
-library(grid, quietly = TRUE)
 library(magrittr, quietly = TRUE)
-library(microbenchmark, quietly = TRUE)
-library(multipanelfigure, quietly = TRUE)
-library(stringi, quietly = TRUE)
 flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
   unlist(use.names = FALSE) %>%
-  stri_split(regex = ",", omit_empty = TRUE) %>%
+  stringi::stri_split(regex = ",", omit_empty = TRUE) %>%
   unlist(use.names = FALSE) %>%
-  stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
-  stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
+  stringi::stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
+  stringi::stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
   tail(n=length(.) - 1) %>%
@@
 divisor <- 20
-figure2 <- multi_panel_figure(
+figure2 <- multipanelfigure::multi_panel_figure(
   widths = rep(17.22), 
@@
 x[["Path"]] <- file.path(tmpDir, x[["Path"]])
-scramblase_assay_traces(
+flippant::scramblase_assay_traces(
   x,
@@
   top_panel = 1,
-  panel = scramblase_assay_plot(x) + 
-    theme_bw() + 
-    xlim(0, 2) + 
-    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
-    ylab(expression(P[{phantom()>=1}])))
-figure2 %<>% add_panel(
+  panel = flippant::scramblase_assay_plot(x) + 
+    ggplot2::theme_bw() + 
+    ggplot2::xlim(0, 3) + 
+    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
+    ggplot2::ylab(expression(P[{phantom()>=1}])))
+figure2 %<>% multipanelfigure::add_panel(
   top_panel = 2,
-  panel = scramblase_assay_plot(x, split_by_experiment = FALSE) + 
-    theme_bw() + 
-    xlim(0, 2) + 
-    xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
-    ylab(expression(P[{phantom()>=1}])) +
-    facet_wrap(c("`Experimental Series`"))+
-    guides(colour = "none"))
+  panel = flippant::scramblase_assay_plot(x, split_by_experiment = FALSE) + 
+    ggplot2::theme_bw() + 
+    ggplot2::xlim(0, 3) + 
+    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
+    ggplot2::ylab(expression(P[{phantom()>=1}])) +
+    ggplot2::facet_wrap(c("`Experimental Series`"))+
+    ggplot2::guides(colour = "none"))
 figure2
@@
 ```{r analysis_tabular_output, echo = FALSE}
-ppr_results <- scramblase_assay_stats(
+ppr_results <- flippant::scramblase_assay_stats(
     x, split_by_experiment = FALSE) %>%
-  mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
-  set_names(c("Experimental Series", "Fit Constant ($\\times 10^4$)"))
+  dplyr::mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
+  magrittr::set_names(c("Experimental Series", "Fit Constant ($\\times 10^4$)"))
 ppr_results_names <- ppr_results %>%
-  extract2("Experimental Series") %>%
+  magrittr::extract2("Experimental Series") %>%
   head(n = nrow(ppr_results) - 1) %>%
@@
 ppr_results_alpha_print <- ppr_results %>%
-  extract2("Fit Constant ($\\times 10^4$)") %>%
+  magrittr::extract2("Fit Constant ($\\times 10^4$)") %>%
   round(2) %>%
@@
 analysis_timing_function <- function(){
-  scramblase_assay_traces(
+  flippant::scramblase_assay_traces(
     x,
     time_max_sec = 350)
-  scramblase_assay_plot(
+  flippant::scramblase_assay_plot(
     x)
-  scramblase_assay_plot(
+  flippant::scramblase_assay_plot(
     x,
     split_by_experiment = FALSE)
-  scramblase_assay_stats(
+  flippant::scramblase_assay_stats(
     x,
@@
 
-analysis_timing <- microbenchmark(
+analysis_timing <- microbenchmark::microbenchmark(
   analysis_timing_function(),

### 2016-07-14 R/parse_felix_32_output.R

@@ -18,8 +18,8 @@ parse_felix_32_output <- function(x = NULL){
 
 # Check Prerequisites -----------------------------------------------------
   x %>%
-    assert_is_not_null() %>%
-    assert_all_are_non_missing_nor_empty_character()
+    assertive.properties::assert_is_not_null() %>%
+    assertive.strings::assert_all_are_non_missing_nor_empty_character()
 
 # Processing --------------------------------------------------------------
   # Extract data

### 2016-07-14 R/parse_felix_gx_output.R

@@ -17,8 +17,8 @@ parse_felix_gx_output <- function(x = NULL){
   #######################
   # Check Prerequisites #
   #######################
-  assert_is_not_null(x)
-  assert_all_are_non_missing_nor_empty_character(x)
+  assertive.properties::assert_is_not_null(x)
+  assertive.strings::assert_all_are_non_missing_nor_empty_character(x)
   ##############
   # Processing #
   ##############

### 2016-07-14 R/parse_fluorimeter_output.R

@@ -63,9 +63,9 @@ parse_fluorimeter_output <- function(
   #######################
   # Check Prerequisites #
   #######################
-  assert_is_a_string(spec_file)
-  assert_all_are_readable_files(spec_file)
-  assert_is_a_bool(adjust)
+  assertive.types::assert_is_a_string(spec_file)
+  assertive.files::assert_all_are_readable_files(spec_file)
+  assertive.types::assert_is_a_bool(adjust)
   ##############
   # Processing #
   ##############
@@ -110,9 +110,9 @@ parse_fluorimeter_output <- function(
     smoothedTmpData <- RcppRoll::roll_mean(output$Data$Fluorescence.Intensity, n)
     # Wavelet-based peak detection
     gradient <- -diff(smoothedTmpData)
-    cwt <- wavCWT(gradient)
-    tree <- wavCWTTree(cwt)
-    peaks <- wavCWTPeaks(tree)
+    cwt <- wmtsa::wavCWT(gradient)
+    tree <- wmtsa::wavCWTTree(cwt)
+    peaks <- wmtsa::wavCWTPeaks(tree)
     # Functionality appears to have memory mapping issues ...
     gc()
     # Safeguard against artifact peaks (based on incomplete understanding of wmtsa)

### 2016-07-14 R/parse_manual_output.R

@@ -18,8 +18,8 @@ parse_manual_output <- function(x = NULL){
   #######################
   # Check Prerequisites #
   #######################
-  assert_is_not_null(x)
-  assert_all_are_non_missing_nor_empty_character(x)
+  assertive.properties::assert_is_not_null(x)
+  assertive.strings::assert_all_are_non_missing_nor_empty_character(x)
   ##############
   # Processing #
   ##############

### 2016-07-14 R/read_scramblase_input_file.R

@@ -4,8 +4,8 @@
 #' @importFrom utils read.delim
 read_scramblase_input_file <- function(x){
   x %>%
-    assert_is_a_non_empty_string() %>%
-    assert_all_are_readable_files() %>%
+    assertive.strings::assert_is_a_non_empty_string() %>%
+    assertive.files::assert_all_are_readable_files() %>%
     read.delim(
       header=TRUE,
       sep="\t",

### 2016-07-14 R/scramblase_assay_calculations.R

@@ -48,7 +48,7 @@ scramblase_assay_calculations <- function(
   
 # Parsing spectra ---------------------------------------------------------
   spectralData <- x %>%
-    extract2("Path") %>%
+    magrittr::extract2("Path") %>%
     lapply(parse_fluorimeter_output)
   
 # Read out data -----------------------------------------------------------
@@ -58,23 +58,23 @@ scramblase_assay_calculations <- function(
     sapply(
       function(y){
         y %>%
-          extract2("Min.Acquisition.Time.in.sec") %>%
+          magrittr::extract2("Min.Acquisition.Time.in.sec") %>%
           return()
       }
     ) %>%
-    assert_all_are_less_than(0)
+    assertive.numbers::assert_all_are_less_than(0)
   
   spectralData %>%
     sapply(
       function(y){
         y %>%
-          extract2("Max.Acquisition.Time.in.sec") %>%
+          magrittr::extract2("Max.Acquisition.Time.in.sec") %>%
           return()
       }
     ) %>%
-    assert_all_are_greater_than_or_equal_to(x[["Timepoint of Measurement (s)"]])
+    assertive.numbers::assert_all_are_greater_than_or_equal_to(x[["Timepoint of Measurement (s)"]])
   maxAcquisitionTime <- x %>%
-      extract2("Timepoint of Measurement (s)") %>%
+      magrittr::extract2("Timepoint of Measurement (s)") %>%
       max(na.rm = TRUE)
   
   # Average over 10 values before dithionite addition for activity baseline
@@ -82,15 +82,15 @@ scramblase_assay_calculations <- function(
     vapply(
       function(z){
         indexesForAveraging <- z %>%
-          extract2("Data") %>%
-          extract2("Time.in.sec") %>%
-          is_less_than(0) %>%
+          magrittr::extract2("Data") %>%
+          magrittr::extract2("Time.in.sec") %>%
+          magrittr::is_less_than(0) %>%
           which() %>%
           tail(n = 10)
         z %>%
-          extract2("Data") %>%
-          extract2("Fluorescence.Intensity") %>%
-          extract(indexesForAveraging) %>%
+          magrittr::extract2("Data") %>%
+          magrittr::extract2("Fluorescence.Intensity") %>%
+          magrittr::extract(indexesForAveraging) %>%
           median(na.rm = TRUE) %>%
           return()
       },
[…]

### 2016-07-14 R/scramblase_assay_input_template.R

@@ -12,8 +12,8 @@
 scramblase_assay_input_template <- function(path="scramblase_assay_input_template.txt"){
 # Check input -------------------------------------------------------------
   path %>%
-    assert_is_a_non_empty_string() %>%
-    assert_any_are_existing_files()
+    assertive.strings::assert_is_a_non_empty_string() %>%
+    assertive.files::assert_any_are_existing_files()
 
 # Generate template data.frame --------------------------------------------
   # Create data structure in list form
@@ -58,18 +58,18 @@ scramblase_assay_input_template <- function(path="scramblase_assay_input_templat
       function(x){
         if(x == "columnName"){
           dataStructure %>%
-            extract2(x) %>%
+            magrittr::extract2(x) %>%
             return()
         } else {
           dataStructure %>%
-            extract2(x) %>%
-            inset2(1,paste("#", .[1])) %>%
+            magrittr::extract2(x) %>%
+            magrittr::inset2(1,paste("#", .[1])) %>%
             return()
         }
       })
   # Assemble the data.frame
   commentedDataStructure %>%
-    extract(2:length(.)) %>%
+    magrittr::extract(2:length(.)) %>%
     lapply(
       function(x){
         x %>%
@@ -78,8 +78,8 @@ scramblase_assay_input_template <- function(path="scramblase_assay_input_templat
           return()
       }
     ) %>%
-    rbind.fill() %>%
-    set_names(dataStructure %>% extract2(1)) %>%
+    plyr::rbind.fill() %>%
+    set_names(dataStructure %>% magrittr::extract2(1)) %>%
   # Write the table out
     write.table(
       file=path,

### 2016-07-14 R/scramblase_assay_input_validation.R

@@ -16,11 +16,11 @@ scramblase_assay_input_validation <- function(
   sigma_r_bar,
   verbose=TRUE){
   # Check verbose
-  assert_is_a_bool(verbose)
+  assertive.types::assert_is_a_bool(verbose)
   # Check x
   ## General DF characteristics
-  assert_is_data.frame(x)
-  assert_has_rows(x)
+  assertive.types::assert_is_data.frame(x)
+  assertive.properties::assert_has_rows(x)
   if(any(is.na(x))){
     stop("'x' cannot contain 'NA'.")
   }
@@ -132,7 +132,7 @@ scramblase_assay_input_validation <- function(
   # Check ppr_scale_factor
   if(!is.null(ppr_scale_factor)){
     ppr_scale_factor %>%
-      assert_is_a_number()
+      assertive.types::assert_is_a_number()
     if(verbose){
       message("PPR will be scaled by a factor of ", ppr_scale_factor, ".")
     }
@@ -157,18 +157,18 @@ scramblase_assay_input_validation <- function(
   }
   # Check force_through_origin
   force_through_origin %>%
-    assert_is_a_bool()
+    assertive.types::assert_is_a_bool()
   # Check split_by_experiment
   split_by_experiment %>%
-    assert_is_a_bool()
+    assertive.types::assert_is_a_bool()
   # check r_bar
   r_bar %>%
-    assert_is_a_number() %>%
-    assert_all_are_greater_than(0)
+    assertive.types::assert_is_a_number() %>%
+    assertive.numbers::assert_all_are_greater_than(0)
   # check sigmar_bar
   sigma_r_bar %>%
-    assert_is_a_number() %>%
-    assert_all_are_greater_than(0)
+    assertive.types::assert_is_a_number() %>%
+    assertive.numbers::assert_all_are_greater_than(0)
   # Return
   list(
     x = x,

### 2016-07-14 R/scramblase_assay_plot.R

@@ -177,7 +177,6 @@
 #' @export
 #' @seealso \code{\link{parse_fluorimeter_output}} \code{\link{nlsLM}}
 #' @import ggplot2
-#' @importFrom assertive.types assert_is_a_string
 #' @importFrom plyr rbind.fill
 #' @examples
 #' stop("Cite Birgit's paper.")

### 2016-07-14 R/scramblase_assay_traces.R

@@ -40,8 +40,8 @@ base_function_scramblase_assay_traces <- function(
     sigma_r_bar = 28,
     verbose = FALSE)
   x <- validatedParams[["x"]]
-  assert_is_a_number(time_min_sec)
-  assert_is_a_number(time_max_sec)
+  assertive.types::assert_is_a_number(time_min_sec)
+  assertive.types::assert_is_a_number(time_max_sec)
 
 # Processing --------------------------------------------------------------
   # Perform assay calculations to retrive PPR

### 2016-07-16 inst/manuscript/manuscript.rmd
Integrate new data from Birgit Ploier;

@@
 
-`flippant`s capabilities are demonstrated here by reanalyzing data underlying 
-Figure 4C--F in @ploier_perturbed_submitted. The following work flow in a first 
-step plots the corresponding spectral traces (Figure 1). Note that algorithmic
-alignment to the time of dithionite addition is employed (default) as well as 
-custom trimming of the time axis to account for divergent acquisition 
-times between experiments. PPR scaling is used with the default factor of 0.65.
+`flippant`s capabilities are demonstrated here by reanalyzing a subset of the
+data underlying  Figure 4C--F in @ploier_dimerization_2016. The following work
+flow in a first  step plots the corresponding spectral traces (Figure 1). Note
+that algorithmic alignment to the time of dithionite addition is employed
+(default) as well as  custom trimming of the time axis to account for divergent
+acquisition  times between experiments. PPR scaling is used with the default
+factor of 0.65.
 
@@
   "inputTable.txt") +
-xlim(0, 2)
+xlim(0, 3)
 ```
@@
   split_by_experiment = FALSE) + 
-xlim(0, 2)
+xlim(0, 3)
 ```

### 2016-07-16 inst/manuscript/manuscript.rmd
Update citations;

@@
 homo--multimers reconstituting into the proteoliposomes 
-[@ploier_perturbed_submitted] and probe the ATP--dependence of flippases, 
+[@ploier_dimerization_2016] and probe the ATP--dependence of flippases, 
 molecules that under energy--consumption flip lipids against a concentration 
@@
 of manual steps, at most supported by spreadsheet calculation facilities
-[see @menon_opsin_2011;@goren_constitutive_2014;@ploier_perturbed_submitted for
+[see @menon_opsin_2011;@goren_constitutive_2014;@ploier_dimerization_2016 for
 extensive step--wise discussion].
 Based on the `R` free software environment for statistical computing and 
-graphics [@r_core_team_r:_2015] and prominently drawing on the power and 
+graphics [@r_core_team_r:_2016] and prominently drawing on the power and 
 elegance of the `ggplot2` plotting system [@wickham_ggplot2_2009], we here 
@@
 # Availablility and Implementation
-`flippant` has been implemented in `R` [@r_core_team_r:_2015] and integrated 
+`flippant` has been implemented in `R` [@r_core_team_r:_2016] and integrated 
 into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
@@
 Based on @menon_opsin_2011, @goren_constitutive_2014 as well as
-@ploier_perturbed_submitted and largely keeping with nomenclature used therein,
+@ploier_dimerization_2016 and largely keeping with nomenclature used therein,
 data is processed as follows. Input is format checked and defaults are injected
@@
 (mg/mmol)), providing the scramblase--characterizing fit factor $\alpha$. By
-default and following @ploier_perturbed_submitted, PPR is scaled by a factor of
+default and following @ploier_dimerization_2016, PPR is scaled by a factor of
 0.65 to account for a fraction of the vesicle pool used that is refractory to
@@
 The formula to which the data is fitted has evolved over time and `flippant`
-supports both the original (@menon_opsin_2011; @goren_constitutive_2014; `generation_of_algorithm = 1`), as well as the more recent iteration (@ploier_perturbed_submitted; default; `generation_of_algorithm = 2`), which
+supports both the original (@menon_opsin_2011; @goren_constitutive_2014; `generation_of_algorithm = 1`), as well as the more recent iteration (@ploier_dimerization_2016; default; `generation_of_algorithm = 2`), which
 takes into account the size distribution of the liposome polulation used and
@@
 ordered quarternary structure of the molecule in the retina 
-[@ploier_perturbed_submitted].
+[@ploier_dimerization_2016].
 
@@
 
-```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying the data in Figure 4C--F from @ploier_perturbed_submitted.** See text for command and details."}
+```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
 # Plot spectral traces (Figure 1)
@@
 
-```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of data in Figure 4C--F from @ploier_perturbed_submitted.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details).
+```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details).
 In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit.
@@
 PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
-figure2 %<>% add_panel(
+figure2 %<>% multipanelfigure::add_panel(
   top_panel = 1,
@@
 following more closely the analysis in Figure 4C--F by
-@ploier_perturbed_submitted, a single fit may be performed for the combined data
+@ploier_dimerization_2016, a single fit may be performed for the combined data
 from all experiments as follows, resulting in Figure 2B:
@@
   row.names = FALSE,
-  caption = "**Tabular output of `flippant`--based reanalysis of data in Figure 4C--F from @ploier_perturbed_submitted.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
+  caption = "**Tabular output of `flippant`--based reanalysis of data in Figure 4C--F from @ploier_dimerization_2016.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
 ```
@@
 `r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
-prior manual analysis by @ploier_perturbed_submitted (Table S2), where $\alpha
+prior manual analysis by @ploier_dimerization_2016 (Table S2), where $\alpha
 \times 10^4 \approx 16$ was reported for mutant and $\alpha \times 10^4 \approx
 7$ for wild type rhodopsin. Based on the manual analysis of the data we conclude
-in @ploier_perturbed_submitted that the mutant rhodopsins investigated are
+in @ploier_dimerization_2016 that the mutant rhodopsins investigated are
 reconstituted into proteoliposomes in monomeric form, contrary to the wild type,
@@
 R as an environment for statistical computing and graphics 
-[@r_core_team_r:_2015], scientists can quickly analyse such data and arrive at 
+[@r_core_team_r:_2016], scientists can quickly analyse such data and arrive at 
 publication--grade graphics that offer extensive facilities for individual 

### 2016-07-16 inst/manuscript/manuscript.rmd
Remove "Funding" section and integrate content into "Acknowledgements";
Finalize (supported by "R CMD check") transition to "::" notation;

@@
 ```{r calculate_pprs, echo = FALSE}
-max_PPR <- read.delim(
+max_PPR <- utils::read.delim(
     file.path(tmpDir,"inputTable.txt"),
@@
 
-# Funding
+# Acknowledgements
 J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
@@
 
-# Acknowledgements
-
 # References

### 2016-07-16 R/parse_felix_32_output.R

@@ -9,9 +9,8 @@
 #' @seealso \code{\link{parse_fluorimeter_output}}, 
 #' \code{\link[flippant]{parse_felix_gx_output}},
 #' \code{\link[flippant]{parse_manual_output}}
-#' @importFrom assertive.properties assert_is_not_null
-#' @importFrom assertive.strings assert_all_are_non_missing_nor_empty_character
 #' @importFrom magrittr %>%
+#' @importFrom magrittr %<>%
 #' @author Johannes Graumann
 #' @keywords manip IO file
 parse_felix_32_output <- function(x = NULL){

### 2016-07-16 R/parse_felix_gx_output.R

@@ -9,8 +9,6 @@
 #' @seealso \code{\link{parse_fluorimeter_output}}, 
 #' \code{\link[flippant]{parse_felix_32_output}},
 #' \code{\link[flippant]{parse_manual_output}}
-#' @importFrom assertive.properties assert_is_not_null
-#' @importFrom assertive.strings assert_all_are_non_missing_nor_empty_character
 #' @author Johannes Graumann
 #' @keywords manip IO file
 parse_felix_gx_output <- function(x = NULL){

### 2016-07-16 R/parse_fluorimeter_output.R

@@ -47,15 +47,6 @@
 #' @author Johannes Graumann
 #' @keywords manip IO file
 #' @examples
-#' # stop("Function is missing examples!")
-#' @importFrom assertive.files assert_all_are_readable_files
-#' @importFrom assertive.types assert_is_a_bool
-#' @importFrom assertive.types assert_is_a_string
-#' @importFrom RcppRoll roll_mean
-#' @importFrom utils tail
-#' @importFrom wmtsa wavCWT
-#' @importFrom wmtsa wavCWTPeaks
-#' @importFrom wmtsa wavCWTTree
 #' @export
 parse_fluorimeter_output <- function(
   spec_file = NULL,
@@ -77,12 +68,12 @@ parse_fluorimeter_output <- function(
   if(
     grepl(pattern="^<Trace>\\s*$",x=linesInSpecFile[1],ignore.case=TRUE) &
       grepl(pattern="^X\\tY\\s*$",x=linesInSpecFile[4],ignore.case=TRUE) &
-      grepl(pattern="^</Trace>\\s*$",x=tail(linesInSpecFile,n=1),ignore.case=TRUE)){
+      grepl(pattern="^</Trace>\\s*$",x=utils::tail(linesInSpecFile,n=1),ignore.case=TRUE)){
     formatOfSpecFile <- "FelixGXv4.1.0.3096"
   } else if(
     grepl(pattern="^1\\s*$",x=linesInSpecFile[1],ignore.case=TRUE) &
       grepl(pattern="^X\\tY\\s*$",x=linesInSpecFile[4],ignore.case=TRUE) &
-      grepl(pattern="^\\d+\\.{1,1}\\d+\t\\d+\\s*$",x=tail(linesInSpecFile,n=1),ignore.case=TRUE)
+      grepl(pattern="^\\d+\\.{1,1}\\d+\t\\d+\\s*$",x=utils::tail(linesInSpecFile,n=1),ignore.case=TRUE)
   ){
     formatOfSpecFile <- "Felix32v1.20"
   } else if(

### 2016-07-16 R/parse_manual_output.R

@@ -10,8 +10,6 @@
 #' @seealso \code{\link{parse_fluorimeter_output}},
 #' \code{\link[flippant]{parse_felix_gx_output}}, 
 #' \code{\link[flippant]{parse_felix_32_output}}
-#' @importFrom assertive.properties assert_is_not_null
-#' @importFrom assertive.strings assert_all_are_non_missing_nor_empty_character
 #' @author Johannes Graumann
 #' @keywords manip IO file
 parse_manual_output <- function(x = NULL){

### 2016-07-16 R/read_scramblase_input_file.R

@@ -1,12 +1,9 @@
-#' @importFrom assertive.files assert_all_are_readable_files
-#' @importFrom assertive.strings assert_is_a_non_empty_string
 #' @importFrom magrittr %>%
-#' @importFrom utils read.delim
 read_scramblase_input_file <- function(x){
   x %>%
     assertive.strings::assert_is_a_non_empty_string() %>%
     assertive.files::assert_all_are_readable_files() %>%
-    read.delim(
+    utils::read.delim(
       header=TRUE,
       sep="\t",
       quote="\"'",

### 2016-07-16 R/scramblase_assay_calculations.R

@@ -1,20 +1,5 @@
-#' @importFrom assertive.numbers assert_all_are_greater_than_or_equal_to
-#' @importFrom assertive.numbers assert_all_are_less_than
 #' @importFrom magrittr %>%
 #' @importFrom magrittr %<>%
-#' @importFrom magrittr equals
-#' @importFrom magrittr extract
-#' @importFrom magrittr extract2
-#' @importFrom magrittr is_less_than
-#' @importFrom magrittr is_weakly_less_than
-#' @importFrom magrittr multiply_by
-#' @importFrom magrittr set_names
-#' @importFrom magrittr subtract
-#' @importFrom minpack.lm nlsLM
-#' @importFrom stats as.formula
-#' @importFrom stats coef
-#' @importFrom stats median
-#' @importFrom stats predict
 scramblase_assay_calculations <- function(
   x,
   scale_to,
@@ -30,16 +15,16 @@ scramblase_assay_calculations <- function(
     maxit=100)
   formulae <- list(
     pre_fit = list(
-      "TRUE" = as.formula("y ~ b * ( 1 - exp( -x / a ))"),
-      "FALSE" = as.formula("y ~ b - c * exp( -x / a )")),
+      "TRUE" = stats::as.formula("y ~ b * ( 1 - exp( -x / a ))"),
+      "FALSE" = stats::as.formula("y ~ b - c * exp( -x / a )")),
     first_generation_algorithm = list(
-      "TRUE" = as.formula("y ~ b * ( 1 - exp( -x / a ) )"),
-      "FALSE" = as.formula("y ~ b - c * exp( -x / a )")),
+      "TRUE" = stats::as.formula("y ~ b * ( 1 - exp( -x / a ) )"),
+      "FALSE" = stats::as.formula("y ~ b - c * exp( -x / a )")),
     second_generation_algorithm = list(
-      # "TRUE" = as.formula("y ~ b * ( 1 - ( 1 / sqrt( 1 + 784 * a * x ) ) * exp( ( -3872 * a * x ) / ( 1 + 784 * a * x ) ) )"),
-      "TRUE" = as.formula("y ~ b * ( 1 - ( 1 / sqrt( 1 + sigma_r_bar^2 * a * x ) ) * exp( ( -a * r_bar^2 / 2 * x ) / ( 1 + sigma_r_bar^2 * a * x ) ) )"),
[…]

### 2016-07-16 R/scramblase_assay_input_template.R

@@ -1,13 +1,5 @@
 #' @rdname scramblase_assay_plot
-#' @importFrom assertive.files assert_any_are_existing_files
-#' @importFrom assertive.strings assert_is_a_non_empty_string
 #' @importFrom magrittr %>%
-#' @importFrom magrittr extract
-#' @importFrom magrittr extract2
-#' @importFrom magrittr inset2
-#' @importFrom plyr rbind.fill
-#' @importFrom utils globalVariables
-#' @importFrom utils write.table
 #' @export
 scramblase_assay_input_template <- function(path="scramblase_assay_input_template.txt"){
 # Check input -------------------------------------------------------------
@@ -79,9 +71,9 @@ scramblase_assay_input_template <- function(path="scramblase_assay_input_templat
       }
     ) %>%
     plyr::rbind.fill() %>%
-    set_names(dataStructure %>% magrittr::extract2(1)) %>%
+    magrittr::set_names(dataStructure %>% magrittr::extract2(1)) %>%
   # Write the table out
-    write.table(
+    utils::write.table(
       file=path,
       sep="\t",
       row.names=FALSE)

### 2016-07-16 R/scramblase_assay_input_validation.R

@@ -1,8 +1,3 @@
-#' @importFrom assertive.numbers assert_all_are_greater_than
-#' @importFrom assertive.properties assert_has_rows
-#' @importFrom assertive.types assert_is_a_bool
-#' @importFrom assertive.types assert_is_a_number
-#' @importFrom assertive.types assert_is_data.frame
 #' @importFrom magrittr %>%
 #' @importFrom magrittr %<>%
 scramblase_assay_input_validation <- function(

### 2016-07-16 R/scramblase_assay_stats.R

@@ -1,5 +1,4 @@
 #' @rdname scramblase_assay_plot
-#' @importFrom plyr rbind.fill
 #' @export
 scramblase_assay_stats <- function(
   x,

### 2016-07-16 R/scramblase_assay_traces.R

@@ -1,7 +1,4 @@
 #' @rdname scramblase_assay_plot
-#' @import ggplot2
-#' @importFrom assertive.types assert_is_a_number
-#' @importFrom plyr rbind.fill
 #' @export
 scramblase_assay_traces <- function(
   x,

### 2016-07-16 R/parse_fluorimeter_output.R
Add examples;

@@ -47,6 +47,20 @@
 #' @author Johannes Graumann
 #' @keywords manip IO file
 #' @examples
+#' library(magrittr)
+#' # Extract example data
+#' tmpDir <- tempdir()
+#' file.path("extdata", "PloierEtAl_Data.zip") %>%
+#'  system.file(
+#'    package = "flippant",
+#'    mustWork = TRUE) %>%
+#'  unzip(
+#'    overwrite = TRUE,
+#'    exdir = tmpDir)
+#' # Parse an exemplary file
+#' file.path(tmpDir, "wildtypeEx1_0.txt") %>%
+#'   parse_fluorimeter_output() %>%
+#'   str()
 #' @export
 parse_fluorimeter_output <- function(
   spec_file = NULL,

### 2016-07-16 R/scramblase_assay_plot.R

@@ -179,16 +179,17 @@
 #' @import ggplot2
 #' @importFrom plyr rbind.fill
 #' @examples
-#' stop("Cite Birgit's paper.")
-#' # Extract the packaged example data from Ploier et al (2016)
+#' library(magrittr)
+#' library(ggplot2)
+#' # Extract example data
 #' tmpDir <- tempdir()
-#' unzip(
-#'   system.file(
-#'     file.path("extdata", "PloierEtAl_Data.zip"),
-#'     package = "flippant",
-#'     mustWork = TRUE),
-#'   overwrite = TRUE,
-#'   exdir = tmpDir)
+#' file.path("extdata", "PloierEtAl_Data.zip") %>%
+#'  system.file(
+#'    package = "flippant",
+#'    mustWork = TRUE) %>%
+#'  unzip(
+#'    overwrite = TRUE,
+#'    exdir = tmpDir)
 #' setwd(tmpDir)
 #' # Plot the spectal traces
 #' scramblase_assay_traces(
@@ -196,10 +197,14 @@
 #'   time_max_sec = 350)
 #' # Plot the PPR plot(s) faceting by experiment
 #' scramblase_assay_plot("inputTable.txt")
+#' # Modify x-axis to avoid visual compression
+#' scramblase_assay_plot("inputTable.txt") +
+#'   xlim(0, 3)
 #' # Generate tabular results
 #' scramblase_assay_stats("inputTable.txt")
 #' # Plot the PPR plot(s) forgoing faceting by experiment
-#' scramblase_assay_plot("inputTable.txt", split_by_experiment = FALSE)
+#' scramblase_assay_plot("inputTable.txt", split_by_experiment = FALSE) +
+#'   xlim(0, 3)
 #' # Generate tabular results
 #' scramblase_assay_stats("inputTable.txt", split_by_experiment = FALSE)
 scramblase_assay_plot <- function(

### 2016-07-16 R/scramblase_assay_plot.R
A last "@importFrom" remnant ...

@@ -177,7 +177,6 @@
 #' @export
 #' @seealso \code{\link{parse_fluorimeter_output}} \code{\link{nlsLM}}
 #' @import ggplot2
-#' @importFrom plyr rbind.fill
 #' @examples
 #' library(magrittr)
 #' library(ggplot2)

### 2016-07-16 R/scramblase_assay_plot.R
Fix "Accepted" --> "In Press";

@@ -174,6 +174,11 @@
 #' Cherezov, V., Stevens, R.C., Ernst, O.P., and Menon, A.K. (2014). 
 #' Constitutive phospholipid scramblase activity of a G Protein-coupled 
 #' receptor. Nat Commun 5, 5115.
+#' 
+#' Ploier, B., Caro, L.N., Morizumi, T., Pandey, K., Pearring, J.N.,
+#' Goren, M.A., Finnemann, S.C., Graumann, J., Arshavsky, V.Y., Dittman, J.S.,
+#' Ernst, O.P., Menon, A.K. (2016). Dimerization deficiency of enigmatic
+#' retinitis pigmentosa-linked rhodopsin mutants. Nat Commun. In Press.
 #' @export
 #' @seealso \code{\link{parse_fluorimeter_output}} \code{\link{nlsLM}}
 #' @import ggplot2

### 2016-07-16 inst/manuscript/manuscript.rmd
R-enable explicitly loading flippant to achieve formated code-chunk presentation;

@@
 ```{r setting_up_r, echo = FALSE, message = FALSE}
+library(flippant, quietly = TRUE)
 library(magrittr, quietly = TRUE)

### 2016-07-16 inst/manuscript/manuscript.rmd
Clarifying in captions that we are only presenting a subset of the data from Ploier et al 2016;

@@
 
-```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
+```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
 # Plot spectral traces (Figure 1)
@@
 
-```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details).
+```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details).
 In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit.
@@
   row.names = FALSE,
-  caption = "**Tabular output of `flippant`--based reanalysis of data in Figure 4C--F from @ploier_dimerization_2016.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
+  caption = "**Tabular output of `flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
 ```

### 2016-07-16 inst/manuscript/manuscript.rmd
Remove xlim (and all references to it, as the new dataset does NOT contain an outlier requiring it;

@@
 # Plot PPR plot (Figure 2A)
-scramblase_assay_plot(
-  "inputTable.txt") +
-xlim(0, 3)
+scramblase_assay_plot("inputTable.txt")
 ```
@@
     ggplot2::theme_bw() + 
-    ggplot2::xlim(0, 3) + 
     ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
@@
 
-```{r calculate_pprs, echo = FALSE}
-max_PPR <- utils::read.delim(
-    file.path(tmpDir,"inputTable.txt"),
-    check.names = FALSE) %>%
-  flippant:::calculate_ppr() %>%
-  max(
-    na.rm = TRUE) %>%
-  signif(
-    digits = 2
-  )
-```
-
 The call results in the protein to phospholipid ratio (PPR) plot shown in
-Figure 2A. Using the customization facilities provided by `ggplot2` 
-[@wickham_ggplot2_2009] as a plotting system the plot's x--axis is trimmed to
-avoid visual compression of all data by a single data point from the wild type 
-rhodopsin series in experiment 1, where $\text{PPR}=`r max_PPR`$.
+Figure 2A.
 
@@
   "inputTable.txt",
-  split_by_experiment = FALSE) + 
-xlim(0, 3)
+  split_by_experiment = FALSE)
 ```

### 2016-07-16 R/scramblase_assay_plot.R

@@ -201,14 +201,10 @@
 #'   time_max_sec = 350)
 #' # Plot the PPR plot(s) faceting by experiment
 #' scramblase_assay_plot("inputTable.txt")
-#' # Modify x-axis to avoid visual compression
-#' scramblase_assay_plot("inputTable.txt") +
-#'   xlim(0, 3)
 #' # Generate tabular results
 #' scramblase_assay_stats("inputTable.txt")
 #' # Plot the PPR plot(s) forgoing faceting by experiment
-#' scramblase_assay_plot("inputTable.txt", split_by_experiment = FALSE) +
-#'   xlim(0, 3)
+#' scramblase_assay_plot("inputTable.txt", split_by_experiment = FALSE)
 #' # Generate tabular results
 #' scramblase_assay_stats("inputTable.txt", split_by_experiment = FALSE)
 scramblase_assay_plot <- function(

### 2016-07-16 inst/manuscript/manuscript.rmd
Add yaml headers for word and html conversion;

@@
 author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^,
-  Anant K. Menon ^‡^ and Johannes Graumann ^†,^*
+  Anant K. Menon^‡^ and Johannes Graumann ^†,^*
 date: '`r format(Sys.Date(), "%B %d,%Y")`'
@@
     fig_caption: yes
+  html_document:
+    fig_caption: yes
   word_document:
-    fig_caption: yes
-  html_document:
     fig_caption: yes

### 2016-07-19 inst/manuscript/manuscript.rmd
capitalized Bioconductor

@@
 `flippant` has been implemented in `R` [@r_core_team_r:_2016] and integrated 
-into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
+into the `Bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
 within a functional `R` environment:

### 2016-07-19 inst/manuscript/manuscript.rmd
show how to extract template file

@@
 ```{r noeval_demonstrate_traces, eval = FALSE}
+template_file <- "extdata/PloierEtAl_Data.zip" %>% 
+  system.file(package = "flippant") %>% 
+  unzip(files = "inputTable.txt")
 # Plot spectral traces (Figure 1)
 scramblase_assay_traces(
-  "inputTable.txt",
+  template_file,
   time_max_sec = 350)
+```
+
+```{r define_template_file, echo = FALSE}
+template_file <- "inputTable.txt"
 ```
@@
 x <- tmpDir %>%
-  file.path("inputTable.txt") %>%
+  file.path(template_file) %>%
   flippant:::read_scramblase_input_file()
@@
 # Plot PPR plot (Figure 2A)
-scramblase_assay_plot("inputTable.txt")
+scramblase_assay_plot(template_file)
 ```
@@
 scramblase_assay_plot(
-  "inputTable.txt",
+  template_file,
   split_by_experiment = FALSE)
@@
 scramblase_assay_stats(
-  "inputTable.txt",
+  template_file,
   split_by_experiment = FALSE)

### 2016-07-19 inst/manuscript/manuscript.rmd
tmpDir -> analysis_dir for clarity

@@
 
-tmpDir <- tempdir()
+analysis_dir <- tempdir()
 file.path("extdata", "PloierEtAl_Data.zip") %>%
@@
     overwrite = TRUE,
-    exdir = tmpDir)
+    exdir = analysis_dir)
 
@@
 ```{r noeval_demonstrate_traces, eval = FALSE}
+analysis_dir <- tempdir()
 template_file <- "extdata/PloierEtAl_Data.zip" %>% 
   system.file(package = "flippant") %>% 
-  unzip(files = "inputTable.txt")
+  unzip(files = "inputTable.txt", exdir = analysis_dir)
+
 # Plot spectral traces (Figure 1)
@@
 # Plot spectral traces (Figure 1)
-x <- tmpDir %>%
+x <- analysis_dir %>%
   file.path(template_file) %>%
   flippant:::read_scramblase_input_file()
-x[["Path"]] <- file.path(tmpDir, x[["Path"]])
+x[["Path"]] <- file.path(analysis_dir, x[["Path"]])
 flippant::scramblase_assay_traces(

### 2016-07-19 R/read_scramblase_input_file.R
turn off warning in assert_all_are_readable_files

@@ -2,7 +2,7 @@
 read_scramblase_input_file <- function(x){
   x %>%
     assertive.strings::assert_is_a_non_empty_string() %>%
-    assertive.files::assert_all_are_readable_files() %>%
+    assertive.files::assert_all_are_readable_files(warn_about_windows = FALSE) %>%
     utils::read.delim(
       header=TRUE,
       sep="\t",

### 2016-07-19 inst/manuscript/manuscript.rmd
simplify data read and fig 1

--- 2016-07-19 inst/manuscript/manuscript.rmd
@@
       collapse = "")} )
-
-tmpDir <- tempdir()
-file.path("extdata", "PloierEtAl_Data.zip") %>%
-  system.file(
-    package = "flippant",
-    mustWork = TRUE) %>%
-  unzip(
-    overwrite = TRUE,
-    exdir = tmpDir)
 
@@
 
-`flippant`s capabilities are demonstrated here by reanalyzing a subset of the
-data underlying  Figure 4C--F in @ploier_dimerization_2016. The following work
-flow in a first  step plots the corresponding spectral traces (Figure 1). Note
+`flippant`'s capabilities are demonstrated here by reanalyzing a subset of the
+data underlying Figure 4C--F in @ploier_dimerization_2016. The first step is to
+extract the data files, stored in a ZIP archive within the pacakge.
+
+```{r extract_case_study_dataset}
+analysis_dir <- file.path(tempdir(), "flippant-case-study")
+extract_case_study_data(analysis_dir)
+template_file <- file.path(analysis_dir, "inputTable.txt")
+```
+
+To begin the analysis it is useful to plot the spectral traces of each 
+experimental series (Figure 1). Note
 that algorithmic alignment to the time of dithionite addition is employed
@@
 
-```{r noeval_demonstrate_traces, eval = FALSE}
-template_file <- "extdata/PloierEtAl_Data.zip" %>% 
-  system.file(package = "flippant") %>% 
-  unzip(files = "inputTable.txt")
+```{r figure1_creation, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
 # Plot spectral traces (Figure 1)
@@
   template_file,
-  time_max_sec = 350)
-```
-
-```{r define_template_file, echo = FALSE}
-template_file <- "inputTable.txt"
-```
-
-```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
-# Plot spectral traces (Figure 1)
-x <- tmpDir %>%
-  file.path(template_file) %>%
-  flippant:::read_scramblase_input_file()
-x[["Path"]] <- file.path(tmpDir, x[["Path"]])
-flippant::scramblase_assay_traces(
-  x,
   time_max_sec = 350)

### 2016-07-19 inst/manuscript/manuscript.rmd
use template file in fig 2

@@
   top_panel = 1,
-  panel = flippant::scramblase_assay_plot(x) + 
+  panel = flippant::scramblase_assay_plot(template_file) + 
     ggplot2::theme_bw() + 
@@
   top_panel = 2,
-  panel = flippant::scramblase_assay_plot(x, split_by_experiment = FALSE) + 
+  panel = flippant::scramblase_assay_plot(template_file, split_by_experiment = FALSE) + 
     ggplot2::theme_bw() + 

### 2016-07-19 inst/manuscript/manuscript.rmd
simplify get dependencies

@@
 library(magrittr, quietly = TRUE)
-flippant_dependencies <- packageDescription("flippant",fields=c("Depends","Imports")) %>%
-  unlist(use.names = FALSE) %>%
-  stringi::stri_split(regex = ",", omit_empty = TRUE) %>%
-  unlist(use.names = FALSE) %>%
-  stringi::stri_replace_all(replacement = "", regex = "\\s*\\(.*\\)\\s*", omit_empty = TRUE) %>%
-  stringi::stri_replace_all(replacement = "", regex = "\\s*", omit_empty = TRUE) %>%
-  tail(n=length(.) - 1) %>%
-  sort() %>%
-  ( function(x){
-    paste0(
-      c(
-        "`",
-        paste0(head(x, n = length(x) - 1), collapse = "`, `"),
-        "` and `",
-        tail(x, n = 1),
-        "`"),
-      collapse = "")} )
+to_string <- function(x)
+{
+  paste(toString(head(x, -1)), "and", tail(x, 1))
+}
+
+# Copied from sig:::backquote
+backquote <- function (x)
+{
+    x <- gsub("`", "\\\\`", x)
+    paste0("`", x, "`")
+}
+flippant_dependencies <- "flippant" %>%
+  tools::package_dependencies(installed.packages()) %>%
+  extract2("flippant") %>%
+  backquote %>%
+  to_string
 

### 2016-07-19 inst/manuscript/manuscript.rmd
simplify get ppr results as text

@@
   magrittr::extract2("Experimental Series") %>%
-  head(n = nrow(ppr_results) - 1) %>%
-  paste(collapse = ", ") %>%
-  paste("and") %>%
-  paste(tail(ppr_results$`Experimental Series`, n = 1))
+  to_string
 ppr_results_alpha_print <- ppr_results %>%
@@
   round(2) %>%
-  head(n = nrow(ppr_results) - 1) %>%
-  paste(collapse = ", ") %>%
-  paste("and") %>%
-  paste(tail(ppr_results$`Fit Constant ($\\times 10^4$)`, n = 1))
+  to_string
 knitr::kable(

### 2016-07-22 inst/manuscript/manuscript.rmd
Magrittrize the microbenchmarking read-out and switch to use of MAD;

--- 2016-07-19 inst/manuscript/manuscript.rmd
@@
       collapse = "")} )
+
+tmpDir <- tempdir()
+file.path("extdata", "PloierEtAl_Data.zip") %>%
+  system.file(
+    package = "flippant",
+    mustWork = TRUE) %>%
+  unzip(
+    overwrite = TRUE,
+    exdir = tmpDir)
 
@@
 `flippant` has been implemented in `R` [@r_core_team_r:_2016] and integrated 
-into the `Bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
+into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
 within a functional `R` environment:
@@
 
-`flippant`'s capabilities are demonstrated here by reanalyzing a subset of the
-data underlying Figure 4C--F in @ploier_dimerization_2016. The first step is to
-extract the data files, stored in a ZIP archive within the pacakge.
-
-```{r extract_case_study_dataset}
-analysis_dir <- file.path(tempdir(), "flippant-case-study")
-extract_case_study_data(analysis_dir)
-template_file <- file.path(analysis_dir, "inputTable.txt")
-```
-
-To begin the analysis it is useful to plot the spectral traces of each 
-experimental series (Figure 1). Note
+`flippant`s capabilities are demonstrated here by reanalyzing a subset of the
+data underlying  Figure 4C--F in @ploier_dimerization_2016. The following work
+flow in a first  step plots the corresponding spectral traces (Figure 1). Note
 that algorithmic alignment to the time of dithionite addition is employed
@@
 
-```{r figure1_creation, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
+```{r noeval_demonstrate_traces, eval = FALSE}
 # Plot spectral traces (Figure 1)
 scramblase_assay_traces(
-  template_file,
+  "inputTable.txt",
+  time_max_sec = 350)
+```
+
+```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
+# Plot spectral traces (Figure 1)
+x <- tmpDir %>%
+  file.path("inputTable.txt") %>%
+  flippant:::read_scramblase_input_file()
+x[["Path"]] <- file.path(tmpDir, x[["Path"]])
+flippant::scramblase_assay_traces(
+  x,
   time_max_sec = 350)
@@
 # Plot PPR plot (Figure 2A)
-scramblase_assay_plot(template_file)
+scramblase_assay_plot("inputTable.txt")
 ```
@@
   top_panel = 1,
-  panel = flippant::scramblase_assay_plot(template_file) + 
+  panel = flippant::scramblase_assay_plot(x) + 
     ggplot2::theme_bw() + 
@@
   top_panel = 2,
-  panel = flippant::scramblase_assay_plot(template_file, split_by_experiment = FALSE) + 
+  panel = flippant::scramblase_assay_plot(x, split_by_experiment = FALSE) + 
     ggplot2::theme_bw() + 
@@
 scramblase_assay_plot(
-  template_file,
+  "inputTable.txt",
   split_by_experiment = FALSE)
@@
 scramblase_assay_stats(
-  template_file,
+  "inputTable.txt",
   split_by_experiment = FALSE)
@@
 
-analysis_timing_median <- signif(
-  summary(
-    analysis_timing)$median,
-  2)
+analysis_timing_median <- analysis_timing %>%
+  summary() %>%
+  magrittr::extract2("median") %>%
+  signif(2)
 
-analysis_timing_iqr <- signif(
-  diff(
-    unlist(
-      summary(analysis_timing)[c("lq", "uq")],
-      use.names = FALSE)),
-  2)
+analysis_timing_mad <- analysis_timing %>%
+  magrittr::extract2("time") %>%
+  mad() %>%
+  magrittr::divide_by(1E9) %>%
+  signif(2)
 ```
@@
 take a mere `r analysis_timing_median` seconds (median; 
-$\text{IQR}=`r analysis_timing_iqr`~\text{s}$; $n=`r analysis_timing_n`$).
+$\text{MAD}=`r analysis_timing_mad`~\text{s}$; $n=`r analysis_timing_n`$).
 

### 2016-07-23 inst/manuscript/manuscript.rmd
Integtrate changes by AKM;

@@
 ---
-title: '`flippant` --- An `R` package for the automated analysis of dithionite scramblase
-  assays'
+title: '`flippant` --- An `R` package for the automated analysis of
+  fluorescense--based scramblase assays'
 author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^,
@@
 # Abstract
-Dithionite scramblase assays are an established means of probing the lipid 
-scrambling activity of protein extracts and purified proteins. While the assay
-has yielded insight into the scramblase activity in crude membrane preparations,
+The lipid scrambling activity of protein extracts and purified scramblases is
+typically measured using a fluorescence--based assay. While the assay has
+yielded insight into the scramblase activity in crude membrane preparations,
 functional validation of candidate scramblases, stoichiometry of scramblase 
@@
 equilibration of lipids between the leaflets of lipid bilayers that constitute 
-biological membranes [@waechter_flippases_2013]. Independent of energy 
-equivalents such as ATP they facilitate this ``flipping'' by providing a 
-mechanism of transition through the hydrophobic environment of membranes to 
-polar lipid head groups, thus reducing the massive energetic cost that process 
-would carry otherwise [@kornberg_inside-outside_1971]. The underlying molecular 
-mechanisms remain largely enigmatic [for a discussion including exceptions see @ernst_phospholipid_2015].
+biological membranes
+[@waechter_flippases_2013;@pomorski_lipid_2006;brunner_structural_2016].
+Independent of energy  equivalents such as ATP they facilitate this "flipping"
+by providing a mechanism by which polar lipid head groups can transition through
+the hydrophobic environment of membranes, thus reducing the massive energetic
+cost this process would carry otherwise [@kornberg_inside-outside_1971]. The
+underlying molecular  mechanisms remain largely enigmatic [for a discussion
+including exceptions see @ernst_phospholipid_2015].
 Proteins supporting flipping processes as central as the equilibration of the 
@@
 be identified [@menon_specific_2000]. 
-None the less, there has been much recent progress in scramblase identification 
+Nonetheless, there has been much recent progress in scramblase identification 
 and characterization. Proteins shown to have scramblase activity include 
@@
 Upon addition of membrane--impermeable reducing agents such as dithionite to 
-these liposomes, fluorophores in the external leaflet are quenched and fluorescence in scramblase--free liposomes accordingly quickly drops to approximately 50% of the 
-initial value. However, for proteoliposomes reconstituted with proteins 
-conferring a scramblase activity, fluorescence disappears entirely, as
-fast scramblase--mediated equilibration between outer (exposed) and inner
-(protected) leaflet of the bilayer renders all fluorescent lipids
-accessible to reduction. By titration of the protein amount reconstituted into
-the liposome membranes it is thus possible to characterize scramblases and probe
-their activity. Beyond the identification of scramblase activities in crude 
-membrane preparations [@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
-functional validation of candidate scramblases [@menon_opsin_2011;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014], the 
-assay has also been used to characterize the stoichiometry of scramblase 
+these liposomes, fluorophores in the external leaflet are reduced and
+fluorescence in scramblase--free liposomes accordingly quickly drops to
+approximately 50% of the initial value. However, for proteoliposomes
+reconstituted with proteins  conferring a scramblase activity, fluorescence
+disappears almost entirely, as fast scramblase--mediated equilibration between
+outer (exposed) and inner (protected) leaflet of the bilayer renders all
+fluorescent lipids accessible to reduction. By titration of the protein amount
+reconstituted into the liposome membranes it is thus possible to characterize
+scramblases and probe their activity. Beyond the identification of scramblase
+activities in crude membrane preparations
+[@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
+functional validation of candidate scramblases [@menon_opsin_2011;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014mohammadi_specificity_2014],
+the  assay has also been used to characterize the stoichiometry of scramblase 
 homo--multimers reconstituting into the proteoliposomes 
@@
 Starting with the identification of baseline and post--reduction fluorescence 
-from fluorometer--generated spectra, via the calculation of the underlying 
+from fluorimeter--generated spectra, via the calculation of the underlying 
 statistics and through publication--grade representation of the results, data 
@@
 requires for each data point information on the path to the 
-fluorometer--generated spectrum, the amount of protein used to reconstitute 
+fluorimeter--generated spectrum, the amount of protein used to reconstitute 
 proteoliposomes, the assay volume before and after addition of 
@@
 Spectral input data is read by `flippant` using the file paths provided in the
-spreadsheet. Raw spectra produced by QuantaMaster fluorometer instruments 
+spreadsheet. Raw spectra produced by QuantaMaster fluorimeter instruments 
 (Photon Technology International, Inc., Edison, New Jersey) running software 
@@
 @ploier_dimerization_2016 and largely keeping with nomenclature used therein,
-data is processed as follows. Input is format checked and defaults are injected
+data are processed as follows. Input is format checked and defaults are injected
 for facultative parameters/columns as appropriate. 
@@
 scramblase reconstitution. This behavior can be modified using the 
-`ppr_scale_factor` parameter and avoided alltogether setting it to `NULL`.
+`ppr_scale_factor` parameter and avoided altogether setting it to `NULL`.
 
@@
 supports both the original (@menon_opsin_2011; @goren_constitutive_2014; `generation_of_algorithm = 1`), as well as the more recent iteration (@ploier_dimerization_2016; default; `generation_of_algorithm = 2`), which
-takes into account the size distribution of the liposome polulation used and
+takes into account the size distribution of the liposome population used and
 thus also requires parameters for liposome radius and its standard deviation 
@@
 transducin activation, may in fact be impacted in their scramblase activity.
-This hypothesis was disproved when tested using the dithionite scramblase assay
-among other techniques. However, the same set of experiments pointed at a defect 
-in rhodopsin dimerization prior to insertion into liposomes, generating the new 
-hypothesis that the mutations may cause disease by interfering with the highly 
-ordered quarternary structure of the molecule in the retina 
+This hypothesis was disproved. However, the same set of experiments pointed at a
+defect  in rhodopsin dimerization prior to insertion into liposomes, generating
+the new hypothesis that the mutations may cause disease by interfering with the
+highly ordered quarternary structure of rhodopsin in the retina 
 [@ploier_dimerization_2016].
@@
 `flippant`, in conclusion, provides means for quick, reproducible data analysis
-in the context of dithionite scramblase analysis and a platform for review, 
+in the context of scramblase activity analysis and a platform for review, 
 dissemination and extension of the strategies it employs. As BSA--back 

### 2016-07-23 inst/manuscript/manuscript.rmd
Add the possibility of divergence contribution by dithionite addition time point determination;
Clarification requested by B.P.;

@@
 requires for each data point information on the path to the 
-fluorimeter--generated spectrum, the amount of protein used to reconstitute 
+fluorimeter--generated spectrum, the amount of protein reconstituted into
 proteoliposomes, the assay volume before and after addition of 
@@
 algorithm as implemented by @elzhov_minpack.lm:_2015) and 
-general handling of significant digits and rounding.
+general handling of significant digits and rounding. Another potential source
+of minor divergence is the algorithmic *versus* manual determination of the time
+point at which reductant is added in an experiment, potentialy resulting in
+slightly differing determination of relative fluorescence reduction.
 

### 2016-07-24 inst/manuscript/manuscript.rmd
fixed x -> template_file in manuscript

@@
 ppr_results <- flippant::scramblase_assay_stats(
-    x, split_by_experiment = FALSE) %>%
+    template_file, split_by_experiment = FALSE) %>%
   dplyr::mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
@@
   flippant::scramblase_assay_traces(
-    x,
+    template_file,
     time_max_sec = 350)
   flippant::scramblase_assay_plot(
-    x)
+    template_file)
   flippant::scramblase_assay_plot(
-    x,
+    template_file,
     split_by_experiment = FALSE)
   flippant::scramblase_assay_stats(
-    x,
+    template_file,
     split_by_experiment = FALSE)

### 2016-07-24 inst/manuscript/manuscript.rmd
typo fix

@@
 of minor divergence is the algorithmic *versus* manual determination of the time
-point at which reductant is added in an experiment, potentialy resulting in
+point at which reductant is added in an experiment, potentially resulting in
 slightly differing determination of relative fluorescence reduction.

### 2016-07-25 R/scramblase_assay_input_template.R
Fix another instance of "Protein in Reconstitution";

@@ -13,7 +13,7 @@ scramblase_assay_input_template <- function(path="scramblase_assay_input_templat
     ## Available fileds/columns
     columnName = c(
       "Path",
-      "Protein in Reconstitution (mg)",
+      "Protein Reconstituted (mg)",
       "Fluorescence Assay Vol. w/o DT (ul)",
       "Fluorescence Assay Vol. with DT (ul)",
       "Lipid in Reconstitution (mmol)",

### 2016-07-25 inst/manuscript/manuscript.rmd
Minor reformatting;
Minor edit;

--- 2016-07-24 inst/manuscript/manuscript.rmd
@@
 ---
-title: '`flippant` --- An `R` package for the automated analysis of
-  fluorescense--based scramblase assays'
-author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^,
-  Anant K. Menon^‡^ and Johannes Graumann ^†,^*
+title: '`flippant` --- An `R` package for the automated analysis of fluorescense--based
+  scramblase assays'
+author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon^‡^
+  and Johannes Graumann ^†,^*
 date: '`r format(Sys.Date(), "%B %d,%Y")`'
@@
 
-The resulting values for the fit constant $\alpha$ correspond with
+The resulting values for the fit constant correspond with
 `r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the

### 2016-09-11 inst/manuscript/manuscript.rmd
Minor reformatting;

@@
 output:
+  word_document:
+    fig_caption: yes
   pdf_document:
@@
   html_document:
-    fig_caption: yes
-  word_document:
     fig_caption: yes

### 2016-09-11 inst/manuscript/manuscript.rmd
Fix various citation snafus;

@@
 biological membranes
-[@waechter_flippases_2013;@pomorski_lipid_2006;brunner_structural_2016].
+[@waechter_flippases_2013;@pomorski_lipid_2006;@brunner_structural_2016].
 Independent of energy  equivalents such as ATP they facilitate this "flipping"
@@
 [@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
-functional validation of candidate scramblases [@menon_opsin_2011;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014mohammadi_specificity_2014],
+functional validation of candidate scramblases [@menon_opsin_2011;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014;@mohammadi_specificity_2014],
 the assay has also been used to characterize the stoichiometry of scramblase 

### 2016-09-11 inst/manuscript/manuscript.rmd
Reformat and ammend the abstract to follow BMC Bioinformatic's requirements;

@@
 # Abstract
-The lipid scrambling activity of protein extracts and purified scramblases is
-typically measured using a fluorescence--based assay. While the assay has
-yielded insight into the scramblase activity in crude membrane preparations,
-functional validation of candidate scramblases, stoichiometry of scramblase 
-complexes as well as ATP--dependence of flippases, data analysis in its context 
-has remained a task involving many manual steps. With the extension package 
-`flippant` to `R`, a free software environment for statistical computing and 
-graphics, we introduce an integrated solution for the analysis and 
-publication--grade graphical presentation of dithionite scramblase assays and 
-demonstrate its utility in revisiting an originally manual analysis from the 
-publication record, closely reproducing the reported results.
+**Background:** The lipid scrambling activity of protein extracts and purified
+scramblases is typically measured using a fluorescence--based assay. While the
+assay has yielded insight into the scramblase activity in crude membrane
+preparations, functional validation of candidate scramblases, stoichiometry of
+scramblase complexes as well as ATP--dependence of flippases, data analysis in
+its context has remained a task involving many manual steps.
+
+**Results:** With the extension package `flippant` to `R`, a free software
+environment for statistical computing and graphics, we introduce an integrated
+solution for the analysis and publication--grade graphical presentation of
+dithionite scramblase assays and demonstrate its utility in revisiting an
+originally manual analysis from the publication record, closely reproducing the
+reported results.
+
+**Conclusions:**  `flippant` allows for quick, reproducible data analysis of
+scramblase activity assays and provides a platform for review, dissemination and
+extension of the strategies it employs.
 

### 2016-09-11 inst/manuscript/manuscript.rmd
Add a keywords section;

@@
 # Introduction
+# Keywords
+scramblase; sithionite scramblase assay; R
+
 Scramblases are proteins mediating the bidirectional, mass--action driven 

### 2016-09-11 inst/manuscript/manuscript.rmd
Adapt headers to better fit BMC Bioinformatic's requirements;

--- 2016-09-11 inst/manuscript/manuscript.rmd
@@
 
-# Introduction
+# Keywords
+scramblase; sithionite scramblase assay; R
+
+# Background
 Scramblases are proteins mediating the bidirectional, mass--action driven 
@@
 
-# Conclusion
+# Conclusions
 

### 2016-09-11 inst/manuscript/manuscript.rmd
Fix a "Declariations" section according to BMC Bioinformatic's requirements;

@@
 
-# Acknowledgements
+# Declarations
+## Ethics approval and consent to participate
+Not applicable.
+
+## Consent for publication
+Not applicable.
+
+## Availability of data and material
+Upon acceptance of the manuscript, `flippant` will be depositied as a
+self--contained `R` package including all data presented in the `Bioconductor`
+collection of tools for biomedical data analysis [@huber_orchestrating_2015].
+
+## Competing interests
+The authors declare that they have no competing interests.
+
+## Funding
 J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
@@
 
+## Authors' contributions
+R.J.C and J.G. wrote the code, B.P., M.A.G. and A.K.M. guided the implementation
+and edited the manuscript, which J.G. wrote. B.P. provided the exemplary assay
+data. A.K.M. and J.G. supervised the work.
+
 # References

### 2016-09-11 inst/manuscript/manuscript.rmd
Typo fix;
Switch citation style;

@@
 ---
-title: '`flippant` --- An `R` package for the automated analysis of fluorescense--based
+title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
   scramblase assays'
@@
     fig_caption: yes
-csl: bioinformatics.csl
+csl: bmc-bioinformatics.csl
 bibliography: flippant.bib

### 2016-09-11 inst/manuscript/manuscript.rmd
Adapt to primary pdf compilation;

@@
 output:
-  word_document:
-    fig_caption: yes
   pdf_document:
@@
   html_document:
+    fig_caption: yes
+  word_document:
     fig_caption: yes

### 2016-09-11 inst/manuscript/manuscript.rmd
Fix typos;

@@
 # Keywords
-scramblase; sithionite scramblase assay; R
+scramblase; dithionite scramblase assay; R
 
@@
 data underlying Figure 4C--F in @ploier_dimerization_2016. The first step is to
-extract the data files, stored in a ZIP archive within the pacakge.
+extract the data files, stored in a ZIP archive within the package.
 
@@
 ## Availability of data and material
-Upon acceptance of the manuscript, `flippant` will be depositied as a
+Upon acceptance of the manuscript, `flippant` will be deposited as a
 self--contained `R` package including all data presented in the `Bioconductor`

### 2016-12-15 inst/manuscript/manuscript.rmd
Add author emails as editorially requested;

@@
 :   To whom correspondence should be addressed: jog2030@qatar-med.cornell.edu
+
+Author Emails
+:   Richard J. Cotton: [richierocks@gmail.com](mailto:richierocks@gmail.com)\
+    Birgit Ploier: [birgit.ploier@gmail.com](mailto:birgit.ploier@gmail.com)\
+    Michael A. Goren: [wiscmag@gmail.com](mailto:wiscmag@gmail.com)\
+    Anant K. Menon: [akm2003@med.cornell.edu](mailto:akm2003@med.cornell.edu)\
+    Johannes Graumann: [jog2030@qatar-med.cornell.edu](mailto:jog2030@qatar-med.cornell.edu)
 

### 2016-12-15 inst/manuscript/manuscript.rmd
Add a current address indicator for JG;

@@
 author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon^‡^
-  and Johannes Graumann ^†,^*
+  and Johannes Graumann ^†,§,^*
 date: '`r format(Sys.Date(), "%B %d,%Y")`'
@@
     10065, USA
+
+§
+:   Current Address: Scientific Service Group Biomolecular Mass Spectrometry, Max Planck Institute for Heart and Lung Research, W.G. Kerckhoff Institute, Ludwigstr. 43, D--61231 Bad Nauheim, Germany
 

### 2016-12-15 inst/manuscript/manuscript.rmd
Step 1 in removing figures from manuscript as requested by the editor: save them in a dedicated subdirectory;

@@
 divisor <- 20
-figure2 <- multipanelfigure::multi_panel_figure(
+figure2_plot <- multipanelfigure::multi_panel_figure(
   widths = rep(17.22), 
@@
   inter_column_spacing = 0.5)
+
+# Ensure presence of "figures" directory
+if(!dir.exists("figures")){
+  dir.create("figures")
+}
 
@@
 
-```{r figure1_creation, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
+```{r figure1-creation, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
 # Plot spectral traces (Figure 1)
-scramblase_assay_traces(
+figure1_plot <- scramblase_assay_traces(
   template_file,
   time_max_sec = 350)
+```
+```{r figure1-save, echo=FALSE}
+ggsave(
+  plot = figure1_plot,
+  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure1.png"),
+  width = 177.2,
+  units = "mm",
+  dpi = 600)
 ```
@@
 
-```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details).
+```{r figure2-creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details).
 In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit.
@@
 PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
-figure2 %<>% multipanelfigure::add_panel(
+figure2_plot %<>% multipanelfigure::add_panel(
   top_panel = 1,
@@
     ggplot2::ylab(expression(P[{phantom()>=1}])))
-figure2 %<>% multipanelfigure::add_panel(
+figure2_plot %<>% multipanelfigure::add_panel(
   top_panel = 2,
@@
     ggplot2::guides(colour = "none"))
-figure2
 ```
-
+```{r figure2-save, echo=FALSE}
+ggsave(
+  plot = figure2_plot,
+  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure2.png"),
+  width = 177.2,
+  units = "mm",
+  dpi = 600)
+```
 The call results in the protein to phospholipid ratio (PPR) plot shown in

### 2016-12-15 inst/manuscript/manuscript.rmd
Step 2 in removing figures from manuscript as requested by the editor: Move legends etc to the end; adapt code echoing as required;

@@
 
-```{r figure1-creation, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
+```{r eval=FALSE}
 # Plot spectral traces (Figure 1)
-figure1_plot <- scramblase_assay_traces(
+scramblase_assay_traces(
   template_file,
   time_max_sec = 350)
-```
-```{r figure1-save, echo=FALSE}
-ggsave(
-  plot = figure1_plot,
-  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure1.png"),
-  width = 177.2,
-  units = "mm",
-  dpi = 600)
 ```
@@
 
-```{r figure2-creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details).
-In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit.
-'adj.
-PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
-figure2_plot %<>% multipanelfigure::add_panel(
-  top_panel = 1,
-  panel = flippant::scramblase_assay_plot(template_file) + 
-    ggplot2::theme_bw() + 
-    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
-    ggplot2::ylab(expression(P[{phantom()>=1}])))
-figure2_plot %<>% multipanelfigure::add_panel(
-  top_panel = 2,
-  panel = flippant::scramblase_assay_plot(template_file, split_by_experiment = FALSE) + 
-    ggplot2::theme_bw() + 
-    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
-    ggplot2::ylab(expression(P[{phantom()>=1}])) +
-    ggplot2::facet_wrap(c("`Experimental Series`"))+
-    ggplot2::guides(colour = "none"))
-```
-```{r figure2-save, echo=FALSE}
-ggsave(
-  plot = figure2_plot,
-  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure2.png"),
-  width = 177.2,
-  units = "mm",
-  dpi = 600)
-```
 The call results in the protein to phospholipid ratio (PPR) plot shown in
@@
 
+# Figure legends
+```{r figure1-creation, echo=FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
+# Plot spectral traces (Figure 1)
+figure1_plot <- scramblase_assay_traces(
+  template_file,
+  time_max_sec = 350)
+```
+```{r figure1-save, echo=FALSE}
+ggsave(
+  plot = figure1_plot,
+  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure1.png"),
+  width = 177.2,
+  units = "mm",
+  dpi = 600)
+```
+
+```{r figure2-creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details).
+In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit.
+'adj.
+PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
+figure2_plot %<>% multipanelfigure::add_panel(
+  top_panel = 1,
+  panel = flippant::scramblase_assay_plot(template_file) + 
+    ggplot2::theme_bw() + 
+    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
+    ggplot2::ylab(expression(P[{phantom()>=1}])))
+figure2_plot %<>% multipanelfigure::add_panel(
+  top_panel = 2,
+  panel = flippant::scramblase_assay_plot(template_file, split_by_experiment = FALSE) + 
+    ggplot2::theme_bw() + 
+    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
+    ggplot2::ylab(expression(P[{phantom()>=1}])) +
+    ggplot2::facet_wrap(c("`Experimental Series`"))+
+    ggplot2::guides(colour = "none"))
+```
+```{r figure2-save, echo=FALSE}
+ggsave(
+  plot = figure2_plot,
+  filename = file.path("figures", "Cotton_et_al_-_flippant_-_Figure2.png"),
+  width = figure2_plot %>%
+    multipanelfigure::simple_grob_width(),
+  height = figure2_plot %>%
+    multipanelfigure::simple_grob_height(),
+  units = "mm",
+  dpi = 600)
+```
+
 # References

### 2016-12-15 inst/manuscript/manuscript.rmd
Step 3 in removing figures from manuscript as requested by the editor: Add dummy plots to render legends displayed;

@@
   time_max_sec = 350)
+grid::rectGrob(
+    width = grid::unit(0.1, "mm"),
+    height = grid::unit(0.1, "mm")) %>%
+  grid::grid.draw()
 ```
@@
     ggplot2::guides(colour = "none"))
+grid::rectGrob(
+    width = grid::unit(0.1, "mm"),
+    height = grid::unit(0.1, "mm")) %>%
+  grid::grid.draw()
 ```

### 2016-12-16 inst/manuscript/manuscript.rmd
Rework 'Declarations' section to conform to editorial policy and in response to reviewer;

@@
 
-## Consent for publication
+## Consent to publish
 Not applicable.
 
-## Availability of data and material
-Upon acceptance of the manuscript, `flippant` will be deposited as a
-self--contained `R` package including all data presented in the `Bioconductor`
-collection of tools for biomedical data analysis [@huber_orchestrating_2015].
+## Availability of data and materials
+The `R` package `flippant` provides all functionality as well as data presented
+here along with extensive additional documentation and example code accessible
+from within `R` in an integrated manner.
+
+The package is available as an `R` source package in the version current at
+acceptance for publication in the supplementary material and may be installed
+from that file using ` install.packages(file.choose(), type = 'source')`.
+
+The package is also uploaded to the comprehensive `R` archive network (CRAN) and
+may thus be installed in its most up--to date version using 
+`install.packages('flippant')` from within any appropriately configured `R`
+installation.
+
+Thirdly the code base and development history is publicly accessible at \
+`https://bitbucket.org/graumannlabtools/flippant`.
 
@@
 data. A.K.M. and J.G. supervised the work.
+
+## Acknowledgements
+Not applicable.
 

### 2016-12-16 inst/manuscript/manuscript.rmd
Minor reformatting;

@@
 ```
+
 ```{r figure1-save, echo=FALSE}
@@
 ```
+
 ```{r figure2-save, echo=FALSE}

### 2016-12-17 inst/manuscript/manuscript.rmd
Switch from stale bmc-bioinformatics to current biomed-central.csl citation style definition;

@@
     fig_caption: yes
-csl: bmc-bioinformatics.csl
+csl: biomed-central.csl
 bibliography: flippant.bib

### 2016-12-17 inst/manuscript/manuscript.rmd
Transition to use of bookdown for cross referencing of figures etc.; Switch from 'kable' to 'pandner' for table formatting, as text formatting in caption works flawlessly using it;

@@
 output:
-  pdf_document:
+  bookdown::pdf_document2:
+    toc: no
     fig_caption: yes
@@
     fig_caption: yes
-  word_document:
+  bookdown::word_document2:
+    toc: no
     fig_caption: yes
@@
 
-# Abstract
+# Abstract {-}
 **Background:** The lipid scrambling activity of protein extracts and purified
@@
 
-# Keywords
+# Keywords {-}
 scramblase; dithionite scramblase assay; R
 
-# Background
+# Background {-}
 Scramblases are proteins mediating the bidirectional, mass--action driven 
@@
 
-# Availablility and Implementation
+# Availablility and Implementation {-}
 `flippant` has been implemented in `R` [@r_core_team_r:_2016] and integrated 
@@
 
-# Input Data and Data Processing
+# Input Data and Data Processing {-}
 To analyse raw data stemming from dithionite scramblase assays, `flippant` 
@@
 
-# Main Features
-## Template Generation for Data Input
+# Main Features {-}
+## Template Generation for Data Input {-}
 Supporting the user in providing the input data needed, the following function 
@@
 
-## Graphic Representation of Spectral Traces
+## Graphic Representation of Spectral Traces {-}
 In a first, graphical data analytic step of a scramblase assay--derived data 
@@
 
-## Scramblase Assay Analysis
+## Scramblase Assay Analysis {-}
 Plotting protein to phospholipid ratio (PPR) against the likelihood for a given
@@
 
-# Case Study
+# Case Study {-}
 *Retinitis pigmentosa* is a degenerative disease of the retina, the majority of 
@@
 To begin the analysis it is useful to plot the spectral traces of each 
-experimental series (Figure 1). Note
+experimental series (Figure \@ref(fig:figure1-creation)). Note
 that algorithmic alignment to the time of dithionite addition is employed
@@
 The call results in the protein to phospholipid ratio (PPR) plot shown in
-Figure 2A.
+Figure \@ref(fig:figure2-creation)A.
 
-Figure 2A emphasizes reproducibility between independent experiments
-("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
-reproducibility analysis in favor of a potentially more reliable result and
-following more closely the analysis in Figure 4C--F by
+Figure \@ref(fig:figure2-creation) A emphasizes reproducibility between
+independent experiments ("Experiment 1" and "Experiment 2") on the four probed
+rhodopsins. Forgoing reproducibility analysis in favor of a potentially more
+reliable result and following more closely the analysis in Figure 4C--F by
 @ploier_dimerization_2016, a single fit may be performed for the combined data
-from all experiments as follows, resulting in Figure 2B:
+from all experiments as follows, resulting in 
+Figure \@ref(fig:figure2-creation)B:
 
@@
 difficult to visually evaluate and easy access to the numeric values desirable.
-Recapitulation of the calculations underlying PPR plot generation for Figure 2B
-by `scramblase_assay_plot` in a call to `scramblase_assay_stats`, this is achieved
-and produces tabular output represented in Table 1.
+Recapitulation of the calculations underlying PPR plot generation for Figure \@ref(fig:figure2-creation)B by `scramblase_assay_plot` in a call to
+`scramblase_assay_stats`, this is achieved and produces tabular output
+represented in Table \@ref(tab:analysis-tabular-output).
 
@@
 
-```{r analysis_tabular_output, echo = FALSE}
+```{r analysis-tabular-output, echo = FALSE}
 ppr_results <- flippant::scramblase_assay_stats(
@@
   to_string
-knitr::kable(
-  ppr_results,
-  row.names = FALSE,
-  caption = "**Tabular output of `flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
+ppr_results %>%
+  pander::pander(
+    caption = "(\\#tab:analysis-tabular-output) **Tabular output of `flippant`--based reanalysis of a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
 ```
@@
 
-# Conclusions
-
+# Conclusions {-}
 ```{r analysis_timing, echo = FALSE, cache = TRUE}
@@
 
-# Declarations
-## Ethics approval and consent to participate
+# Declarations {-}
+## Ethics approval and consent to participate {-}
 Not applicable.
 
-## Consent to publish
+## Consent to publish {-}
 Not applicable.
 
-## Availability of data and materials
+## Availability of data and materials {-}
 The `R` package `flippant` provides all functionality as well as data presented
@@
 
-## Competing interests
+## Competing interests {-}
 The authors declare that they have no competing interests.
 
-## Funding
+## Funding {-}
 J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
@@
 
-## Authors' contributions
+## Authors' contributions {-}
 R.J.C and J.G. wrote the code, B.P., M.A.G. and A.K.M. guided the implementation
@@
 
-## Acknowledgements
+## Acknowledgements {-}
 Not applicable.
 
-# Figure legends
+# Figure legends {-}
 ```{r figure1-creation, echo=FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
@@
 
-# References
+# References {-}

### 2016-12-17 inst/manuscript/manuscript.rmd
Minor clarification that 'Table S2' is NOT in the current manuscript but in Ploier et al. (2016);

@@
 `r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
-prior manual analysis by @ploier_dimerization_2016 (Table S2), where $\alpha
-\times 10^4 \approx 16$ was reported for mutant and $\alpha \times 10^4 \approx
-7$ for wild type rhodopsin. Based on the manual analysis of the data we conclude
-in @ploier_dimerization_2016 that the mutant rhodopsins investigated are
-reconstituted into proteoliposomes in monomeric form, contrary to the wild type,
-which is reconstituting as a homodimer. 
+prior manual analysis by @ploier_dimerization_2016 (Table S2 therein), where
+$\alpha \times 10^4 \approx 16$ was reported for mutant and 
+$\alpha \times 10^4 \approx 7$ for wild type rhodopsin. Based on the manual
+analysis of the data we conclude in @ploier_dimerization_2016 that the mutant
+rhodopsins investigated are reconstituted into proteoliposomes in monomeric
+form, contrary to the wild type, which is reconstituting as a homodimer. 
 `flippant` analysis of the data shows identical trends and close matches of the

### 2016-12-17 inst/manuscript/manuscript.rmd
Minor clarifications in the 'Availability' section;

@@
 ## Availability of data and materials {-}
-The `R` package `flippant` provides all functionality as well as data presented
-here along with extensive additional documentation and example code accessible
-from within `R` in an integrated manner.
+The `R` package `flippant` provides in an integrated manner and accessible
+from within `R` all functionality as well as data presented here along with
+extensive additional documentation and example code.
 
@@
 acceptance for publication in the supplementary material and may be installed
-from that file using ` install.packages(file.choose(), type = 'source')`.
+from that file using `install.packages(file.choose(), type = 'source')`.
 
@@
 
-Thirdly the code base and development history is publicly accessible at \
-`https://bitbucket.org/graumannlabtools/flippant`.
+Thirdly the code base and development history will, upon publication, be
+publicly accessible at
+[`https://bitbucket.org/graumannlabtools/flippant`](https://bitbucket.org/graumannlabtools/flippant).
 

### 2016-12-18 inst/manuscript/manuscript.rmd
Fix a minor typo/formatting issue;

@@
 
-Figure \@ref(fig:figure2-creation) A emphasizes reproducibility between
+Figure \@ref(fig:figure2-creation)A emphasizes reproducibility between
 independent experiments ("Experiment 1" and "Experiment 2") on the four probed

### 2016-12-19 inst/manuscript/manuscript.rmd
Switch to CRAN as targeted hosting archive;

@@
 # Availablility and Implementation {-}
-`flippant` has been implemented in `R` [@r_core_team_r:_2016] and integrated 
-into the `Bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
-within a functional `R` environment:
+`flippant` has been implemented in `R` [@r_core_team_r:_2016] and Is available
+"Comprehensive `R` Archive Network" (CRAN). It is thus install-- and loadable as
+follows from within a functional `R` environment:
 
 ```{r noeval_demonstrate_installation, eval = FALSE}
-source("http://bioconductor.org/biocLite.R")
-biocLite(pkgs = "flippant")
+install.packages("flippant")
 library("flippant")

### 2016-12-19 inst/manuscript/manuscript.rmd
Add an abbreviaton section as requested by BMC Bioinformatics;
Minor fixes to mentionings of CRAN;

@@
 
+# Abbreviations {-}
+ATP: 
+  ~ Adenosine triphosphate
+
+BSA:
+  ~ Bovine serum albumin
+
+CRAN:
+  ~ The Comprehensive `R` Archive Network
+
+MAD:
+  ~ Median absolute deviation
+
+NBD:
+  ~ Nitrobenzoxadiazole
+
+PPR:
+  ~ Protein to phospholipid ratio
+
+RAM:
+  ~ Random--access memory
+
+SSD:
+  ~ Solid state disk
+
 # Background {-}
@@
 # Availablility and Implementation {-}
-`flippant` has been implemented in `R` [@r_core_team_r:_2016] and Is available
-"Comprehensive `R` Archive Network" (CRAN). It is thus install-- and loadable as
-follows from within a functional `R` environment:
+`flippant` has been implemented in `R` [@r_core_team_r:_2016] and is available
+in The Comprehensive `R` Archive Network (CRAN). It is thus install-- and
+loadable as follows from within a functional `R` environment:
 
@@
 
-The package is also uploaded to the comprehensive `R` archive network (CRAN) and
+The package is also uploaded to The Comprehensive `R` Archive Network (CRAN) and
 may thus be installed in its most up--to date version using 

### 2016-12-19 inst/manuscript/manuscript.rmd
Render two further mentionings of "R" fixed-width;

@@
 # Keywords {-}
-scramblase; dithionite scramblase assay; R
+scramblase; dithionite scramblase assay; `R`
 
@@
 context of dithionite scramblase assays. Requiring only basic familiarity with 
-R as an environment for statistical computing and graphics 
+`R` as an environment for statistical computing and graphics 
 [@r_core_team_r:_2016], scientists can quickly analyse such data and arrive at 

### 2016-12-22 inst/manuscript/manuscript.rmd
Unify title casing of section headers;

@@
 # Declarations {-}
-## Ethics approval and consent to participate {-}
+## Ethics Approval and Consent to Participate {-}
 Not applicable.
 
-## Consent to publish {-}
+## Consent to Publish {-}
 Not applicable.
 
-## Availability of data and materials {-}
+## Availability of Data and Materials {-}
 The `R` package `flippant` provides in an integrated manner and accessible
@@
 
-## Competing interests {-}
+## Competing Interests {-}
 The authors declare that they have no competing interests.
@@
 
-## Authors' contributions {-}
+## Authors' Contributions {-}
 R.J.C and J.G. wrote the code, B.P., M.A.G. and A.K.M. guided the implementation
@@
 
-# Figure legends {-}
+# Figure Legends {-}
 ```{r figure1-creation, echo=FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying a subset of the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}

### 2017-01-02 inst/manuscript/manuscript.rmd
Minor reformatting;

@@
   scramblase assays'
-author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon^‡^
-  and Johannes Graumann ^†,§,^*
+author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon
+  ^‡^ and Johannes Graumann ^†§\*^
 date: '`r format(Sys.Date(), "%B %d,%Y")`'
@@
   bookdown::pdf_document2:
+    fig_caption: yes
+    keep_tex: yes
     toc: no
+  bookdown::word_document2:
     fig_caption: yes
-  html_document:
-    fig_caption: yes
-  bookdown::word_document2:
     toc: no
-    fig_caption: yes
 csl: biomed-central.csl
@@
 †
-:    \
-    Research Division, Weill Cornell Medicine -- Qatar, P.O.Box 24144, Doha, State of Qatar
+:   Research Division, Weill Cornell Medicine -- Qatar, P.O.Box 24144, Doha,
+    State of Qatar
 
@@
 §
-:   Current Address: Scientific Service Group Biomolecular Mass Spectrometry, Max Planck Institute for Heart and Lung Research, W.G. Kerckhoff Institute, Ludwigstr. 43, D--61231 Bad Nauheim, Germany
+:   Current Address: Scientific Service Group Biomolecular Mass Spectrometry,
+    Max Planck Institute for Heart and Lung Research, W.G. Kerckhoff Institute,
+    Ludwigstr. 43, D--61231 Bad Nauheim, Germany
 

### 2017-01-02 inst/manuscript/manuscript.rmd
Minor yaml-header modification: keep processed md files for manual pandoc-processing outside of RStudio;

@@
 output:
-  bookdown::pdf_document2:
-    fig_caption: yes
-    keep_tex: yes
-    toc: no
   bookdown::word_document2:
@@
     toc: no
+  bookdown::pdf_document2:
+    fig_caption: yes
+    toc: no
+clean: no
 csl: biomed-central.csl

### 2017-01-02 inst/manuscript/manuscript.rmd
'clean = FALSE' dows NOT apear to work from the yaml header but must be called from the console: rmarkdown::render('inst/manuscript/manuscript.rmd', 'bookdown::pdf_document2', clean = FALSE);

@@
     toc: no
-clean: no
 csl: biomed-central.csl

### 2017-01-10 inst/manuscript/manuscript.rmd
Fix typos;

@@
 # Input Data and Data Processing {-}
-To analyse raw data stemming from dithionite scramblase assays, `flippant` 
+To analyze raw data stemming from dithionite scramblase assays, `flippant` 
 requires for each data point information on the path to the 
@@
 `R` as an environment for statistical computing and graphics 
-[@r_core_team_r:_2016], scientists can quickly analyse such data and arrive at 
+[@r_core_team_r:_2016], scientists can quickly analyze such data and arrive at 
 publication--grade graphics that offer extensive facilities for individual 
@@
 [@kubelt_transbilayer_2002;@vehring_flip-flop_2007], can utilize an essentially 
-identical data analysis workflow, `flippant` is expected to facilitate analysis
+identical data analysis work flow, `flippant` is expected to facilitate analysis
 of such experiments as well.
@@
 'adj.
-PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
+PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconstitution."}
 figure2_plot %<>% multipanelfigure::add_panel(

### 2017-01-10 inst/manuscript/manuscript.rmd
Make pandoc understand "em"-dashes;

@@
     toc: no
+    pandoc_args: ["--smart"]
   bookdown::pdf_document2:

### 2017-02-03 inst/manuscript/manuscript.rmd
Move the abbreviations list to above the 'Declaration' statements,as requested by editorial staff;
Renmae sections, as requested by editorial staff;

@@
 
-# Abbreviations {-}
-ATP: 
-  ~ Adenosine triphosphate
-
-BSA:
-  ~ Bovine serum albumin
-
-CRAN:
-  ~ The Comprehensive `R` Archive Network
-
-MAD:
-  ~ Median absolute deviation
-
-NBD:
-  ~ Nitrobenzoxadiazole
-
-PPR:
-  ~ Protein to phospholipid ratio
-
-RAM:
-  ~ Random--access memory
-
-SSD:
-  ~ Solid state disk
-
 # Background {-}
@@
 
-# Availablility and Implementation {-}
+# Implementation {-}
 `flippant` has been implemented in `R` [@r_core_team_r:_2016] and is available
@@
 
-# Input Data and Data Processing {-}
+## Input Data and Data Processing {-}
 To analyze raw data stemming from dithionite scramblase assays, `flippant` 
@@
 
-# Main Features {-}
-## Template Generation for Data Input {-}
+## Main Features {-}
+### Template Generation for Data Input {-}
 Supporting the user in providing the input data needed, the following function 
@@
 
-## Graphic Representation of Spectral Traces {-}
+### Graphic Representation of Spectral Traces {-}
 In a first, graphical data analytic step of a scramblase assay--derived data 
@@
 
-## Scramblase Assay Analysis {-}
+### Scramblase Assay Analysis {-}
 Plotting protein to phospholipid ratio (PPR) against the likelihood for a given
@@
 
-# Case Study {-}
+# Results and Discussion {-}
 *Retinitis pigmentosa* is a degenerative disease of the retina, the majority of 
@@
 
+# Abbreviations {-}
+ATP: 
+  ~ Adenosine triphosphate
+
+BSA:
+  ~ Bovine serum albumin
+
+CRAN:
+  ~ The Comprehensive `R` Archive Network
+
+MAD:
+  ~ Median absolute deviation
+
+NBD:
+  ~ Nitrobenzoxadiazole
+
+PPR:
+  ~ Protein to phospholipid ratio
+
+RAM:
+  ~ Random--access memory
+
+SSD:
+  ~ Solid state disk
+
 # Declarations {-}

### 2017-02-03 inst/manuscript/manuscript.rmd
Amend funding statement as requested by editorial staff;
Include 'Additional Files' section and approrpiate referencing, as requested by editorial staff;

@@
 The package is available as an `R` source package in the version current at
-acceptance for publication in the supplementary material and may be installed
+acceptance for publication as Additional file 1 and may be installed
 from that file using `install.packages(file.choose(), type = 'source')`.
@@
 authors. B.P. was also supported by the Austrian Science Fund (FWF), project
-J3686--B21.
+J3686--B21. No funding body was involved in the design of or conclusions drawn
+from this study.
 
@@
 
+# Additional Files {-}
+Additional file 1: `R` source package of `flippant` in the version current at
+acceptance for publication.
+
 # References {-}

### 2017-02-03 inst/manuscript/manuscript.rmd
Remove deep referencing of Ploier et al 2016 in the main text, as requested by editorial staff;

@@
 `flippant`'s capabilities are demonstrated here by reanalyzing a subset of the
-data underlying Figure 4C--F in @ploier_dimerization_2016. The first step is to
-extract the data files, stored in a ZIP archive within the package.
+data in @ploier_dimerization_2016. The first step is to extract the data files,
+stored in a ZIP archive within the package.
 
@@
 rhodopsins. Forgoing reproducibility analysis in favor of a potentially more
-reliable result and following more closely the analysis in Figure 4C--F by
+reliable result and following more closely the analysis by
 @ploier_dimerization_2016, a single fit may be performed for the combined data
@@
 `r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
-prior manual analysis by @ploier_dimerization_2016 (Table S2 therein), where
+prior manual analysis by @ploier_dimerization_2016, where
 $\alpha \times 10^4 \approx 16$ was reported for mutant and 

### 2017-02-03 inst/manuscript/manuscript.rmd
Minor edit to reflect the fact that the repository is public;

@@
 
-Thirdly the code base and development history will, upon publication, be
-publicly accessible at
+Thirdly the code base and development history is publicly accessible at
 [`https://bitbucket.org/graumannlabtools/flippant`](https://bitbucket.org/graumannlabtools/flippant).

### 2017-02-03 inst/manuscript/manuscript.rmd
Order shuffle;
Minor change in pandoc argument handling by rstudio;

@@
     fig_caption: yes
+    pandoc_args: --smart
     toc: no
-    pandoc_args: ["--smart"]
   bookdown::pdf_document2:
@@
 ## Funding {-}
-J.G., R.J.C. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
+R.J.C., J.G. and the Proteomics Core at WCM--Q are supported by ``Biomedical 
 Research Program'' funds at Weill Cornell Medicine -- Qatar, a program 
